### 2020-02-21 sections/pitfalls.tex
First commit

\section{Potential Pitfalls}
\label{sec:pitfalls}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:

### 2020-02-21 manuscript.tex
added toc

% This is the main manuscript file. The preamble is suggested by Springer and
% should not be changed.
%
% 
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

\usepackage{newtxtext}       % 
\usepackage{newtxmath}       % selects Times Roman as basic font

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy}
\titlerunning{Correlating SICM and SRFM}

\author{Name of First Author and Name of Second Author}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long

\institute{%
  Name of First Author \and
  Name of Second Author \and
  Patrick Happel \at
  Nanoscopy Group,
  RUBION, Ruhr-Universität Bochum,
  Universtätsstraße 150, D-44801 Bochum, Germany
  \email{patrick.happel@rub.de}
}

\maketitle

%\abstract*{Each chapter should be preceded by an abstract (no more than 200 words) that summarizes the content. The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access. This allows unregistered users to read the abstract as a teaser for the complete chapter.
%Please use the 'starred' version of the \texttt{abstract} command for typesetting the text of the online abstracts (cf. source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript. Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}

\abstract{%
sdfa  
}

\tableofcontents

\input{sections/introduction}
\input{sections/srfm}
\input{sections/correlated-sicm-and-fm}
\input{sections/correlated-sicm-and-srfm}
\input{sections/pitfalls}

\bibliographystyle{spphys}
\bibliography{literature}

\end{document}

% Here are some introductions how to use the class

Use the standard \verb|equation| environment to typeset your equations, e.g.
%
\begin{equation}
a \times b = c\;,
\end{equation}
%
however, for multiline equations we recommend to use the \verb|eqnarray| environment\footnote{In physics texts please activate the class option \texttt{vecphys} to depict your vectors in \textbf{\itshape boldface-italic} type - as is customary for a wide range of physical subjects}.
\begin{eqnarray}
\left|\nabla U_{\alpha}^{\mu}(y)\right| &\le&\frac1{d-\alpha}\int
\left|\nabla\frac1{|\xi-y|^{d-\alpha}}\right|\,d\mu(\xi) =
\int \frac1{|\xi-y|^{d-\alpha+1}} \,d\mu(\xi)  \\
&=&(d-\alpha+1) \int\limits_{d(y)}^\infty
\frac{\mu(B(y,r))}{r^{d-\alpha+2}}\,dr \le (d-\alpha+1)
\int\limits_{d(y)}^\infty \frac{r^{d-\alpha}}{r^{d-\alpha+2}}\,dr
\label{eq:01}
\end{eqnarray}

\subsection{Subsection Heading}
\label{subsec:2}
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.  Further on please use the \LaTeX\ automatism for all your cross-references\index{cross-references} and citations\index{citations} as has already been described in Sect.~\ref{sec:2}.

\begin{quotation}
Please do not use quotation marks when quoting texts! Simply use the \verb|quotation| environment -- it will automatically be rendered in line with the preferred layout.
\end{quotation}

\subsubsection{Subsubsection Heading}
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.  Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{subsec:2}, see also Fig.~\ref{fig:1}\footnote{If you copy text passages, figures, or tables from other works, you must obtain \textit{permission} from the copyright holder (usually the original publisher). Please enclose the signed permission with the manuscript. The sources\index{permission to print} must be acknowledged either in the captions, as footnotes or in a separate section of the book.}

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

% For figures use
%
%\begin{figure}[b]
%\sidecaption
% Use the relevant command for your figure-insertion program
% to insert the figure file.
% For example, with the graphicx style use
%\includegraphics[scale=.65]{figure}
%
% If no graphics program available, insert a blank space i.e. use
%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
%
%\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page. If the %figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional %argument \texttt{[t]} with the \texttt{sidecaption} command}
%\label{fig:1}       % Give a unique label
%\end{figure}

\paragraph{Paragraph Heading} %
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.  Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

For typesetting numbered lists we recommend to use the \verb|enumerate| environment -- it will automatically rendered in line with the preferred layout.

\begin{enumerate}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\begin{enumerate}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\end{enumerate}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\end{enumerate}

\subparagraph{Subparagraph Heading} In order to avoid simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}, see also Fig.~\ref{fig:2}.

For unnumbered list we recommend to use the \verb|itemize| environment -- it will automatically be rendered in line with the preferred layout.

\begin{itemize}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development, cf. Table~\ref{tab:1}.}
\begin{itemize}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\end{itemize}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\end{itemize}

% \begin{figure}[t]
% \sidecaption[t]
% % Use the relevant command for your figure-insertion program
% % to insert the figure file.
% % For example, with the option graphics use
% \includegraphics[scale=.65]{figure}
% %
% % If no graphics program available, insert a blank space i.e. use
% %\picplace{5cm}{2cm} % Give the correct figure height and width in cm
% %
% %\caption{Please write your figure caption here}
% \caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page. If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
% \label{fig:2}       % Give a unique label
% \end{figure}

\runinhead{Run-in Heading Boldface Version} Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

\subruninhead{Run-in Heading Boldface and Italic Version} Use the \LaTeX\ automatism for all your cross-refer\-ences and citations as has already been described in Sect.~\ref{sec:2}\index{paragraph}.

\subsubruninhead{Run-in Heading Displayed Version} Use the \LaTeX\ automatism for all your cross-refer\-ences and citations as has already been described in Sect.~\ref{sec:2}\index{paragraph}.
% Use the \index{} command to code your index words
%
% For tables use
%
\begin{table}[!t]
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
%
% Follow this input for your own table layout
%
\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
\hline\noalign{\smallskip}
Classes & Subclass & Length & Action Mechanism  \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Translation & mRNA$^a$  & 22 (19--25) & Translation repression, mRNA cleavage\\
Translation & mRNA cleavage & 21 & mRNA cleavage\\
Translation & mRNA  & 21--22 & mRNA cleavage\\
Translation & mRNA  & 24--26 & Histone and DNA Modification\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
$^a$ Table foot note (with superscript)
\end{table}
%
\section{Section Heading}
\label{sec:3}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.  Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

If you want to list definitions or the like we recommend to use the enhanced \verb|description| environment -- it will automatically rendered in line with the preferred layout.

\begin{description}[Type 1]
\item[Type 1]{That addresses central themes pertainng to migration, health, and disease. In Sect.~\ref{sec:1}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
\item[Type 2]{That addresses central themes pertainng to migration, health, and disease. In Sect.~\ref{subsec:2}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
\end{description}

\subsection{Subsection Heading} %
In order to avoid simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Use the \LaTeX\ automatism for all your cross-references and citations citations as has already been described in Sect.~\ref{sec:2}.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

\begin{svgraybox}
If you want to emphasize complete paragraphs of texts we recommend to use the newly defined class option \verb|graybox| and the newly defined environment \verb|svgraybox|. This will produce a 15 percent screened box 'behind' your text.

If you want to emphasize complete paragraphs of texts we recommend to use the newly defined class option and environment \verb|svgraybox|. This will produce a 15 percent screened box 'behind' your text.
\end{svgraybox}

\subsubsection{Subsubsection Heading}
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.  Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

\begin{theorem}
Theorem text goes here.
\end{theorem}
%
% or
%
\begin{definition}
Definition text goes here.
\end{definition}

\begin{proof}
%\smartqed
Proof text goes here.
%\qed
\end{proof}

\paragraph{Paragraph Heading} %
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.  Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

Note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
%
% For built-in environments use
%
\begin{theorem}
Theorem text goes here.
\end{theorem}
%
\begin{definition}
Definition text goes here.
\end{definition}
%
\begin{proof}
%\smartqed
Proof text goes here.
%\qed
\end{proof}
%
\begin{trailer}{Trailer Head}
If you want to emphasize complete paragraphs of texts in an \verb|Trailer Head| we recommend to
use  \begin{verbatim}\begin{trailer}{Trailer Head}
...
\end{trailer}\end{verbatim}
\end{trailer}
%
\begin{question}{Questions}
If you want to emphasize complete paragraphs of texts in an \verb|Questions| we recommend to
use  \begin{verbatim}\begin{question}{Questions}
...
\end{question}\end{verbatim}
\end{question}
\eject%
\begin{important}{Important}
If you want to emphasize complete paragraphs of texts in an \verb|Important| we recommend to
use  \begin{verbatim}\begin{important}{Important}
...
\end{important}\end{verbatim}
\end{important}
%
\begin{warning}{Attention}
If you want to emphasize complete paragraphs of texts in an \verb|Attention| we recommend to
use  \begin{verbatim}\begin{warning}{Attention}
...
\end{warning}\end{verbatim}
\end{warning}

\begin{programcode}{Program Code}
If you want to emphasize complete paragraphs of texts in an \verb|Program Code| we recommend to
use

\verb|\begin{programcode}{Program Code}|

\verb|\begin{verbatim}...\end{verbatim}|

\verb|\end{programcode}|

\end{programcode}
%
\begin{tips}{Tips}
If you want to emphasize complete paragraphs of texts in an \verb|Tips| we recommend to
use  \begin{verbatim}\begin{tips}{Tips}
...
\end{tips}\end{verbatim}
\end{tips}
\eject
%
\begin{overview}{Overview}
If you want to emphasize complete paragraphs of texts in an \verb|Overview| we recommend to
use  \begin{verbatim}\begin{overview}{Overview}
...
\end{overview}\end{verbatim}
\end{overview}
\begin{backgroundinformation}{Background Information}
If you want to emphasize complete paragraphs of texts in an \verb|Background|
\verb|Information| we recommend to
use

\verb|\begin{backgroundinformation}{Background Information}|

\verb|...|

\verb|\end{backgroundinformation}|
\end{backgroundinformation}
\begin{legaltext}{Legal Text}
If you want to emphasize complete paragraphs of texts in an \verb|Legal Text| we recommend to
use  \begin{verbatim}\begin{legaltext}{Legal Text}
...
\end{legaltext}\end{verbatim}
\end{legaltext}
%
\begin{acknowledgement}
If you want to include acknowledgments of assistance and the like at the end of an individual chapter please use the \verb|acknowledgement| environment -- it will automatically be rendered in line with the preferred layout.
\end{acknowledgement}
%
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
%
%
When placed at the end of a chapter or contribution (as opposed to at the end of the book), the numbering of tables, figures, and equations in the appendix section continues on from that in the main text. Hence please \textit{do not} use the \verb|appendix| command when writing an appendix at the end of your chapter or contribution. If there is only one the appendix is designated ``Appendix'', or ``Appendix 1'', or ``Appendix 2'', etc. if there is more than one.

\begin{equation}
a \times b = c
\end{equation}

%\input{references}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-09-04 manuscript.tex
First draft of abstract (still too long)

@@
 
-\author{Name of First Author and Name of Second Author}
+\author{Annika Haak, Astrid Gesper and Patrick Happel}
+\authorrunning{Haak et al.}
 % Use \authorrunning{Short Title} for an abbreviated version of
@@
 \institute{%
-  Name of First Author \and
-  Name of Second Author \and
+  Annika Haak\and
+  Astrid Gesper \and
   Patrick Happel \at
@@
 \abstract{%
-sdfa  
+  The development of diffraction unlimited fluorescence microscopy has paved
+  the way for a detailed understanding of cellular dynamics since live-cell
+  investigations with a resolution below 100\,nm have become
+  available, allowing to investigate 
+  labeled specimen such as proteins and their distribution within a cell at a
+  new level of detail. However, the place of the interaction between the
+  cell's internal processes and external signals, the cell membrane, cannot be
+  investigated by fluorescence microscopy since inserting fluorescent dyes
+  alters the physico-chemical properties of the cell membrane.
+%
+  The latter, however, is a unique strength of scanning ion conductance
+  microscopes (SICM),
+  which use a fine tip to determine the topography of the investigated sample
+  and thus allow to investigate the cell membrane without labelling.    
+%  
+  Since both types of microscopes can be applied to living cells and provide a
+  resolution below the diffraction limit, correlating data from the two
+  seems a promising approach to further the understanding of
+  the organisation of the cell plasma membrane and of the mechanisms involved
+  in the transport processes across it.
+%  
+  Here we briefly introduce the different approaches to Super-Resolved
+  Fluorescence Microscopy (SRFM) and review the applications of correlating SICM
+  and diffraction-limited as well as diffraction-unlimited fluorescence
+  microscopy. Lastly, we discuss potential implementations of combined
+  SRFM/SICM instruments and the potential pitfalls that may arise during the
+  development of such, hitherto putative, instruments.
 }

### 2020-09-08 sections/introduction.tex
first commit
Started explaining the resolutions of SICM and LM

--- 2020-02-21 sections/pitfalls.tex
@@
-\section{Potential Pitfalls}
-\label{sec:pitfalls}
+\section{Introduction}
+\label{sec:introduction}
+Many cellular processes like exo- and endocytosis, cell growth, division and
+migration, to name only a few, require the rearrangement, growth or shrinkage
+of the cellular membrane. Scanning Ion Conductance Microscopy (SICM)
+\cite{Hansma1989} is a contact-free scanning probe technique which, if applied
+to cellular specimen, provides information about the dynamics of the
+topography of the cell membrane. However, the underlying dynamics of the
+molecular machinery which orchestrates the cell membrane dynamics remain
+unresolved by SICM investigations. The latter can be resolved by fluorescence
+microscopy (FM), which allows tagging a protein of interest with a fluorescent
+marker and observing its dynamics. Therefore, correlating fluorescence and
+scanning ion conductance microscopy data might help to unravel the mechanisms
+that underlie the cellular processes listed above that occur at the cellular
+membrane.
+
+\begin{figure}
+  \sidecaption[t]
+  \includegraphics{gr/intro/Fig_SICM-resolution}
+  \caption{\textbf{Resolution of SICM.} \textbf{A} \textbf{B} Two
+    consecutive SICM recordings of the equatorial segment of a living boar
+    spermatozoon recorded 10 minutes apart with a scanning pipette with
+    $r_\mathrm{i} \approx 6.75\,\text{nm}$}
+  \label{fig:sicm-resolution}
+\end{figure}
+
+The resolution of SICM is determined by the inner opening radius
+$r_\mathrm{i}$ of the scanning pipette and can be approximated as
+$3r_\mathrm{i}$ (Fig.~\ref{fig:sicm-resolution}A)
+\cite{rheinlaender:094905,Rheinlaender2015}.  Thus, the resolution of SICM is
+only limited by the technical limits to produce pipettes with very small
+openings. Pipettes with radii of approximately 6.75\,nm have been used in for
+SICM imaging (Fig.~\ref{fig:sicm-resolution}B) \cite{Shevchuk2008}. In
+contrast, the resolution in light microscopy is fundamentally limited by the
+diffraction of light. As Ernst Abbe found out in 1873, a beam of light cannot
+be focused to a spot smaller than the resolution limit $d_\text{min}$ \cite{Abbe1873}:
+\begin{equation}
+  d_\text{min} = \frac\lambda{2n\sin\alpha} = \frac\lambda{2\mathrm{NA}}\text{.}
+  \label{eq:diffraction-limit}
+\end{equation}
+Here, $\lambda$ denotes the wavelength of the light used to generate the
+image, $n$ the diffractive index of the medium between sample and objective
+lense and $\alpha$ the half-cone opening angle of the objective lense. The
+product $n\sin\alpha$ is called the numerical aperture $\mathrm{NA}$ of the
+objective. The exact limit, of course, depends on $\lambda$ and the NA of the
+objective, but as a rule of thumb, it is often stated that the resolution
+limit is in the range of 200\,nm. This is approximately 14 times the size of
+the smallest structures observed in the SICM recordings shown in
+Fig.~\ref{fig:sicm-resolution}B, which were reported to be 14\,nm
+\cite{Shevchuk2008}.
+
+\begin{figure}
+  \sidecaption
+  \includegraphics{gr/intro/Fig_SICM-and-Light-resolution}%
+  \caption{\textbf{Hypothetical fluorescence analysis of proteins in the boar
+      spermatozoon.} \textbf{A:} Proteins A and B in the stable structures
+    observed by SICM. \textbf{B:} Hypothetical positions of the fluorescent
+    labels of proteins A and B. Scale bar: 200\,nm \textbf{C:} Computed
+    fluorescence image.}
+  \label{fig:sicm-and-light-resolution}
+\end{figure}
+In all stable structures in the recordings (highlighted by
+the dashed lines) at least one group of three protrusions arranged in a line
+are observable. If one assumes, without any biological support and just to be
+able to exemplify the impact of the limited resolution of light microscopy,
+that such a row is comprised of two different proteins, one at the first and
+last position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A),
+and the other one on the central spot (green arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and one further assumes
+that the two different proteins have been labelled by two different markers
+(the positions of the markers are indicated by the magenta and green dots in Fig.~\ref{fig:sicm-and-light-resolution}B),
+the resulting light microscopy images would result in
+
+% Since its invention, the light microscope is a widely used tool in
+% biology. The development of the fluorescence and the confocal microscope
+% \cite{Heimstaedt1911,Minsky1988} along with the improvement and development in
+% staining techniques \cite{Coons1942,Tsien1998} made fluorescence microscopy
+% (FM) a standard tool in the life sciences and medicine. With the new
+% development of super-resolved fluorescence microscopy (SRFM)
+% \cite{hell+wichmann,Betzig2006,Rust2006}, fluorescence microscopy entered the
+% world beyond Abbe's diffraction limit \cite{Abbe1873}, and now allows to
+% routinely investigate questions at a length scale below 100\,nm.
+
+% SICM, as any scanning probe technique, provides information about the surface
+% of the scanned sample. In contrast, FM provides information about the
+% distribution of the labeled specimen. Gathering complementary information from
+% the same sample, surface topography
+
+% \begin{equation}
+%   \label{eq:abbe}
+%   d = \frac{\lambda}{2 n \sin\alpha}
+% \end{equation}
+
 %%% Local Variables:

### 2020-09-09 sections/introduction.tex
updated

@@
 diffraction of light. As Ernst Abbe found out in 1873, a beam of light cannot
-be focused to a spot smaller than the resolution limit $d_\text{min}$ \cite{Abbe1873}:
+be focused to a spot smaller than the resolution limit $d_\text{min}$
+\cite{Abbe1873}:
 \begin{equation}
@@
     labels of proteins A and B. Scale bar: 200\,nm \textbf{C:} Computed
-    fluorescence image.}
+    fluorescence image, resolutions were 250\,nm for the magenta and 300\,nm
+    for the green marker.}
   \label{fig:sicm-and-light-resolution}
 \end{figure}
-In all stable structures in the recordings (highlighted by
-the dashed lines) at least one group of three protrusions arranged in a line
-are observable. If one assumes, without any biological support and just to be
-able to exemplify the impact of the limited resolution of light microscopy,
-that such a row is comprised of two different proteins, one at the first and
-last position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A),
-and the other one on the central spot (green arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and one further assumes
-that the two different proteins have been labelled by two different markers
-(the positions of the markers are indicated by the magenta and green dots in Fig.~\ref{fig:sicm-and-light-resolution}B),
-the resulting light microscopy images would result in
+In all stable structures in the recordings (highlighted by the dashed lines)
+at least one group of three protrusions arranged in a line are observable. To
+exemplify the impact of the limited resolution of light microscopy, assume,
+without any biological support, that such a complex is comprised of two
+different proteins A and B, which float in the plasma membrane until they form
+the complex. In the complex, protein A is located at the first and last
+position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and
+protein B on the central spot (green arrows in
+Fig.~\ref{fig:sicm-and-light-resolution}A). Further, assume that the two
+different proteins have been labelled by two different fluorescent markers
+(the positions of the markers are indicated by the magenta and green dots in
+Fig.~\ref{fig:sicm-and-light-resolution}B) and a correlating light microscopic
+image has been recorded (Fig.~\ref{fig:sicm-and-light-resolution}C) to analyze
+the molecular composition of the stable structures.
+
+Due to the limited resolution, the fluorescence image consists of overlapping
+spots of the two different markers and looks blurred, compared to the
+SICM topography image. Although co-localisation of the two proteins can be
+observed at the positions of the stable structures, it is hard if not
+impossible to allocate the fluorescent spots to protrusions in the topography
+image.
 

### 2020-09-09 sections/introduction.tex
changed panel labels to lowercase as specified in the key style document

@@
   \includegraphics{gr/intro/Fig_SICM-resolution}
-  \caption{\textbf{Resolution of SICM.} \textbf{A} \textbf{B} Two
+  \caption{\textbf{Resolution of SICM.} \textbf{a:} \textbf{b:} Two
     consecutive SICM recordings of the equatorial segment of a living boar
@@
   \caption{\textbf{Hypothetical fluorescence analysis of proteins in the boar
-      spermatozoon.} \textbf{A:} Proteins A and B in the stable structures
-    observed by SICM. \textbf{B:} Hypothetical positions of the fluorescent
-    labels of proteins A and B. Scale bar: 200\,nm \textbf{C:} Computed
+      spermatozoon.} \textbf{a:} Proteins A and B in the stable structures
+    observed by SICM. \textbf{b:} Hypothetical positions of the fluorescent
+    labels of proteins A and B. Scale bar: 200\,nm \textbf{c:} Computed
     fluorescence image, resolutions were 250\,nm for the magenta and 300\,nm

### 2020-09-09 sections/introduction.tex
changed the labels in the text, too

@@
 $r_\mathrm{i}$ of the scanning pipette and can be approximated as
-$3r_\mathrm{i}$ (Fig.~\ref{fig:sicm-resolution}A)
+$3r_\mathrm{i}$ (Fig.~\ref{fig:sicm-resolution}a)
 \cite{rheinlaender:094905,Rheinlaender2015}.  Thus, the resolution of SICM is
@@
 openings. Pipettes with radii of approximately 6.75\,nm have been used in for
-SICM imaging (Fig.~\ref{fig:sicm-resolution}B) \cite{Shevchuk2008}. In
+SICM imaging (Fig.~\ref{fig:sicm-resolution}b) \cite{Shevchuk2008}. In
 contrast, the resolution in light microscopy is fundamentally limited by the
@@
 protein B on the central spot (green arrows in
-Fig.~\ref{fig:sicm-and-light-resolution}A). Further, assume that the two
+Fig.~\ref{fig:sicm-and-light-resolution}a). Further, assume that the two
 different proteins have been labelled by two different fluorescent markers
 (the positions of the markers are indicated by the magenta and green dots in
-Fig.~\ref{fig:sicm-and-light-resolution}B) and a correlating light microscopic
-image has been recorded (Fig.~\ref{fig:sicm-and-light-resolution}C) to analyze
+Fig.~\ref{fig:sicm-and-light-resolution}b) and a correlating light microscopic
+image has been recorded (Fig.~\ref{fig:sicm-and-light-resolution}c) to analyze
 the molecular composition of the stable structures.

### 2020-09-09 sections/srfm.tex
first commit
added subsections
added section about FM and (in parts) the differents setups

--- 2020-02-21 sections/pitfalls.tex
@@
-\section{Potential Pitfalls}
-\label{sec:pitfalls}
+\subsection{Super-Resolved Fluorescence Microscopy}
+\label{sec:srfm}
+In order to understand how super-resolved fluorescence microscopy (SRFM)
+circumvents the diffraction limit, it is helpful to recapitulate the operating
+principle of fluorescence microscopy (FM). Fluorescence is the process of the
+absorption of a photon by a molecule, the fluorophore, followed by the
+spontaneous emission of a second photon. The transitions between the energetic
+states of the fluorophore are depicted in
+Fig.~\ref{fig:jablonski-fluorescence}a. Due to the non-radiative loss of
+energy during the involved vibrational decays (black arrows in
+Fig.~\ref{fig:jablonski-fluorescence}a), the energy $h\nu_\text{em}$ of the
+emitted photon is smaller than the energy of the absorbed photon
+$h\nu_\text{ex}$ (here, $h$ denotes the Planck constant). Since the frequency $\nu$
+of a photon is given by $c\lambda^{-1}$ (with $c$: speed of light, $\lambda$:
+wavelength of the photon), the wavelength $\lambda_\text{em}$ of the emitted
+photon is larger than the wavelength $\lambda_\text{ex}$ of the absorbed
+photon.
+
+\begin{figure}
+%  \sidecaption
+  \centering
+  \includegraphics{gr/intro/Jablonski-fluorescence}
+
+  \caption{%
+    \textbf{Principle of fluorescence microscopy.}
+    \textbf{a:}
+      Jablonski diagram of fluorescence. A photon of energy
+      $h\nu_\text{ex}$ gets absorbed and excites the molecule from its
+      electronic ground state $S_0$ to a vibrational excited state of the
+      electronic state $S_1$ (green arrow). After radiation-less relaxation
+      (black arrow) into the vibrational ground state of $S_1$, the molecule
+      returns to any vibrational state of $S_0$ (red arrow) by emitting a photon
+      of energy $h\nu_\text{em}$, after which it relaxes to the lowest
+      vibrational state of $S_0$.
+    \textbf{b:}
+      Typical absorbance (green) and
+      emission (red) spectra of a fluorescent dye molecule. Green and red
+      rectangles indicate the wavelength range used for excitation (exc) and
+      detection.
+  }
+  \label{fig:jablonski-fluorescence}
+\end{figure}
+
+Typical absorbance/emission spectra of fluorophores used as dyes in FM are
+shown in Fig.~\ref{fig:jablonski-fluorescence}b. In FM, a single wavelength or
+a wavelength range (green rectangle Fig.~\ref{fig:jablonski-fluorescence}b) in
+suitable to excite the fluorophore used is chosen, by using a suitable laser
+or LED or by selecting the wavelength range via a band-pass filter from a
+white light source and send through the objective lens of the microscope to
+the sample. In most FMs (the so called epifluorescence microscopes), the
+emission is collected via the same objective lens. Since the emission is
+red-shifted with respect to the excitation wavelength, the emitted photons
+(wavelength range depicted by red rectangle in
+Fig.~\ref{fig:jablonski-fluorescence}b) can be separated from the ones used to
+excite the fluorophores by a dichroic mirror.
+
+\begin{figure}
+  \includegraphics{gr/intro/FM-setups}
+  \caption{\textbf{Beam paths and major components of fluorescent
+      microscopes.} \textbf{a:} Excitation (green) and emission (red) beam
+    paths of a wide-field microscope. \textbf{b:} Excitation (green) and
+    emission beam paths (red) of a confocal microscope.  \textbf{c:} Emission
+    beam path (filters omitted for clarity) of a confocal microscope showing
+    how out-of-focus emission (dashed and dotted lines) is suppressed by the
+    confocal pinhole.}
+  \label{fig:FM-setups}
+\end{figure}
+
+The two most common implementations of FM used in the life sciences are the
+wide-field and the confocal microscope. Both use a dichroic mirror to separate
+excitation and emission, but their implementations differ in the way how the
+sample is excited and how the emission is recorded. The beam paths and the
+major components of a wide-field and a confocal FM are depicted in
+Fig.~\ref{fig:FM-setups}. In a wide-field FM (Fig.~\ref{fig:FM-setups}a), the
+entire sample is excited at 
+the same time, and all fluorophores in the sample emit at the same time
+(yellow circles in the right inset in Fig.~\ref{fig:FM-setups}a). The emission
+of the fluorophores (solid red shape in Fig.~\ref{fig:FM-setups}a, only five
+beam paths are shown for clarity) is collected by the objective lens, passes
+the dichroic mirror and is further cleared by a band-pass filter. The emission
+then is focused by the tube lens onto the camera, which records an image of
+the emission of all fluorophores at the same time.
+
+Each fluorophore in the sample generates a diffraction limited spot on the
+camera, and spots which are not separated in space by at least the diffraction
+cannot be distinguished as single spots. Thus, the wavelength which determines
+the resolution in a wide-field microscope is the wavelength $\lamba_\text{em}$
+of the emission.
+
+The major disadvantage of a wide-field microscope is that the sample is not
+only illuminated evenly in the focal plane of the objective lens, but also
+fluorophores outside the focal plane in $z$-direction are excited and their
+emission is collected (not shown for clarity). Since they are not located in
+the focal plane of the objective lens, their emission does not result in a
+sharp spot on the camera, but instead appears as a blurred background.
+
+This led to the invention of the confocal microscope
+. The beam path of a confocal microscope is
+shown in Fig.~\ref{fig:FM-setups}b. Here, the excitation light (green solid
+shape) is focused into the sample by the objective lens and only the
+fluorophores within the diffraction limited spot are excited. Thus, the
+wavelength which determines the resolution of a confocal microscope is the
+excitation wavelength $\lambda_\text{ex}$.
+
+% Ernst Abbe found in 1873 \cite{Abbe1873} that the resolution $d$ of
+% conventional light microscopes is limited by diffaction to 
+% \begin{equation}
+%   d_\text{min} = \frac{\lambda}{2\mathrm{NA}} = \frac\lambda{2n\sin\alpha}\text.
+%   \label{eq:abbe}
+% \end{equation}
+%  One consequence of the diffraction limit is
+% that a beam of light cannot be focused to a spot smaller than $d_\text{min}$.
+
+% The place in the micropscope where the diffraction limited spot limits the
+% resolution of a microscopic recording depends on the implementation of the
+% microscope.
+
+% \begin{figure}
+% %  \includegraphics{gr/introduction/}
+% \end{figure}
+
+\subsection{General approach}
+
+\subsubsection{Different approaches}
+While the majority of SRFM techniques follows the approach outlined above,
+other techniques exist that use different approaches.
+
+\subsection{Camera-based techniques}
+
+\subsection{Scanning techniques}
 %%% Local Variables:

### 2020-09-09 sections/srfm.tex
fixed typo in "\lambda"

@@
 cannot be distinguished as single spots. Thus, the wavelength which determines
-the resolution in a wide-field microscope is the wavelength $\lamba_\text{em}$
+the resolution in a wide-field microscope is the wavelength $\lambda_\text{em}$
 of the emission.
@@
 This led to the invention of the confocal microscope
-. The beam path of a confocal microscope is
+\cite{Heimstaedt1911,Minsky1988}. The beam path of a confocal microscope is
 shown in Fig.~\ref{fig:FM-setups}b. Here, the excitation light (green solid

### 2020-09-14 sections/pitfalls.tex
Update pitfalls.tex
halb fertig, text ist nicht/nur schlecht ausformuliert, quellen fehlen noch, grafiken auch, noch unklar wo grafik sinnvoll, reihenfolge auch noch unklar
freu mich aber trotzdem über anregungen/anmerkungen

@@
 \label{sec:pitfalls}
+Combining SRFM and SICM in one setup is bound to bring up some potential pitfalls, some of which are discussed in the following:
+
+To avoid some problems from the beginning, both the SRFM and SICM setups should provide spatial resolutions in the same range.
+Also, if possible, one software should be used to control both setups to prevent delays in the imaging process due to ...
+(?)
+
+Some potential pitfalls can arise when aligning the SRFM and SICM setups.
+There are two alignment options: The first one is aligning the pipette tip and the laser beam only in the xy plane, e.g.
+for imaging fluorescent proteins in the cytoskeleton and the cell membrane simultaneously.
+The second one is additionally aligning the tip and beam in the z plane, e.g.
+to image cell membrane and fluorescent particles or proteins within the membrane simultaneously, as has been done in SSCM (?4?).
+
+It has to be put into consideration whether fine adjustment screws are enough to align the pipette and the beam.
+It is apparently sufficient for aligning SICM and confocal microscopes (??).
+In case it isn't accurate enough piezo elements might have to be used.
+However, the usage of 3 piezo elements mounted to the same platform, may it be the pipette holder or sample stage, is reported to have caused cross-talk during sample positioning leading to image artifacts in the range of 100 nm (?1?).
+Hence, it would be better to uncouple xy piezos from the z piezo.
+Furthermore, z piezos come with an increased risk of piezo drift.
+Therefore, especially the sample stage should ideally avoid z piezo usage.
+
+Both alignment options may lead to the pipette tip reflecting the beam and thereby distorting the resulting recordings.
+In this case the pipette tip would have to be retracted until it can't reflect the beam light anymore, before a recording with the optical setup can be executed.
+Consequently, this means the SRFM and the SICM recording can't be executed simultaneously but successively.
+
+While this might seem like a drawback extending the overall recording time, it also solves another problem that comes with combining SRFM and SICM: photo-bleaching and photo-damage of the sample.
+SRFM techniques like STED microscopy come with a general risk of photo-bleaching and -damage as high intensity lasers are used (?6?).
+Combining SRFM with SICM increases this risk, as SICM is a much slower imaging technique.
+The pipette will not only have to be moved in the xy plane but also in the z plane to avoid sample contact.
+Hence, the imaging speed will mostly be dependent on the SICM capillary speed especially in z direction.
+If the sample is illuminated by the laser continuously during capillary approach and retraction, photo-bleaching and -damage is likely to occur.
+Therefore, illuminating the sample right after SICM surface detection, recording and pipette retraction for a short period of time would not only result in reflection avoidance but also in less photo-bleaching and -damage.
+In case, light reflection by the scanning capillary doesn't occur, the sample could be illuminated right after surface detection leading to a faster imaging speed of the combined setup.
+
+Another problem stemming from capillary movement is the resonance of the pipette resulting from it.
+Some groups have ensured resonance reduction by using a v-groove mounting plate for the capillary instead of the conventional patch clamp pipette holders (?1?).
+
+	 		mechanical shutters? limited switching frequency
+	 			switch beams by switching akkusto-optical modulators (AOM)
+
+adjusting focal plane of the optical setup might lead to mismatch in superimposition of excitation and depletion beam
+
 %%% Local Variables:

### 2020-09-15 sections/pitfalls.tex
weniger breite Zeilen, sonst keine Änderung
stichpunkte ausformuliert

@@
 \label{sec:pitfalls}
-Combining SRFM and SICM in one setup is bound to bring up some potential pitfalls, some of which are discussed in the following:
+Combining SRFM and SICM in one setup is bound to bring up some potential
+pitfalls, some of which are discussed in the following:
 
-To avoid some problems from the beginning, both the SRFM and SICM setups should provide spatial resolutions in the same range.
-Also, if possible, one software should be used to control both setups to prevent delays in the imaging process due to ...
-(?)
+To avoid some problems from the beginning, both the SRFM and SICM setups
+should provide spatial resolutions in the same range. Also, if possible, one
+software should be used to control both setups to prevent delays in the
+imaging process due to ... (?)
 
-Some potential pitfalls can arise when aligning the SRFM and SICM setups.
-There are two alignment options: The first one is aligning the pipette tip and the laser beam only in the xy plane, e.g.
-for imaging fluorescent proteins in the cytoskeleton and the cell membrane simultaneously.
-The second one is additionally aligning the tip and beam in the z plane, e.g.
-to image cell membrane and fluorescent particles or proteins within the membrane simultaneously, as has been done in SSCM (?4?).
+Some potential pitfalls can arise when aligning the SRFM and SICM
+setups. There are two alignment options: The first one is aligning the pipette
+tip and the laser beam only in the xy plane, e.g. for imaging fluorescent
+proteins in the cytoskeleton and the cell membrane simultaneously. The second
+one is additionally aligning the tip and beam in the z plane, e.g. to image
+cell membrane and fluorescent particles or proteins within the membrane
+simultaneously, as has been done in SSCM (?4?).
 
-It has to be put into consideration whether fine adjustment screws are enough to align the pipette and the beam.
-It is apparently sufficient for aligning SICM and confocal microscopes (??).
-In case it isn't accurate enough piezo elements might have to be used.
-However, the usage of 3 piezo elements mounted to the same platform, may it be the pipette holder or sample stage, is reported to have caused cross-talk during sample positioning leading to image artifacts in the range of 100 nm (?1?).
-Hence, it would be better to uncouple xy piezos from the z piezo.
-Furthermore, z piezos come with an increased risk of piezo drift.
-Therefore, especially the sample stage should ideally avoid z piezo usage.
+Especially the second option tracing the cell surface would require constant
+focal plane adjustment of the optical setup. This might eventually lead to a
+mismatch in the excitation and depletion beam superimposition.
 
-Both alignment options may lead to the pipette tip reflecting the beam and thereby distorting the resulting recordings.
-In this case the pipette tip would have to be retracted until it can't reflect the beam light anymore, before a recording with the optical setup can be executed.
-Consequently, this means the SRFM and the SICM recording can't be executed simultaneously but successively.
+It has to be put into consideration whether fine adjustment screws are enough
+to align the pipette and the beam. It is apparently sufficient for aligning
+SICM and confocal microscopes (??). In case it isn't accurate enough piezo
+elements might have to be used. However, the usage of 3 piezo elements mounted
+to the same platform, may it be the pipette holder or sample stage, is
+reported to have caused cross-talk during sample positioning leading to image
+artifacts in the range of 100 nm (?1?). Hence, it would be better to uncouple
+xy piezos from the z piezo. Furthermore, z piezos come with an increased risk
+of piezo drift. Therefore, especially the sample stage should ideally avoid z
+piezo usage.
 
-While this might seem like a drawback extending the overall recording time, it also solves another problem that comes with combining SRFM and SICM: photo-bleaching and photo-damage of the sample.
-SRFM techniques like STED microscopy come with a general risk of photo-bleaching and -damage as high intensity lasers are used (?6?).
-Combining SRFM with SICM increases this risk, as SICM is a much slower imaging technique.
-The pipette will not only have to be moved in the xy plane but also in the z plane to avoid sample contact.
-Hence, the imaging speed will mostly be dependent on the SICM capillary speed especially in z direction.
-If the sample is illuminated by the laser continuously during capillary approach and retraction, photo-bleaching and -damage is likely to occur.
-Therefore, illuminating the sample right after SICM surface detection, recording and pipette retraction for a short period of time would not only result in reflection avoidance but also in less photo-bleaching and -damage.
-In case, light reflection by the scanning capillary doesn't occur, the sample could be illuminated right after surface detection leading to a faster imaging speed of the combined setup.
+Both alignment options may lead to the pipette tip reflecting the beam and
+thereby distorting the resulting recordings. In this case the pipette tip
+would have to be retracted until it can't reflect the beam light anymore,
+before a recording with the optical setup can be executed. Consequently, this
+means the SRFM and the SICM recording can't be executed simultaneously but
+successively.
 
-Another problem stemming from capillary movement is the resonance of the pipette resulting from it.
-Some groups have ensured resonance reduction by using a v-groove mounting plate for the capillary instead of the conventional patch clamp pipette holders (?1?).
+While this might seem like a drawback extending the overall recording time, it
+also solves another problem that comes with combining SRFM and SICM:
+photo-bleaching and photo-damage of the sample. SRFM techniques like STED
+microscopy come with a general risk of photo-bleaching and -damage as high
+intensity lasers are used (?6?). Combining SRFM with SICM increases this risk,
+as SICM is a much slower imaging technique. The pipette will not only have to
+be moved in the xy plane but also in the z plane to avoid sample
+contact. Hence, the imaging speed will mostly be dependent on the SICM
+capillary speed especially in z direction. If the sample is illuminated by the
+laser continuously during capillary approach and retraction, photo-bleaching
+and -damage is likely to occur. Therefore, illuminating the sample right after
+SICM surface detection, recording and pipette retraction for a short period of
+time would not only result in reflection avoidance but also in less
+photo-bleaching and -damage. In case, light reflection by the scanning
+capillary doesn't occur, the sample could be illuminated right after surface
+detection leading to a faster imaging speed of the combined setup.
 
-	 		mechanical shutters? limited switching frequency
-	 			switch beams by switching akkusto-optical modulators (AOM)
+The switching of the laser beams could either be done via mechanical
+shutters. However, as mechanical shutters have a limited switching frequency,
+it might be preferential to switch beams by switching akkusto-optical modulators.
 
-adjusting focal plane of the optical setup might lead to mismatch in superimposition of excitation and depletion beam
+Another problem stemming from capillary movement is the resonance of the
+pipette resulting from it. Some groups have ensured resonance reduction by
+using a v-groove mounting plate for the capillary instead of the conventional
+patch clamp pipette holders (?1?).
 

### 2020-09-15 sections/pitfalls.tex
ein paar quellen ergänzt

@@
 cell membrane and fluorescent particles or proteins within the membrane
-simultaneously, as has been done in SSCM (?4?).
+simultaneously, as has been done in SSCM \cite{Gorelik2002a}\cite{Shevchuk2008}.
 
@@
 reported to have caused cross-talk during sample positioning leading to image
-artifacts in the range of 100 nm (?1?). Hence, it would be better to uncouple
-xy piezos from the z piezo. Furthermore, z piezos come with an increased risk
-of piezo drift. Therefore, especially the sample stage should ideally avoid z
-piezo usage.
+artifacts in the range of 100 nm \cite{Shevchuk.2013}. Hence, it would be
+better to uncouple xy piezos from the z piezo. Furthermore, z piezos come with
+an increased risk of piezo drift. Therefore, especially the sample stage
+should ideally avoid z piezo usage.
 
@@
 microscopy come with a general risk of photo-bleaching and -damage as high
-intensity lasers are used (?6?). Combining SRFM with SICM increases this risk,
+intensity lasers are used. Combining SRFM with SICM increases this risk,
 as SICM is a much slower imaging technique. The pipette will not only have to
@@
 using a v-groove mounting plate for the capillary instead of the conventional
-patch clamp pipette holders (?1?).
+patch clamp pipette holders \cite{Shevchuk.2013}.
 

### 2020-09-22 sections/srfm.tex
section on stochastic approaches (needs some closing remarks)

@@
-\subsection{Super-Resolved Fluorescence Microscopy}
-\label{sec:srfm}
+\subsection{Fluorescence Microscopy}
+\label{sec:fm}
 In order to understand how super-resolved fluorescence microscopy (SRFM)
@@
 wavelength which determines the resolution of a confocal microscope is the
-excitation wavelength $\lambda_\text{ex}$.
+excitation wavelength $\lambda_\text{ex}$.  In contrast to the wide-field
+microscope, the emission of the fluorophores is focused onto a pinhole which
+is located in front of a single detector (left inset in
+Fig.~\ref{fig:FM-setups}b). Since this setup does not allow imaging the entire
+sample at once, the sample has to be scanned with respect to the excitation
+light beam and the image is collected pixel by
+pixel. Fig.~\ref{fig:FM-setups}c illustrates the major effect of the pinhole:
+Emission from out-of-focus planes (dotted and dashed lines) is blocked by the
+pinhole since it is located in the same focal plane as the sample (thus the
+name \emph{confocal}).
+
+\subsection{Circumventing the diffraction limit}
+\label{sec:circumvent-diffraction-limit}
+The general approach to circumvent the diffraction limit is to reduce the
+fluorophores within a diffraction limited spot which contribute to the
+recorded signal, that is, to turn the fluorophores into an ``off''-state. Only
+the fluorophores which contribute to the signal remain in the ``on''-state.
+However, a few more approaches exist, for example 4$\pi$-microscopy
+\cite{Hell1994} or structured illumination microscopy (SIM)
+\cite{Guerra1995}. The first uses two objectives on opposite sides of the
+sample, which renders it impossible to be combined with SICM since the space
+required for the scanning pipette is already occupied by the second
+objective. In contrast, SIM is implemented on a wide-field microscope and
+could thus be combined with SICM. Therefore, combining SIM and SICM is similar
+to combining SICM with other wide-field based techniques (see
+section~\ref{sec:smlm}). Since the gain in resolution is low compared with the
+approaches explained in sections~\ref{sec:smlm}
+and~\ref{sec:deterministic-approaches}, we refrain from explaining SIM in
+detail here.
+
+\subsubsection{Stochastic approaches}
+\label{sec:smlm}
+The stochastic approaches to SRFM use dye molecules which can be switched
+between an inactivated (``off'') and an activated (``on'') state by light of a
+specific wavelength. If only a sparse subset of molecules is activated, such
+that, on average, only one dye molecule per diffraction limited spot emits,
+the position of the emitting molecule can be localised with much better
+precision than the diffraction limit. If this is repeated until all
+fluorophores have emitted, plotting the positions instead of the emission of
+all fluorophores yields an image with resolution beyond the diffraction
+limit (localisation microscopy). The first techniques using this principle
+were photo-activated localisation microscopy (PALM) \cite{Betzig2006} (using
+the Eos fluorescent protein \cite{Wiedenmann2004} as marker), fluorescence
+photo-activation localisation microscopy (FPALM) \cite{Hess2006} (using
+photo-activatable GFP as marker), and stochastical
+optical reconstruction microscopy (STORM) \cite{Rust2006} (using Cy5 and Cy3
+dyes).
+
+\begin{figure}
+  \centering
+  \includegraphics{gr/intro/localisation-mic}
+  \caption{}
+  \label{fig:lm}
+\end{figure}
+
+The principle of these methods is illustrated in
+Fig.~\ref{fig:lm}. Initially, all fluorophores within the sample are
+inactivated (``off''-state, grey dots in Fig.~\ref{fig:lm}a). After applying light suitable to switch the fluorophores
+(cyan background, Fig.~\ref{fig:lm}b) from the inactivated to
+the activated (``on'') state (white dots), the activated molecules are excited
+(green background, yellow dots) and their emission is recorded. The excitation
+light is applied as long as all excited molecules have bleached (black
+dots). The series of activation, excitation and read-out is repeated until all
+fluorophores have been excited and bleached, which results in a set of images
+containing diffraction limited emission spots of all fluorophores in the
+sample.
+
+In a post-processing step (Fig.~\ref{fig:lm}c), the positions of the
+fluorophores are determined by fitting (an approximation of) the instrument's
+point spread function to the data. The positions are plotted as Gaussian
+distributions with a standard deviation equal to the uncertainty of the
+determination of the position by the fit, finally yielding an image with an
+improved resolution (Fig.~\ref{fig:lm}c, right).
+
+The resolution provided by this approach scales with the number of photons $N$
+that are detected and theoretically is given by $\sigma_\text{PSF}/\sqrt{N}$
+(with $\sigma_\text{PSF}$ denoting the standard deviation of the point spread
+function of the microscope, which is in the range of 100\,nm). However, in
+practice the resolution is range of 20\,nm \cite{Betzig2006} since the
+theoretical resolution cannot be reached due to background, noise and other
+factors. A more detailed description of the resolution enhancement by
+localisation is provided by \cite{Mortensen2010}.
+
+\subsubsection{Deterministic approaches}
+\label{sec:deterministic-approaches}
+
+% The first concept to circumvent the diffraction limit was published in 1994
+% and realised in 2000 \cite{hell+wichmann,Klar2000}
 
@@
 
-\subsection{Camera-based techniques}
-
 \subsection{Scanning techniques}

### 2020-09-22 sections/pitfalls.tex
There is no Shevchuk.2013 in the bib file, but Shevchuk2013 is

@@
 reported to have caused cross-talk during sample positioning leading to image
-artifacts in the range of 100 nm \cite{Shevchuk.2013}. Hence, it would be
+artifacts in the range of 100 nm \cite{Shevchuk2013}. Hence, it would be
 better to uncouple xy piezos from the z piezo. Furthermore, z piezos come with
@@
 using a v-groove mounting plate for the capillary instead of the conventional
-patch clamp pipette holders \cite{Shevchuk.2013}.
+patch clamp pipette holders \cite{Shevchuk2013}.
 

### 2020-09-23 sections/srfm.tex
some closing remarks on the section of SMLM.

@@
 function of the microscope, which is in the range of 100\,nm). However, in
-practice the resolution is range of 20\,nm \cite{Betzig2006} since the
-theoretical resolution cannot be reached due to background, noise and other
-factors. A more detailed description of the resolution enhancement by
-localisation is provided by \cite{Mortensen2010}.
+practice the resolution is in the range of 20\,nm \cite{Betzig2006,Rust2006}
+since the theoretical resolution cannot be reached due to background, noise
+and other factors. A more detailed description of the resolution enhancement
+by localisation is provided by \cite{Mortensen2010}.
 
+This brief explanation is far from being exhaustive and does not consider the
+differences in the implementations of the various techniques. An in-depth
+overview is provided by several reviews of the techniques
+\cite{Sengupta2014,Liu2015,Sauer2017}, suitable dyes \cite{Li2018a} as well
+as by detailed imaging protocols \cite{Gould2009,Schermelleh2010,Linde2011}.
 \subsubsection{Deterministic approaches}

### 2020-09-23 sections/srfm.tex
tiny update

@@
 Fig.~\ref{fig:lm}. Initially, all fluorophores within the sample are
-inactivated (``off''-state, grey dots in Fig.~\ref{fig:lm}a). After applying light suitable to switch the fluorophores
+inactivated (``off''-state, grey dots in Fig.~\ref{fig:lm}a). Next,  light suitable to switch the fluorophores
 (cyan background, Fig.~\ref{fig:lm}b) from the inactivated to
-the activated (``on'') state (white dots), the activated molecules are excited
+the activated (``on'') state (white dots) is applied. The intensity of the
+activation light is selected such that only a small subset of the inactivated
+molecules is activated, at maximum one molecule per area of the diffraction limited spot. The activated molecules are excited
 (green background, yellow dots) and their emission is recorded. The excitation
@@
 overview is provided by several reviews of the techniques
-\cite{Sengupta2014,Liu2015,Sauer2017}, suitable dyes \cite{Li2018a} as well
+\cite{Patterson2010,Sengupta2014,Liu2015,Sauer2017}, suitable dyes \cite{Li2018a} as well
 as by detailed imaging protocols \cite{Gould2009,Schermelleh2010,Linde2011}.
+
 \subsubsection{Deterministic approaches}
@@
 
-\subsection{General approach}
+% \subsection{General approach}
 
-\subsubsection{Different approaches}
-While the majority of SRFM techniques follows the approach outlined above,
-other techniques exist that use different approaches.
+% \subsubsection{Different approaches}
+% While the majority of SRFM techniques follows the approach outlined above,
+% other techniques exist that use different approaches.
 
-\subsection{Scanning techniques}
+% \subsection{Scanning techniques}
+
 %%% Local Variables:

### 2020-09-25 sections/srfm.tex
figure for sted principle

@@
 
+\begin{figure}
+  \centering
+  \includegraphics{gr/intro/direct-SR-mic}
+  \caption{\textbf{Principle of STED microscopy.} \textbf{a:} Shape of
+    excitation and ring-shaped depletion beam. \textbf{b:} The two beams are
+    superimposed and the sample is scanned. Fluorophores in the center are
+    excited and emit spontaneously (yellow dot), while the depletion beam
+    induces stimulated emission of the fluorophores in the periphery (black
+    dots). \textbf{c:} Jablonski diagram of stimulated emission (SE, left) and
+    wavelengths of excitation (ex), detection (det) and stimulated emission
+    (SE) superimposed on the absorbance/emission spectrum of a fluorescent dye
+    (right).}
+\end{figure}
 % The first concept to circumvent the diffraction limit was published in 1994

### 2020-09-26 sections/correlated-sicm-and-fm.tex
first commit
Update correlated-sicm-and-fm.tex

--- 2020-02-21 sections/pitfalls.tex
@@
-\section{Potential Pitfalls}
-\label{sec:pitfalls}
+\section{Correlating SICM and Fluorescence Microscopy}
+\label{sec:correlating-sicm-and-fm}
 %%% Local Variables:
@@
 %%% End:
+Nevertheless SICM does not necessary being used for investigating the topography of a cell, the nanopipette of a SICMic could be also used for the gezielte %german word! 
+deposition of molecules, like fluorescently-labeled single stranded-DNA molecules \cite(Ying2002,Hennig2015).
+The nanopipette could be also used for nanoinjection of fluorescently labeled molecules into living cells \cite(Hennig2015_nanoinj).
+The SICM was therefore combined with wide-field and dSTORM microscopy, and mitochondria, actin and DNA could be successfully stained.
+One problem with the nanoinjection was that artifacts, due to the holes that were introduced into the membranes, could occur \cite(Hennig2015_nanoinj).

### 2020-09-26 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 %%% End:
-Nevertheless SICM does not necessary being used for investigating the topography of a cell, the nanopipette of a SICMic could be also used for the gezielte %german word! 
-deposition of molecules, like fluorescently-labeled single stranded-DNA molecules \cite(Ying2002,Hennig2015).
-The nanopipette could be also used for nanoinjection of fluorescently labeled molecules into living cells \cite(Hennig2015_nanoinj).
-The SICM was therefore combined with wide-field and dSTORM microscopy, and mitochondria, actin and DNA could be successfully stained.
-One problem with the nanoinjection was that artifacts, due to the holes that were introduced into the membranes, could occur \cite(Hennig2015_nanoinj).
+Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
+the nanopipette of a SICMic could be also used for the gezielte %german word! 
+deposition of molecules, like fluorescently-labeled single stranded-DNA molecules 
+\cite{Ying2002,Hennig2015}. The nanopipette could be also used for nanoinjection 
+of fluorescently labeled molecules into living cells \cite{Hennig2015_nanoinj}. 
+The SICM was therefore combined with wide-field and dSTORM microscopy, and mitochondria, 
+actin and DNA could be successfully stained. One problem with the nanoinjection was that 
+artifacts, due to the holes that were introduced into the membranes, could occur \cite{Hennig2015_nanoinj}.
+
+SICM in combination with F\"orster resonance energy transfer (FRET) sensors % could be used for
+the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors \cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} in healthy and impaired cardiomyocytes.
+The binding of a

### 2020-09-26 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 
-SICM in combination with F\"orster resonance energy transfer (FRET) sensors % could be used for
-the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors \cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} in healthy and impaired cardiomyocytes.
-The binding of a
+SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
+the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors \cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} 
+and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} in healthy and impaired cardiomyocytes. After measuring the 
+topography with SICM the nanopipette could be moved to

### 2020-09-26 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
-the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors \cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} 
-and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} in healthy and impaired cardiomyocytes. After measuring the 
+the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
+\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} 
+in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. After measuring the 
 topography with SICM the nanopipette could be moved to

### 2020-09-26 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. After measuring the 
-topography with SICM the nanopipette could be moved to
+topography (SICM) the nanopipette could be moved to places - e.g. the z-grooves of the cell 
+\cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} - where the adrenoceptor distribution 
+should be investigated. Then the pipette could be used for stimulating the receptor to procuce 
+cAMP oder cGMP \cite{Xiang2003}, this could bind to the FRET sensor, which changes 
+its conformation and a FRET signal could be detected \cite{Nikolaev2010}.

### 2020-09-26 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 should be investigated. Then the pipette could be used for stimulating the receptor to procuce 
-cAMP oder cGMP \cite{Xiang2003}, this could bind to the FRET sensor, which changes 
+cAMP oder cGMP \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes 
 its conformation and a FRET signal could be detected \cite{Nikolaev2010}.

### 2020-09-26 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 %%% End:
+Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
+which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
+This is especially helpful for applications, where the reaction is not limited to one Untersuchungsobjekt, %german
+for example when investigating the uptake of nanoparticles into cells. There it would be interesting to
+untersuchen, sowohl %german
+the cell membrane with a technique, which is able to do so $–$ AFM \cite{}, EM \cite{}, SICM \cite{Hansma1989} $-$, 
+als auch %german
+to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
+react on the Zugabe %german
+of the nanoparticle by using fluorescence microscopy methods.
+
+% Den Teil brauchen wir ja vielleicht nicht. 
+AFM, a method belonging to the scanning probe microscopy techniques, was successfully
+combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
+cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
+with this method is, that it is not the most favorable for investigating living cells in their
+physiological surrounding. Certain destructive effects on the cell were found by using this 
+technique \cite{}. A better fitting method for investigating living cells would be scanning 
+ion conductance microscopy (SICM) \cite{Hansma1989}.
+
+% Hier jetzt der surface confocal scanning part, NP investigation part usw. (damit warte ich aber, bis ich weiß, wie das
+% richtig eingefügt wird.
+
 Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
@@
 in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. After measuring the 
-topography (SICM) the nanopipette could be moved to places - e.g. the z-grooves of the cell 
-\cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} - where the adrenoceptor distribution 
+topography (SICM) the nanopipette could be moved to places $-$ e.g. the z-grooves of the cell 
+\cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} $-$ where the adrenoceptor distribution 
 should be investigated. Then the pipette could be used for stimulating the receptor to procuce 

### 2020-09-27 sections/srfm.tex
a few sentences on STED

@@
 overview is provided by several reviews of the techniques
-\cite{Patterson2010,Sengupta2014,Liu2015,Sauer2017}, suitable dyes \cite{Li2018a} as well
-as by detailed imaging protocols \cite{Gould2009,Schermelleh2010,Linde2011}.
+\cite{Patterson2010,Sengupta2014,Liu2015,Sauer2017}, suitable dyes
+\cite{Li2018a} as well as by detailed imaging protocols
+\cite{Gould2009,Schermelleh2010,Linde2011}. However, one aspect of the
+implementation which is important for the potential combination with SICM is
+the illumination scheme used by these methods. Since wide-field illumination
+is required to record the emission of the activated fluorophores, out-of-focus
+emission occurs, which increases the background in the recordings and affects
+the resolution. To avoid this, a total internal reflection (TIRF) illumination
+scheme \cite{AMBROSE1956,Axelrod1981} is used, which limits the excitation to
+the layer close to the interface of the microscopy slide and the sample.
 
@@
 \label{sec:deterministic-approaches}
+In contrast to the stochastic approaches, which switch the fluorophores
+randomly in space, the deterministic approaches use a single-spot illumination
+and switch the fluorophores in the periphery of the excitation spot. The
+underlying principle is called reversible saturable optical fluorescence
+transitions (RESOLFT). Methods that use this principle are stimulated emission
+depletion (STED) microscopy \cite{hell+wichmann,Klar2000}, ground state
+depletion (GSD) microscopy \cite{Hell1995,Bretschneider2007} and RESOLFT with
+photo-switchable proteins \cite{Hofmann2005}. The latter is often referred to
+as RESOLFT microscopy, although STED and GSD use the RESOLFT principle, too.
 
@@
     induces stimulated emission of the fluorophores in the periphery (black
-    dots). \textbf{c:} Jablonski diagram of stimulated emission (SE, left) and
-    wavelengths of excitation (ex), detection (det) and stimulated emission
-    (SE) superimposed on the absorbance/emission spectrum of a fluorescent dye
-    (right).}
+    dots). \textbf{c:} (left) Line profile of the intensity of the depletion
+    beam (red) and probability to induce stimulated emission (black); (center)
+    Jablonski diagram of stimulated emission (SE); (right) wavelengths of
+    excitation (ex), detection (det) and stimulated emission (SE) superimposed
+    on the absorbance/emission spectrum of a fluorescent dye.}
+  \label{fig:STED-principle}
 \end{figure}
+
+As an example for RESOLFT, the principle of STED microscopy is sketched in
+Fig.~\ref{fig:STED-principle}. The excitation spot
+(Fig.~\ref{fig:STED-principle}a, top) is superimposed with a second, ring- or
+doughnut-shaped spot (Fig.~\ref{fig:STED-principle}a, bottom). The
+fluorophores are excited by the excitation light, but only those located in
+the center of the minimum of the depletion beam are allowed to emit
+spontaneously (yellow dot). The fluorophores at the periphery are de-excited
+by the depletion and undergo stimulated emission (black dots).
+
 % The first concept to circumvent the diffraction limit was published in 1994

### 2020-09-27 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
-This is especially helpful for applications, where the reaction is not limited to one Untersuchungsobjekt, %german
-for example when investigating the uptake of nanoparticles into cells. There it would be interesting to
-untersuchen, sowohl %german
-the cell membrane with a technique, which is able to do so $–$ AFM \cite{}, EM \cite{}, SICM \cite{Hansma1989} $-$, 
-als auch %german
+This is especially helpful for applications, where the reaction is not limited to \emph{one 
+dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
+be interesting to investigate, sowohl %german
+the cell membrane with a technique, which is able to do so $–$ AFM \cite{}, EM \cite{}, SICM 
+\cite{Hansma1989} $-$, als auch %german
 to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
-react on the Zugabe %german
-of the nanoparticle by using fluorescence microscopy methods.
+react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.
 
@@
 
-% Hier jetzt der surface confocal scanning part, NP investigation part usw. (damit warte ich aber, bis ich weiß, wie das
-% richtig eingefügt wird.
+% Hier jetzt der surface confocal scanning part, NP investigation part usw. (damit warte ich aber,
+% bis ich weiß, wie das richtig eingefügt wird.
+
+Topographical information obtained by SICM were successfully correlated with fluorescence signals
+of stained cytoskeleton molecules obtained by laser scanning confocal microscopy in platelets 
+\cite{Seifert2017}.
+
+In addition, hippocampal neurons, which were very delicate samples with many little protrusions, 
+could be investigated with correlated SICM and confocal microscopy. With such a combination active
+synaptic boutons could be identified \cite{Novak2013} or the topography could be correlated with 
+the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2020}.
+
+Another very delicate sample, because of their three-dimensional, upright (?) structure are cilia.
+Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
+distinguish between surface and sub-surface cilia, which could not be detected with SICM 
+\cite{Zhou2018}.
+
+Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
+scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
+simultaneously and $-$ because fluorescence signals should be investigated, which were originated
+from particles at or near to the surface of the cell $-$ it was important to keep the distance 
+between the sample and the pipette constant. In that study the SSCM was used for investigating the 
+dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
+The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
+(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
+cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.
+
+% Hier jetzt noch den Abschnitt über Bednarska2020 einfügen (anderer PC)
+
+SSCM could be also used for investigating endocytotic pathways \cite{Shevchuk2008}. In a study 
+investigating topography together with actin-binding protein-green fluorescent protein (Abp1-GFP)
+and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) an alternative closing 
+mechanism for clathrin-coated pits (CCPs) \cite{Shevchuk2012}. In another study the uptake of
+200~nm fluorescent, carboxylated latex particles into immortalized human alveolar epithelial type
+1-like (AT1) cells was investigated. Additional to the fluorescence signal of the nanoparticle the 
+fluorescence signal of actin-binding protein-green fluorescent protein (Abp1-GFP) and clathrin
+light-chain-enhanced green fluorescent protein (Clc-EGFP) were detected. Both, actin, as part of
+the cytoskeleton (Quelle), and clathrin, as one important actor of endocytosis (Quelle), give 
+interesting Zusatzinformationen on how the nanoparticle is taken up into the cell 
+\cite{Novak2014}.
+
+The study of Nashimoto was showing that for the detection of secretory proteins, like the von 
+Willebrand factor, it is not always necessary to label the protein. Even with SICM alone the 
+detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
+images \cite{Nashimoto2015}.
 
 Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
-the nanopipette of a SICMic could be also used for the gezielte %german word! 
-deposition of molecules, like fluorescently-labeled single stranded-DNA molecules 
-\cite{Ying2002,Hennig2015}. The nanopipette could be also used for nanoinjection 
-of fluorescently labeled molecules into living cells \cite{Hennig2015_nanoinj}. 
-The SICM was therefore combined with wide-field and dSTORM microscopy, and mitochondria, 
-actin and DNA could be successfully stained. One problem with the nanoinjection was that 
-artifacts, due to the holes that were introduced into the membranes, could occur \cite{Hennig2015_nanoinj}.
+the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
+fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
+could be also used for nanoinjection of fluorescently labeled molecules into living cells 
+\cite{Hennig2015_nanoinj}. The SICM was therefore combined with wide-field and dSTORM microscopy, 
+and mitochondria, actin and DNA could be successfully stained. One problem with the nanoinjection 
+was that artifacts, due to the holes that were introduced into the membranes, could occur 
+\cite{Hennig2015_nanoinj}.
+
+The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
+combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
+In both studies the scanning ion conductance microscope was combined with total internal 
+reflection fluorescence (TIRF) investigations and the diffusion of single molecules over different 
+regions at a spermatozoa were investigated.
 
@@
 the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
-\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors \cite{Schobesberger2020} 
-in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. After measuring the 
-topography (SICM) the nanopipette could be moved to places $-$ e.g. the z-grooves of the cell 
-\cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} $-$ where the adrenoceptor distribution 
-should be investigated. Then the pipette could be used for stimulating the receptor to procuce 
-cAMP oder cGMP \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes 
-its conformation and a FRET signal could be detected \cite{Nikolaev2010}.
+\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors 
+\cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
+After measuring the topography (SICM) the nanopipette could be moved to places $-$ e.g. the 
+z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} $-$ where the 
+adrenoceptor distribution should be investigated. Then the pipette could be used for stimulating 
+the receptor to produce cyclic adenosine monophosphate (cAMP) or cyclic guanosine monophosphate 
+(cGMP) \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes its 
+conformation and a FRET signal could be detected \cite{Nikolaev2010}.
+
+The SICM-nanopipette could be also used for investigating membrane rafts (Quelle) by coordinated 
+manipulation of focal adhesions. The pipette was functionalized with fibronectin, gangliosides
+were fluorescently labeled, the pipette deformed the focal adhesion side and the behavior of the 
+fluorescently labeled gangliosides were detected. This was seen as a hint, how membrane rafts 
+reacted \cite{Fuentes2012}.
+
+Another example for a SICM-nanopipette based manipulation could be found in the study on the 
+generation and distribution of plasma-derived extracellular vesicles (PEVs) on MDA-MB-231 and U87 
+cells. Here the nanopipette were used for both, investigating the topography and for inducing the 
+generation of the PEVs. Additionally the SICM was build up onto a confocal microscope, which could 
+be used for the detection of Calcium \cite{Wang2020}.
+
+% Dieser Abschnitt passt nicht so wirklich zu Fluoreszenz-Mikroskopie! Vielleicht noch so was 
+% schreiben, wie „SICM kann nicht nur mit Fluoreszenz mikroskopischen Methoden kombiniert werden, 
+% sondern kann auch mit … kombiniert werden!? Sonst kann der einfach auch weg. Mal gucken.
+
+By using a special illumination system consisting of a light emitting diode (LED) light ring, SICM 
+could also being combined with condenser-free phase contrast, darkfield and brightfield images and 
+even Rheinberg illuminations were possible \cite{Webb2015}.

### 2020-09-28 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 
-% Hier jetzt noch den Abschnitt über Bednarska2020 einfügen (anderer PC)
+In a study investigating the formation of human immunodeficiency virus (HIV) VLPs the correlated
+SICM-fluorescence confocal microscopy (SICM-FCM) was used to investigate topography changes
+together with die distribution of fluorescently labeled viral proteins like Gag or Viral Protein R 
+(Vpr) \cite{Bednarska2020}. In contrast of investigating the virus formation with total internal 
+reflection fluorescence (TIRF) microscopy \cite{Jouvenet2008} the upside (Oberseite?) of the cells 
+were investigated. The release of VLPs from the upside can be a lot faster, than the release times 
+that were known from TIRF measurements and difference between different cell types and labeled 
+virus proteins were found \cite{Bednarska2020}.
 
@@
 combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
-In both studies the scanning ion conductance microscope was combined with total internal 
-reflection fluorescence (TIRF) investigations and the diffusion of single molecules over different 
-regions at a spermatozoa were investigated.
+In both studies the scanning ion conductance microscope was combined with TIRF investigations and 
+the diffusion of single molecules over different regions at a spermatozoa were investigated.
 

### 2020-09-28 sections/correlated-sicm-and-srfm.tex
first commit
Update correlated-sicm-and-srfm.tex

--- 2020-02-21 sections/pitfalls.tex
@@
-\section{Potential Pitfalls}
-\label{sec:pitfalls}
+\section{Correlating SICM and Super-Resolved Fluorescence Microscopy}
+\label{sec:correlating-sicm-and-srfm}
 %%% Local Variables:
@@
 %%% End:
+
+For resolving tiny structures like single cytoskeleton fibers, nanoparticle, with sizes smaller
+than the diffraction-limit, or protein complexes, it would be helpful to use microscopy
+techniques, which can resolve structures beyond the diffraction limit.
+
+One of that techniques is STED microscopy (see section~\ref{sec:deterministic-approaches}). In a 
+proof-of-principle study the topography of a group of fixed HeLa cells together with the 
+distribution of actin filaments was investigated \cite{Hagemann2018}. Although both methods were 
+able to investigate living cells, the cells needs to be fixed in that study, because the 
+investigation was consecutively done onto two microscopes. The topography was measured with SICM 
+and the distribution of actin with STED microscopy (see figure~\ref{fig:SICM_STED1}).
+
+% Hier soll jetzt Figure 4 unserer ACSNano-Publikation folgen. Patrick, du hast doch die 
+% Ursprungs-/Original-PDF-Version davon, oder? Kannst du die dann bitte hier einfügen und 
+% natürlich gucken, dass wir die Rechte dafür bekommen (das wolltest du ja machen, damit wir das 
+% alles in einem Dokument haben).
+
+\begin{figure}	
+  \centering
+    \includegraphics[clip,scale=1]{.PDF} % @Patrick hier bitte den Filename eintragen
+      \caption{
+      \textbf{Correlative SICM and STED recording of a group of HeLa cells.} 
+      (\textbf{Aa}) SICM recording of the HeLa cells, (\textbf{Ab}) slope representation of the
+      SICM recording. Confocal (\textbf{Ba}) and STED (\textbf{Bb}) recording of the region marked 
+      with a black dotted line in \textbf{Aa} and \textbf{Ab}. (\textbf{C}) Relative position of 
+      the SICM (yellow rectangle) and the confocal/STED (gray rectangle) images against each 
+      other. Magnification of the STED (\textbf{Da}), confocal (\textbf{Db}), SICM (\textbf{Dd}) 
+      and slope (\textbf{De}) images. The region, that is magnified, is marked with a white 
+      arrowhead in \textbf{Aa, Ab, Ac and Ad}. (\textbf{Df} and (\textbf{Dg}) show an overlay of 
+      the STED with the SICM (\textbf{Df}) or the slope representation (\textbf{Dg}). 
+      (\textbf{Dc}) Height profile along the white dotted line in \textbf{Dd}. \newline Reprinted 
+      with permission from \emph{Philipp Hagemann*, Astrid Gesper*, Patrick Happel}, Correlative 
+      stimulated emission depletion and scanning ion conductance microscopy, \emph{ACS Nano} 2018, 
+      12, 5807-5815, DOI: 10.1021/acsnano.8b01731. Copyright 2020 American Chemical Society}
+  \label{fig:SICM_STED1}
+\end{figure}

### 2020-09-29 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 even Rheinberg illuminations were possible \cite{Webb2015}.
+
+% Abschnitt weitere Korrelationen (indirekte)
+
+Beside these more or less \emph{direct} combinations and correlations, which are displaying images 
+obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
+correlations exist. They are showing images under comparable conditions and extent the 
+investigation to aspects, which could not be obtained by using one technique alone. Such 
+\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
+nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
+Nichtsdestotrotz (german)
+is it important to mention, that they could just giving hints of correlations, it 
+is not directly comparable with investigations of both in the same cell.

### 2020-09-29 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

@@
 
-One of that techniques is STED microscopy (see section~\ref{sec:deterministic-approaches}). In a 
-proof-of-principle study the topography of a group of fixed HeLa cells together with the 
-distribution of actin filaments was investigated \cite{Hagemann2018}. Although both methods were 
-able to investigate living cells, the cells needs to be fixed in that study, because the 
-investigation was consecutively done onto two microscopes. The topography was measured with SICM 
-and the distribution of actin with STED microscopy (see figure~\ref{fig:SICM_STED1}).
+% Hier füge ich jetzt einen Abschnitt zum diffraction limit ein. Ich habe gesehen das du (Patrick) 
+% das in deiner SRFM-Einleitung nur im Kommentar eingefügt hattest.
+
+The diffraction limit was defined by Ernst Abbe in 1873 \cite{Abbe1873} and could be described 
+with the following equation.
+
+\begin{equation}
+d = \frac{\lambda}{2 n \sin{\alpha}}
+\label{eq:Abbe_diff}
+\end{equation}
+
+In this equation $\lambda$ is the wavelength of light, $n$ the Brechungsindex (german) of the 
+medium between objective and sample and $\alpha$ is half the opening Winkel (german) of the 
+objective. Following this equation and under ideal conditions, the limit for structures, that 
+could be resolved, would be halftimes the wavelength.
+
+One of that techniques, that can resolve structures beyond the diffraction limit, is STED 
+microscopy (see section~\ref{sec:deterministic-approaches}). In a proof-of-principle study the 
+topography of a group of fixed HeLa cells together with the distribution of actin filaments was
+investigated \cite{Hagemann2018}. Although both methods were able to investigate living cells, the 
+cells were fixed in that study, because the investigation was done consecutively onto two 
+microscopes. The topography was measured with SICM and the distribution of actin with STED 
+microscopy (see figure~\ref{fig:SICM_STED1}).
 

### 2020-09-29 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

--- 2020-09-28 sections/correlated-sicm-and-srfm.tex
@@
 than the diffraction-limit, or protein complexes, it would be helpful to use microscopy
-techniques, which can resolve structures beyond the diffraction limit.
+techniques, which can resolve structures beyond the diffraction limit of light (see 
+equation~\ref{eq:diffraction-limit}; \cite{Abbe1873}).
 
-One of that techniques is STED microscopy (see section~\ref{sec:deterministic-approaches}). In a 
-proof-of-principle study the topography of a group of fixed HeLa cells together with the 
-distribution of actin filaments was investigated \cite{Hagemann2018}. Although both methods were 
-able to investigate living cells, the cells needs to be fixed in that study, because the 
-investigation was consecutively done onto two microscopes. The topography was measured with SICM 
-and the distribution of actin with STED microscopy (see figure~\ref{fig:SICM_STED1}).
+% Hier vielleicht auch noch Fig. 3 aus der ACSNano-Publikation einfügen??? Würde vielleicht ganz
+% gut passen!?
+
+One of that techniques, that can resolve structures beyond the diffraction limit, is STED 
+microscopy (see section~\ref{sec:deterministic-approaches}). In a proof-of-principle study the 
+topography of a group of fixed HeLa cells together with the distribution of actin filaments was
+investigated \cite{Hagemann2018}. Although both methods were able to investigate living cells, the 
+cells were fixed in that study, because the investigation was done consecutively onto two 
+microscopes. The topography was measured with SICM and the distribution of actin with STED 
+microscopy (see figure~\ref{fig:SICM_STED1}).
 
@@
 \end{figure}
+
+The topography of a group of more than four fixed HeLa cells can be seen in 
+figure~\ref{fig:SICM_STED1}Aa the corresponding slope representation in Ab, the confocal image in 
+Ac and the STED image in Ad. The confocal and STED image represents the same region as marked with 
+a black dotted line in Aa and Ab. Many different cell topographies were visible in Aa.
+
+A round cell with a maximum height of approximately 16.4~{\textmu}m height can be seen in the 
+right upper region of the image (marked with a purple arrow in Aa/Ab/Ac/Ad). The cell next to this 
+was flat and extending (?) the scanned region (yellow arrow). A second flat but smaller cell was 
+marked with a with arrow ending with a white dot. Marked with a purple arrow ending with a purple
+dot was a small and a kind of roundish cells. This cell besitzt (german)
+a protrusion (white arrowhead), those magnification could be seen in Dd/Df respectively in De/Dg. 
+The protrusion was approximately 4~{\textmu}m long and 5~{\textmu}m high (Dc, 
+\cite{Hagemann2018}).
+
+Beside the different topographies of these two cells, they also display different types of actin 
+fibres. In the inside of the first mentioned round cell nearly no actin signal could be detected 
+(some dot-like structures were marked with purple arrowheads), whereas at the borders of the cell 
+some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
+fibres (yellow arrowheads).

### 2020-09-30 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

@@
 some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
-fibres (yellow arrowheads).
+fibres (yellow arrowheads). The cell marked with the white arrow, that was ending with a white 
+dot, could be just seen half in the confocal/STED images and dot-like actin structures 
+predominate.
+
+Structures that would have been missed by using one single technique alone: 
+\textsf{
+\begin{tabular}[c]{p{6cm}|p{3cm}|p{3.75cm}}
+\label{tab:missing_structures}
+What? & visible in fig.~\ref{fig:SICM_STED1} by SICM & visible in fig.~\ref{fig:SICM_STED1} by STED microscopy \\ \hline
+The full extend of the protrusion & YES & \textbf{NO} \\ \hline
+The connection between the roundish and the flat cell & \textbf{NO} & YES \\
+\end{tabular}}

### 2020-09-30 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

--- 2020-09-29 sections/correlated-sicm-and-srfm.tex
@@
 Ac and the STED image in Ad. The confocal and STED image represents the same region as marked with 
-a black dotted line in Aa and Ab. Many different cell topographies were visible in Aa.
+a black dotted line in Aa and Ab. C is showing the arrangement of the SICM image (yellow 
+rectangle) against the confocal/STED image (gray rectangle). Many different cell topographies were
+visible in Aa.
 
@@
 right upper region of the image (marked with a purple arrow in Aa/Ab/Ac/Ad). The cell next to this 
-was flat and extending (?) the scanned region (yellow arrow). A second flat but smaller cell was 
-marked with a with arrow ending with a white dot. Marked with a purple arrow ending with a purple
-dot was a small and a kind of roundish cells. This cell besitzt (german)
+was flat and exceeding the scanned region (yellow arrow). A second flat but smaller cell was 
+marked with a white arrow, which was ending with a white dot. Marked with an orange arrow (Aa, Ab) 
+respectively with a cyan arrow (Ba, Bb) was a small, kind of roundish cells. This cell posesses 
 a protrusion (white arrowhead), those magnification could be seen in Dd/Df respectively in De/Dg. 
@@
 Beside the different topographies of these two cells, they also display different types of actin 
-fibres. In the inside of the first mentioned round cell nearly no actin signal could be detected 
+fibers. In the inside of the first mentioned round cell nearly no actin signal could be detected 
 (some dot-like structures were marked with purple arrowheads), whereas at the borders of the cell 
 some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
-fibres (yellow arrowheads).
+fibers (yellow arrowheads). The cell marked with the white arrow, which was ending with a white 
+dot, could be just seen half in the confocal/STED images and dot-like actin structures 
+predominate. The cell with the protrusion was showing fan-like actin structures (cyan arrow, which
+was ending with a cyan dot and white arrow, which was ending with a white dot) where the cell was
+connected to surrounding cells and actin agglomerations (cyan arrow). The agglomerations turned 
+out to be \emph{rings} by watching the STED image (cyan circle). Such a structure could be also 
+found in the protrusion (white arrowhead, Df and Dg). In the center of the \emph{actin ring} two 
+dots could be identified (black arrowheads, Da).
+
+Structures that would have been missed, if just one single technique alone would have been used: 
+\textsf{
+\begin{tabular}[c]{p{6cm}|p{3cm}|p{3.75cm}}
+\label{tab:missing_structures}
+What? & visible in fig.~\ref{fig:SICM_STED1} by SICM & visible in fig.~\ref{fig:SICM_STED1} by STED microscopy \\ \hline
+The connections between the small round cell with the protrusion and the other cells & \textbf{PARTLY} & YES \\ \hline
+The full extent of the protrusion & YES & \textbf{NO} \\ \hline
+The connection between the roundish and the flat cell & \textbf{NO} & YES \\
+\end{tabular}}
+
+This points out again one of the biggest advantage of correlative microscopy: making things 
+visible, that were invisible to one of the microscopy techniques alone. This could be due to 
+fluorescence signals that were out of focus $-$ this could be the case by the actin signal that
+suddenly ends in the protrusion $-$ (STED microscopy) or due to overhanging membranes $-$ this 
+could be the case by the connections between the cells (especially between the highest and the
+flat cell) $-$ (SICM) (Quelle).

### 2020-10-01 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

@@
 
-Structures that would have been missed, if just one single technique alone would have been used: 
+Structures that would have been missed and/or could have been misinterpreted, if just one single
+technique alone would have been used: 
 \textsf{
@@
 flat cell) $-$ (SICM) (Quelle).
+
+As mentioned in section~\ref{}, SICM was also successfully combined with dSTORM (see 
+section~\ref{sec:deterministic-approaches}) \cite{Hennig2015_nanoinj}. The difference to the 
+SICM/STED microscopy correlation study was, that the SICM was there used for nanoinjecting 
+fluorescently labeled molecules $-$ ATTO 655-phalloidin $-$ into living U2OS cells.
+
+% Hier jetzt noch was zu SICM/SNOM!

### 2020-10-01 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

--- 2020-09-30 sections/correlated-sicm-and-srfm.tex
@@
 flat cell) $-$ (SICM) (Quelle).
+
+As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
+with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015_nanoinj}. The difference to the 
+SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
+fluorescently labeled molecules $-$ ATTO 655-phalloidin $-$ into living U2OS cells.
+
+% Hier jetzt noch was zu SICM/SNOM!

### 2020-10-01 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 could be also used for nanoinjection of fluorescently labeled molecules into living cells 
-\cite{Hennig2015_nanoinj}. The SICM was therefore combined with wide-field and dSTORM microscopy, 
-and mitochondria, actin and DNA could be successfully stained. One problem with the nanoinjection 
-was that artifacts, due to the holes that were introduced into the membranes, could occur 
-\cite{Hennig2015_nanoinj}.
+\cite{Hennig2015_nanoinj}. The SICM was therefore combined with wide-field and direct stochastic 
+optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
+stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
+introduced into the membranes, could occur \cite{Hennig2015_nanoinj}.
 

### 2020-10-02 sections/srfm.tex
complete section on deterministic approaches

@@
     induces stimulated emission of the fluorophores in the periphery (black
-    dots). \textbf{c:} (left) Line profile of the intensity of the depletion
-    beam (red) and probability to induce stimulated emission (black); (center)
-    Jablonski diagram of stimulated emission (SE); (right) wavelengths of
-    excitation (ex), detection (det) and stimulated emission (SE) superimposed
-    on the absorbance/emission spectrum of a fluorescent dye.}
+    dots). \textbf{c:} (left) Jablonski diagram of stimulated emission (SE);
+    (center) Line profile of the intensity of the depletion beam (red) and
+    probability (prob) to induce stimulated emission (black); (right)
+    wavelengths of excitation (ex), detection (det) and stimulated emission
+    (SE) superimposed on the absorbance/emission spectrum of a fluorescent
+    dye.}
   \label{fig:STED-principle}
@@
 spontaneously (yellow dot). The fluorophores at the periphery are de-excited
-by the depletion and undergo stimulated emission (black dots).
+by the depletion beam and undergo stimulated emission (black dots). The
+Jablonski diagram of stimulated emission is shown in
+Fig.~\ref{fig:STED-principle}c (left). An incoming photon of the depletion
+beam interacts with the excited fluorophore and causes it to de-excite to the
+ground state and to emit a photon of the same energy as the incoming
+photon. Due to the non-linear relation between intensity and the probability
+to induce stimulated emission and the shape of the depletion beam
+(Fig.~\ref{fig:STED-principle}c, center), the size of the origin of
+spontaneous emission in the center of the depletion beam is decreased. The
+wavelength of the depletion beam and thus the wavelength of stimulated
+emission is selected such that it lies outside the detection window of the
+microscope (Fig.~\ref{fig:STED-principle}c, right), which de-facto switches
+fluorophores that undergo stimulated emission to an ``off''-state.
+
+In summary, this directly yields a recording of the fluorophores with a
+resolution beyond the diffraction limit (Fig.~\ref{fig:STED-principle}d). The
+resolution provided by STED microscopy depends on the intensity $I$ of the
+depletion beam and is given by
+\begin{equation}
+  d_\text{min, STED} = \frac\lambda{2\mathrm{NA}\sqrt{I/I_\text{sat}}}\text,
+  \label{eq:resolution-STED}
+\end{equation}
+which is a modification of Abbe's original equation
+(eq.~\eqref{eq:diffraction-limit}). Here, $I_\text{sat}$ is the intensity
+required to induce stimulated emission in half of the fluorophores.
 

### 2020-10-02 sections/correlated-sicm-and-srfm.tex
changed $-$ to --

@@
   \centering
-    \includegraphics[clip,scale=1]{.PDF} % @Patrick hier bitte den Filename eintragen
+%    \includegraphics[clip,scale=1]{.PDF} % @Patrick hier bitte den Filename eintragen
       \caption{
@@
 technique alone would have been used:
-\textsf{
+
+\noindent\textsf{
 \begin{tabular}[c]{p{6cm}|p{3cm}|p{3.75cm}}
@@
 visible, that were invisible to one of the microscopy techniques alone. This could be due to 
-fluorescence signals that were out of focus $-$ this could be the case by the actin signal that
-suddenly ends in the protrusion $-$ (STED microscopy) or due to overhanging membranes $-$ this 
+fluorescence signals that were out of focus -- this could be the case by the actin signal that
+suddenly ends in the protrusion -- (STED microscopy) or due to overhanging membranes -- this 
 could be the case by the connections between the cells (especially between the highest and the
-flat cell) $-$ (SICM) (Quelle).
+flat cell) -- (SICM) (Quelle).
 
@@
 SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
-fluorescently labeled molecules $-$ ATTO 655-phalloidin $-$ into living U2OS cells.
+fluorescently labeled molecules -- ATTO 655-phalloidin -- into living U2OS cells.
 
 % Hier jetzt noch was zu SICM/SNOM!
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "../manuscript"
+%%% End:

### 2020-10-02 sections/correlated-sicm-and-fm.tex
changed $-$ to --

@@
 be interesting to investigate, sowohl %german
-the cell membrane with a technique, which is able to do so $–$ AFM \cite{}, EM \cite{}, SICM 
-\cite{Hansma1989} $-$, als auch %german
+the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
+\cite{Hansma1989} --, als auch %german
 to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
@@
 scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
-simultaneously and $-$ because fluorescence signals should be investigated, which were originated
-from particles at or near to the surface of the cell $-$ it was important to keep the distance 
+simultaneously and -- because fluorescence signals should be investigated, which were originated
+from particles at or near to the surface of the cell -- it was important to keep the distance 
 between the sample and the pipette constant. In that study the SSCM was used for investigating the 
@@
 \cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
-After measuring the topography (SICM) the nanopipette could be moved to places $-$ e.g. the 
-z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} $-$ where the 
+After measuring the topography (SICM) the nanopipette could be moved to places -- e.g. the 
+z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} -- where the 
 adrenoceptor distribution should be investigated. Then the pipette could be used for stimulating 

### 2020-10-02 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
-be interesting to investigate, sowohl %german
-the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
-\cite{Hansma1989} --, als auch %german
-to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
-react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.
+be interesting to investigate both the cell membrane with a technique, which is able to do so -- 
+AFM \cite{Binnig1986}, EM \cite{}, SICM \cite{Hansma1989} -- and the uptake of nanoparticles into 
+cells or how the cytoskeleton react on the addition of the nanoparticle by using fluorescence 
+microscopy methods.
 
@@
 physiological surrounding. Certain destructive effects on the cell were found by using this 
-technique \cite{}. A better fitting method for investigating living cells would be scanning 
-ion conductance microscopy (SICM) \cite{Hansma1989}.
+technique \cite{You2000,Rheinlaender2011}. A better fitting method for investigating living cells 
+would be scanning ion conductance microscopy (SICM) \cite{Hansma1989}.
 
@@
 
-Another very delicate sample, because of their three-dimensional, upright (?) structure are cilia.
+Another very delicate sample, because of their three-dimensional, upright structure are cilia.
 Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
@@
 
-The SICM-nanopipette could be also used for investigating membrane rafts (Quelle) by coordinated 
-manipulation of focal adhesions. The pipette was functionalized with fibronectin, gangliosides
-were fluorescently labeled, the pipette deformed the focal adhesion side and the behavior of the 
-fluorescently labeled gangliosides were detected. This was seen as a hint, how membrane rafts 
-reacted \cite{Fuentes2012}.
+The SICM-nanopipette could be also used for investigating membrane rafts 
+\cite{Simons1997,Pike2006} by coordinated manipulation of focal adhesions. The pipette was 
+functionalized with fibronectin, gangliosides were fluorescently labeled, the pipette deformed the 
+focal adhesion side and the behavior of the fluorescently labeled gangliosides were detected. This 
+was seen as a hint, how membrane rafts reacted \cite{Fuentes2012}.
 
@@
 nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
-Nichtsdestotrotz (german)
-is it important to mention, that they could just giving hints of correlations, it 
+Nevertheless is it important to mention, that they could just giving hints of correlations, it 
 is not directly comparable with investigations of both in the same cell.

### 2020-10-03 sections/correlated-sicm-and-fm.tex
First paragraphs reviewed

--- 2020-10-02 sections/correlated-sicm-and-fm.tex
@@
 %%% End:
-Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
-which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
-This is especially helpful for applications, where the reaction is not limited to \emph{one 
-dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
-be interesting to investigate, sowohl %german
-the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
-\cite{Hansma1989} --, als auch %german
-to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
-react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.
+Correlative SICM and FM, despite the mismatch in resolution, allows to gather
+information which cannot be obtained by using a single technique
+alone. However, the degree of correlation differs, depending on the FM
+technique combined with SICM. Combining SICM and wide-field FM allows to image
+the same region of the sample, which, for example, can be used to find a
+region of interest such as an area containg synapses in a culture of a
+neuronal network \cite{Novak2013,Scheenen2015}.
 
-% Den Teil brauchen wir ja vielleicht nicht. 
-AFM, a method belonging to the scanning probe microscopy techniques, was successfully
-combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
-cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
-with this method is, that it is not the most favorable for investigating living cells in their
-physiological surrounding. Certain destructive effects on the cell were found by using this 
-technique \cite{}. A better fitting method for investigating living cells would be scanning 
-ion conductance microscopy (SICM) \cite{Hansma1989}.
+% Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
+% (allerdings natürlich nicht innerhalb von irgendetwas). Und irgendwie ist
+% das ja auch nicht der "Haupt"-Vorteil, sondern, dass man überhaupt
+% Fluoreszenz sehen kann.
+
+% This is especially helpful for applications, where the reaction is not limited to \emph{one 
+% dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
+% be interesting to investigate, sowohl %german
+% the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
+% \cite{Hansma1989} --, als auch %german
+% to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
+% react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.
+
+% % Den Teil brauchen wir ja vielleicht nicht. 
+% AFM, a method belonging to the scanning probe microscopy techniques, was successfully
+% combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
+% cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
+% with this method is, that it is not the most favorable for investigating living cells in their
+% physiological surrounding. Certain destructive effects on the cell were found by using this 
+% technique \cite{}. A better fitting method for investigating living cells would be scanning 
+% ion conductance microscopy (SICM) \cite{Hansma1989}.
 
@@
 synaptic boutons could be identified \cite{Novak2013} or the topography could be correlated with 
-the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2020}.
+the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2019}.
 
@@
 could be also used for nanoinjection of fluorescently labeled molecules into living cells 
-\cite{Hennig2015_nanoinj}. The SICM was therefore combined with wide-field and direct stochastic 
+\cite{Hennig2015a}. The SICM was therefore combined with wide-field and direct stochastic 
 optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
 stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
-introduced into the membranes, could occur \cite{Hennig2015_nanoinj}.
+introduced into the membranes, could occur \cite{Hennig2015a}.
 
@@
 
-SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
-the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
-\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors 
+SICM in combination with Förster resonance energy transfer (FRET) sensors could be used for
+the localisation of $\beta_{1}$-adrenoceptors \cite{Wright2018}, $\beta_{2}$-adrenoceptors 
+\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and $\beta_{3}$-adrenoceptors 
 \cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
@@
 could also being combined with condenser-free phase contrast, darkfield and brightfield images and 
-even Rheinberg illuminations were possible \cite{Webb2015}.
+even Rheinberg illuminations were possible \cite{Webb2014}.
 
@@
 is not directly comparable with investigations of both in the same cell.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "../manuscript"
+%%% End:

### 2020-10-03 sections/correlated-sicm-and-fm.tex

@@
 %%% End:
+
 Correlative SICM and FM, despite the mismatch in resolution, allows to gather
@@
 
+Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
+which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
+This is especially helpful for applications, where the reaction is not limited to \emph{one 
+dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
+be interesting to investigate both the cell membrane with a technique, which is able to do so -- 
+AFM \cite{Binnig1986}, EM \cite{}, SICM \cite{Hansma1989} -- and the uptake of nanoparticles into 
+cells or how the cytoskeleton react on the addition of the nanoparticle by using fluorescence 
+microscopy methods.
+
+% Den Teil brauchen wir ja vielleicht nicht. 
+AFM, a method belonging to the scanning probe microscopy techniques, was successfully
+combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
+cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
+with this method is, that it is not the most favorable for investigating living cells in their
+physiological surrounding. Certain destructive effects on the cell were found by using this 
+technique \cite{You2000,Rheinlaender2011}. A better fitting method for investigating living cells 
+would be scanning ion conductance microscopy (SICM) \cite{Hansma1989}.
+
 % Hier jetzt der surface confocal scanning part, NP investigation part usw. (damit warte ich aber,

### 2020-10-05 sections/pitfalls.tex
updated pitfalls.tex by including figure

@@
 \label{sec:pitfalls}
+
+\begin{figure}
+  \sidecaption
+  \includegraphics{gr/pitfalls/CombinedMicroscopy}%
+  \caption{\textbf{Potential implementations of combined SICM and FM.} 
+  			\textit{Left:} Schematic depiction of potential combined SICM 
+  			and TIRF or standard wide-field microscopy (\textit{top}),
+  			SICM and z-stacking (\textit{middle}) and SICM and surface
+  			scanning (\textit{bottom}). 
+  			\textit{Right:} Resulting correlating data of these combinations.}
+  \label{fig:CombinedMicroscopy}
+\end{figure}
+
 Combining SRFM and SICM in one setup is bound to bring up some potential

### 2020-10-05 sections/pitfalls.tex
Update pitfalls.tex

@@
 \label{sec:pitfalls}
+
+Combining SICM and FM or SRFM techniques leads to a variable quantity of 
+correlating data depending on the overlap of data acquired by each technique.
+Figure \ref{fig:CombinedMicroscopy} schematically illustrates implementations 
+of combined microscopes and the respective resulting correlating data.
 
@@
 
-Combining SRFM and SICM in one setup is bound to bring up some potential
-pitfalls, some of which are discussed in the following:
+A combination of SICM and wide-field microscopy techniques such as TIRF yields
+two data sets, just as any other combination would. However, before these data
+sets can be combined and examined for correlating data, it has to be ensured that 
+a data point from one set is assigned a data point from the other set. As SICM 
+can have significantly higher resolutions than wide-field microscopy, it is 
+likely that one data point from the wide-field microscopy data set is assigned 
+multiple data points from the SICM data set. To avoid this, the SICM pipette 
+could be adjusted to yield a lower resolution comparable to the wide-field 
+microscopy resolution. In case of a resolution mismatch the data sets have to be
+aligned after imaging, as wide-field microscopy is not a scanning technique and
+records all data at once instead of one another making it impossible to align the
+microscopes and thus the data recording prior to imaging. Due to the resolution
+mismatch this can prove difficult.
+
+Once the data is aligned, it can be checked for correlations. As SICM traces the 
+surface of the sample, it changes its position constantly in all 3 dimensions unless
+the sample has a very flat surface and a change in z direction is not necessary.
+In contrast, wide-field microscopy only records two dimensional data (in x and y
+directions). This means, that data points from the two different sets only truly 
+correlate, if the focus of the wide-field microscope is set to a focal plane (z)
+in the same or nearly the same z position as the SICM. To achieve this, the SICM
+should either not change its z position much, which is only reasonable for
+relatively flat samples, or SICM data from different z planes has to be discarded.
+Flat cell processes or extensions are an example for a structure, which could be 
+investigated by a such a combination.
+
+SICM and z-stacking FM techniques, when combined, yield more correlating data than
+SICM and wide-field techniques as z-stacking microscopy as this FM technique
+records data points in multiple z planes. After imaging these can be aligned with 
+the SICM data set and non-correlating data can be separated from correlating data.
+However, there is still a potential mismatch in resolution and the data has the 
+processed after imaging to yield correlation. Yet, this implementation is suitable
+for all, not only flat, samples.
+
+Implementations of SICM and surface scanning microscopy automatically solve one
+of the problems occuring when combining SICM with other FM techniques: Both 
+microscopes are scanning techniques able to change their z position from one data
+point to the next enabling an alignment before data recording. Therefore, all 
+recorded data, if aligned correctly, can be assumed to be correlating.
+
+Instead of having to worsen SICM resolution to match FM resolution, it might be 
+reasonable to combine SICM and SRFM in one setup. Though, this implementation
+comes with its own potential pitfalls, especially as due to the super resolution
+of both techniques small deviations or disturbances are sufficient to ruin the 
+alignment of the setup. Some of these potential pitfalls are discussed in the 
+following:
 
@@
 software should be used to control both setups to prevent delays in the
-imaging process due to ... (?)
+imaging process due to transmitting information from one software to the other.
 
@@
 tip and the laser beam only in the xy plane, e.g. for imaging fluorescent
-proteins in the cytoskeleton and the cell membrane simultaneously. The second
-one is additionally aligning the tip and beam in the z plane, e.g. to image
-cell membrane and fluorescent particles or proteins within the membrane
-simultaneously, as has been done in SSCM \cite{Gorelik2002a}\cite{Shevchuk2008}.
+proteins in the cytoskeleton and the cell membrane simultaneously. This is 
+comparable, in terms of data recording, to the above mentioned combinations of
+SICM and wide-field or z-stacking microscopy. 
+The second one, surface scanning, is additionally aligning the tip and beam
+in the z plane, e.g. to image cell membrane and fluorescent particles or proteins 
+within the membrane simultaneously, as has been done in 
+SSCM \cite{Gorelik2002a}\cite{Shevchuk2008}.
 
@@
 to align the pipette and the beam. It is apparently sufficient for aligning
-SICM and confocal microscopes (??). In case it isn't accurate enough piezo
-elements might have to be used. However, the usage of 3 piezo elements mounted
-to the same platform, may it be the pipette holder or sample stage, is
-reported to have caused cross-talk during sample positioning leading to image
-artifacts in the range of 100 nm \cite{Shevchuk2013}. Hence, it would be
-better to uncouple xy piezos from the z piezo. Furthermore, z piezos come with
-an increased risk of piezo drift. Therefore, especially the sample stage
-should ideally avoid z piezo usage.
+SICM and confocal microscopes \cite{Gorelik2002a}\cite{Shevchuk2008}. 
+In case it isn't accurate enough piezo elements might have to be used. 
+However, the usage of 3 piezo elements mounted to the same platform, may it be
+the pipette holder or sample stage, is reported to have caused cross-talk during
+sample positioning leading to image artifacts in the range of 100 nm 
+\cite{Shevchuk2013}. Hence, it would be better to uncouple xy piezos from 
+the z piezo. Furthermore, z piezos come with an increased risk of piezo drift. 
+Therefore, especially the sample stage should ideally avoid z piezo usage.
 

### 2020-10-07 sections/correlated-sicm-and-fm.tex
Added subsections (and some content to the first one)

--- 2020-10-03 sections/correlated-sicm-and-fm.tex
@@
 %%% End:
+
+% Assume a figure here which shows the different degrees of correlation
+\begin{figure}
+  \includegraphics[width=\textwidth]{gr/correlating/sicm+fm}
+  \caption{%
+    \textbf{Combining SICM and wide-field fluorescence microscopy.}
+    \textbf{a:}
+    \textbf{b:} FM image of presynaptic nerve terminals stained with
+    FM1-43. \textbf{c:} Overlay of the FM-image and two SICM recordings of the
+    same region. \textbf{d:} 3D-representation of the SICM recordings.
+    \textbf{b--d:} Reprinted with permission from ref \cite{Scheenen2015}.
+  }
+  \label{fig:sicm+fm}
+\end{figure}
+
 Correlative SICM and FM, despite the mismatch in resolution, allows to gather
 information which cannot be obtained by using a single technique
-alone. However, the degree of correlation differs, depending on the FM
-technique combined with SICM. Combining SICM and wide-field FM allows to image
-the same region of the sample, which, for example, can be used to find a
-region of interest such as an area containg synapses in a culture of a
-neuronal network \cite{Novak2013,Scheenen2015}.
+alone. However, the degree of correlation as well as the technical
+implementation differs, depending on the FM
+technique combined with SICM.
 
+\subsection{Combining SICM and wide-field FM}
+\label{sec:SICM+widefield}
+Combining SICM and wide-field FM allows to image the same region of
+the sample with both techniques (Fig.~\ref{fig:sicm+fm}a). Technically, this
+combination is simple, since most implementations of SICM are built on
+inverted optical microscopes. However, due to the
+poor $z$-resolution of wide-field FM, a direct correlation of data from the
+along the optical axis, $z$, which, for example, can be used to find a region
+of interest such as an area containing synapses in a culture of a neuronal
+network \cite{Novak2013,Scheenen2015}
+(Fig.~\ref{fig:scheenen2015}). Furthermore, a combination of wide-field FM and
+SICM has been used to first identify primary cilia in a cell culture and
+subsequently use SICM to reveal whether the selected cilium was extending into
+the extracellular space or was embedded in the cell, an information which
+could not be retrieved by using FM alone \cite{Zhou2018}.
 % Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
@@
 
+% Another very delicate sample, because of their three-dimensional, upright structure are cilia.
+% Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
+% distinguish between surface and sub-surface cilia, which could not be detected with SICM 
+% \cite{Zhou2018}.
+\subsection{Combining SICM and confocal FM}
+
+\subsection{Surface scanning}
+
 Topographical information obtained by SICM were successfully correlated with fluorescence signals
@@
 the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2019}.
-
-Another very delicate sample, because of their three-dimensional, upright (?) structure are cilia.
-Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
-distinguish between surface and sub-surface cilia, which could not be detected with SICM 
-\cite{Zhou2018}.
 

### 2020-10-07 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 
-\subsection{Surface scanning}
-
 Topographical information obtained by SICM were successfully correlated with fluorescence signals
@@
 the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2019}.
+
+In a study investigating the formation of human immunodeficiency virus (HIV) virus-like particles 
+(VLPs) the correlated SICM-fluorescence confocal microscopy (SICM-FCM) was used to investigate 
+topography changes together with die distribution of fluorescently labeled viral proteins like Gag 
+or Viral Protein R (Vpr) \cite{Bednarska2020}. In contrast of investigating the virus formation 
+with total internal reflection fluorescence (TIRF) microscopy \cite{Jouvenet2008} the upside 
+(Oberseite?) of the cells were investigated. The release of VLPs from the upside can be a lot 
+faster, than the release times that were known from TIRF measurements and difference between 
+different cell types and labeled virus proteins were found \cite{Bednarska2020}.
+
+The study of Nashimoto was showing that for the detection of secretory proteins, like the von 
+Willebrand factor, it is not always necessary to label the protein. Even with SICM alone the 
+detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
+images \cite{Nashimoto2015}.
+
+\subsection{\emph{Indirect} combination of SICM and FM}
+
+% Abschnitt weitere Korrelationen (indirekte)
+
+Beside \emph{direct} combinations in one instrument and correlations, which are displaying images 
+obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
+correlations exist. They are showing images under comparable conditions and extent the 
+investigation to aspects, which could not be obtained by using one technique alone. Such 
+\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
+nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
+Nevertheless is it important to mention, that they could just giving hints of correlations, it 
+is not directly comparable with investigations of both in the same cell.
+
+\subsection{Surface scanning}
 
@@
 cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.
-
-In a study investigating the formation of human immunodeficiency virus (HIV) VLPs the correlated
-SICM-fluorescence confocal microscopy (SICM-FCM) was used to investigate topography changes
-together with die distribution of fluorescently labeled viral proteins like Gag or Viral Protein R 
-(Vpr) \cite{Bednarska2020}. In contrast of investigating the virus formation with total internal 
-reflection fluorescence (TIRF) microscopy \cite{Jouvenet2008} the upside (Oberseite?) of the cells 
-were investigated. The release of VLPs from the upside can be a lot faster, than the release times 
-that were known from TIRF measurements and difference between different cell types and labeled 
-virus proteins were found \cite{Bednarska2020}.
 
@@
 
-The study of Nashimoto was showing that for the detection of secretory proteins, like the von 
-Willebrand factor, it is not always necessary to label the protein. Even with SICM alone the 
-detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
-images \cite{Nashimoto2015}.
+\subsection{Nanoinjection of fluorescently labeled molecules}
 
@@
 
-% Abschnitt weitere Korrelationen (indirekte)
-
-Beside these more or less \emph{direct} combinations and correlations, which are displaying images 
-obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
-correlations exist. They are showing images under comparable conditions and extent the 
-investigation to aspects, which could not be obtained by using one technique alone. Such 
-\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
-nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
-Nevertheless is it important to mention, that they could just giving hints of correlations, it 
-is not directly comparable with investigations of both in the same cell.
-
 %%% Local Variables:

### 2020-10-07 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

@@
 
-% Hier vielleicht auch noch Fig. 3 aus der ACSNano-Publikation einfügen??? Würde vielleicht ganz
-% gut passen!?
+% Hier kommt jetzt Fig. 3 aus der ACSNano-Publikation. @Patrick: Dafür bräuchten wir dann auch die 
+% Rechte + davon hast du glaube ich auch die Original-PDF-Version!?
+
+\begin{figure}
+  \centering
+%   \includegraphics[clip,scale=1]{.PDF} % @Patrick hier bitte auch den entsprechenden Filename 
+% eintragen
+    \caption{
+    \textbf{Simulating diffraction-limited and subdiffraction recordings of a protein involved in 
+    membrane protrusion formation.} 
+    (\textbf{A}) Topographical image of a membrane protrusion on the surface of a HeLa cell. The 
+    black traces indicate the putative location of a hypothetical protein, that could be involved 
+    in the formation of the membrane protrusion. (\textbf{B}) Simulated diffraction-limited 
+    recording of the hypothetical protein (resolution 250~nm). (\textbf{C}) Simulated 
+    subdiffraction recording of the hypothetical protein (resolution 75~nm). The scale bar in A 
+    applies to all images \newline Reprinted with permission from \emph{Philipp Hagemann*, Astrid 
+    Gesper*, Patrick Happel}, Correlative stimulated emission depletion and scanning ion 
+    conductance microscopy, \emph{ACS Nano} 2018, 12, 5807-5815, DOI: 10.1021/acsnano.8b01731. 
+    Copyright 2020 American Chemical Society}
+  \label{fig:structure_element_FM_vs_SRFM}
+\end{figure}
+
+\subsection{Combining SICM with STED microscopy}
 

### 2020-10-08 sections/correlated-sicm-and-fm.tex
Extended the introductory paragraph
I have incorporated the refs from the "indirect correlation" section into the
introductory paragraph. We can delete the "indirect correlation" section.

@@
     FM1-43. \textbf{c:} Overlay of the FM-image and two SICM recordings of the
-    same region. \textbf{d:} 3D-representation of the SICM recordings.
+    same region. \textbf{d:} 3D-representation of the lower right SICM
+    recording from c.
     \textbf{b--d:} Reprinted with permission from ref \cite{Scheenen2015}.
@@
 alone. However, the degree of correlation as well as the technical
-implementation differs, depending on the FM
-technique combined with SICM.
+implementation differs, depending on the FM technique combined with SICM, as
+we will detail in the following sections.
+
+Although recording SICM and FM data independently on different samples under
+the same conditions can support conclusions that could not be drawn from data
+from a single technique alone \cite{Gesper2017,Lee2013,Lyon2009}, we will
+focus on applications were SICM and FM data has been recorded from the same
+sample.
 
@@
 \label{sec:SICM+widefield}
-Combining SICM and wide-field FM allows to image the same region of
-the sample with both techniques (Fig.~\ref{fig:sicm+fm}a). Technically, this
-combination is simple, since most implementations of SICM are built on
-inverted optical microscopes. However, due to the
-poor $z$-resolution of wide-field FM, a direct correlation of data from the
-along the optical axis, $z$, which, for example, can be used to find a region
-of interest such as an area containing synapses in a culture of a neuronal
-network \cite{Novak2013,Scheenen2015}
-(Fig.~\ref{fig:scheenen2015}). Furthermore, a combination of wide-field FM and
-SICM has been used to first identify primary cilia in a cell culture and
-subsequently use SICM to reveal whether the selected cilium was extending into
-the extracellular space or was embedded in the cell, an information which
-could not be retrieved by using FM alone \cite{Zhou2018}.
+Combining SICM and wide-field FM allows to image the same region of the sample
+with both techniques (Fig.~\ref{fig:sicm+fm}a). Due to the different fields of
+view, the different pixel sizes and the different times required to record one
+image, the two data sets are not recorded synchronously and thus cannot by
+correlated pixel-by-pixel.  Technically, the combination is simple, since
+the SICM only has to be mounted onto an inverted optical FM and both
+instruments can be controlled independently by their own software.
+
+So far, the combination of SICM and wide-field FM has been used to find a
+region of interest such as an area containing active synapses in a culture of
+a neuronal network \cite{Novak2013,Scheenen2015}
+(Fig.~\ref{fig:sicm+fm}b--d). Furthermore, it has been used to first identify
+primary cilia in a cell culture and subsequently use SICM to reveal whether
+the selected cilium was extending into the extracellular space or was embedded
+in the cell, an information which could not be retrieved by using FM alone
+\cite{Zhou2018}.
 % Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D

### 2020-10-08 sections/correlated-sicm-and-srfm.tex
update

--- 2020-10-02 sections/correlated-sicm-and-srfm.tex
@@
 As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
-with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015_nanoinj}. The difference to the 
+with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015a}. The difference to the 
 SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 

### 2020-10-08 sections/pitfalls.tex
Update pitfalls.tex
Abbildung & zugehöriger Text auskommentiert

--- 2020-09-22 sections/pitfalls.tex
@@
 \label{sec:pitfalls}
-Combining SRFM and SICM in one setup is bound to bring up some potential
-pitfalls, some of which are discussed in the following:
+
+%Combining SICM and FM or SRFM techniques leads to a variable quantity of 
+%correlating data depending on the overlap of data acquired by each technique.
+%Figure \ref{fig:CombinedMicroscopy} schematically illustrates implementations 
+%of combined microscopes and the respective resulting correlating data. 
+%
+%\begin{figure}
+%  \sidecaption
+%  \includegraphics{gr/pitfalls/CombinedMicroscopy}%
+%  \caption{\textbf{Potential implementations of combined SICM and FM.} 
+%  			\textit{Left:} Schematic depiction of potential combined SICM 
+%  			and TIRF or standard wide-field microscopy (\textit{top}),
+%  			SICM and z-stacking (\textit{middle}) and SICM and surface
+%  			scanning (\textit{bottom}). 
+%  			\textit{Right:} Resulting correlating data of these combinations.}
+%  \label{fig:CombinedMicroscopy}
+%\end{figure}
+%
+%A combination of SICM and wide-field microscopy techniques such as TIRF yields
+%two data sets, just as any other combination would. However, before these data
+%sets can be combined and examined for correlating data, it has to be ensured that 
+%a data point from one set is assigned a data point from the other set. As SICM 
+%can have significantly higher resolutions than wide-field microscopy, it is 
+%likely that one data point from the wide-field microscopy data set is assigned 
+%multiple data points from the SICM data set. To avoid this, the SICM pipette 
+%could be adjusted to yield a lower resolution comparable to the wide-field 
+%microscopy resolution. In case of a resolution mismatch the data sets have to be
+%aligned after imaging, as wide-field microscopy is not a scanning technique and
+%records all data at once instead of one another making it impossible to align the
+%microscopes and thus the data recording prior to imaging. Due to the resolution
+%mismatch this can prove difficult.
+%
+%Once the data is aligned, it can be checked for correlations. As SICM traces the 
+%surface of the sample, it changes its position constantly in all 3 dimensions unless
+%the sample has a very flat surface and a change in z direction is not necessary.
+%In contrast, wide-field microscopy only records two dimensional data (in x and y
+%directions). This means, that data points from the two different sets only truly 
+%correlate, if the focus of the wide-field microscope is set to a focal plane (z)
+%in the same or nearly the same z position as the SICM. To achieve this, the SICM
+%should either not change its z position much, which is only reasonable for
+%relatively flat samples, or SICM data from different z planes has to be discarded.
+%Flat cell processes or extensions are an example for a structure, which could be 
+%investigated by a such a combination.
+%
+%SICM and z-stacking FM techniques, when combined, yield more correlating data than
+%SICM and wide-field techniques as z-stacking microscopy as this FM technique
+%records data points in multiple z planes. After imaging these can be aligned with 
+%the SICM data set and non-correlating data can be separated from correlating data.
+%However, there is still a potential mismatch in resolution and the data has the 
+%processed after imaging to yield correlation. Yet, this implementation is suitable
+%for all, not only flat, samples.
+%
+%Implementations of SICM and surface scanning microscopy automatically solve one
+%of the problems occuring when combining SICM with other FM techniques: Both 
+%microscopes are scanning techniques able to change their z position from one data
+%point to the next enabling an alignment before data recording. Therefore, all 
+%recorded data, if aligned correctly, can be assumed to be correlating.
+
+Instead of having to worsen SICM resolution to match FM resolution, it might be 
+reasonable to combine SICM and SRFM in one setup. Though, this implementation
+comes with its own potential pitfalls, especially as due to the super resolution
+of both techniques small deviations or disturbances are sufficient to ruin the 
+alignment of the setup. Some of these potential pitfalls are discussed in the 
+following:
 

### 2020-10-08 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Deleted "indirect" correlation part

@@
 
-\subsection{\emph{Indirect} combination of SICM and FM}
+% \subsection{\emph{Indirect} combination of SICM and FM}
 
-% Abschnitt weitere Korrelationen (indirekte)
-
-Beside \emph{direct} combinations in one instrument and correlations, which are displaying images 
-obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
-correlations exist. They are showing images under comparable conditions and extent the 
-investigation to aspects, which could not be obtained by using one technique alone. Such 
-\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
-nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
-Nevertheless is it important to mention, that they could just giving hints of correlations, it 
-is not directly comparable with investigations of both in the same cell.
+% Beside \emph{direct} combinations in one instrument and correlations, which are displaying 
+% images obtained by SICM and fluorescence microscopy of the same cell/same region, also 
+% \emph{indirect} correlations exist. They are showing images under comparable conditions and 
+% extent the investigation to aspects, which could not be obtained by using one technique alone. 
+% Such \emph{indirect} correlations were used for investigating the uptake of nanotubes 
+% \cite{Lee2013}, nanoparticles \cite{Gesper2017} or for investigating healthy and failing 
+% myocytes \cite{Lyon2009}. Nevertheless is it important to mention, that they could just giving 
+% hints of correlations, it is not directly comparable with investigations of both in the same 
+% cell.
 

### 2020-10-09 sections/introduction.tex
added caption for resolution figure

@@
   \includegraphics{gr/intro/Fig_SICM-resolution}
-  \caption{\textbf{Resolution of SICM.} \textbf{a:} \textbf{b:} Two
+  \caption{\textbf{Resolution of SICM.} \textbf{a:} Height profiles (plotted
+    vertically) of modelled SICM recordings of two cilindrical particles
+    (height and diameter: $r_\text{i}$) at varying distances. \textbf{b:} Two
     consecutive SICM recordings of the equatorial segment of a living boar
     spermatozoon recorded 10 minutes apart with a scanning pipette with
-    $r_\mathrm{i} \approx 6.75\,\text{nm}$}
+    $r_\mathrm{i} \approx 6.75\,\text{nm}$. \textbf{a:} reprinted with
+    permission from ref. \cite{rheinlaender:094905}, \textbf{b:} reprinted
+    with permission from ref. \cite{Shevchuk2006}. 
+  }
   \label{fig:sicm-resolution}
@@
 openings. Pipettes with radii of approximately 6.75\,nm have been used in for
-SICM imaging (Fig.~\ref{fig:sicm-resolution}b) \cite{Shevchuk2008}. In
+SICM imaging (Fig.~\ref{fig:sicm-resolution}b) \cite{Shevchuk2006}. In
 contrast, the resolution in light microscopy is fundamentally limited by the
@@
 Fig.~\ref{fig:sicm-resolution}B, which were reported to be 14\,nm
-\cite{Shevchuk2008}.
+\cite{Shevchuk2006}.
 
@@
 
-% Since its invention, the light microscope is a widely used tool in
-% biology. The development of the fluorescence and the confocal microscope
-% \cite{Heimstaedt1911,Minsky1988} along with the improvement and development in
-% staining techniques \cite{Coons1942,Tsien1998} made fluorescence microscopy
-% (FM) a standard tool in the life sciences and medicine. With the new
-% development of super-resolved fluorescence microscopy (SRFM)
-% \cite{hell+wichmann,Betzig2006,Rust2006}, fluorescence microscopy entered the
-% world beyond Abbe's diffraction limit \cite{Abbe1873}, and now allows to
-% routinely investigate questions at a length scale below 100\,nm.
-
-% SICM, as any scanning probe technique, provides information about the surface
-% of the scanned sample. In contrast, FM provides information about the
-% distribution of the labeled specimen. Gathering complementary information from
-% the same sample, surface topography
-
-% \begin{equation}
-%   \label{eq:abbe}
-%   d = \frac{\lambda}{2 n \sin\alpha}
-% \end{equation}
-
 %%% Local Variables:

### 2020-10-09 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 
+%work in progress / noch nicht fertig
+By combining SICM and surface scanning confocal microscopy or scanning surface confocal
+microscopy (SSCM) \cite{Gorelik2002} two scanning microscopy techniques are combined enabling 
+simultaneous imaging of the same region on the same sample at the same time. To achieve matching 
+field of views, pixel sizes and recording times consequentially yielding two correlating data sets
+two slightly different setups are imaginable and have been put to the test (see figure \ref{fig:sicm+sscm_setup}) 
+\cite{Gorelik2002}\cite{Shevchuk2013}.
+\begin{figure}
+  \includegraphics[width=\textwidth]{gr/correlating/sicm+sscm_setup}
+  \caption{%
+    \textbf{Two possible setups for a combined SIC and SSC microscope.}
+    \textbf{a:}
+    \textbf{b:} 
+    Reprinted with permission from ref \cite{Shevchuk2013}.
+  }
+  \label{fig:sicm+sscm_setup}
+\end{figure}
+
 Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 

### 2020-10-09 sections/srfm.tex
one more sentence on STED resolution
A few additions

@@
   \caption{%
-    \textbf{Principle of fluorescence microscopy.}
-    \textbf{a:}
-      Jablonski diagram of fluorescence. A photon of energy
-      $h\nu_\text{ex}$ gets absorbed and excites the molecule from its
-      electronic ground state $S_0$ to a vibrational excited state of the
-      electronic state $S_1$ (green arrow). After radiation-less relaxation
-      (black arrow) into the vibrational ground state of $S_1$, the molecule
-      returns to any vibrational state of $S_0$ (red arrow) by emitting a photon
-      of energy $h\nu_\text{em}$, after which it relaxes to the lowest
-      vibrational state of $S_0$.
-    \textbf{b:}
-      Typical absorbance (green) and
-      emission (red) spectra of a fluorescent dye molecule. Green and red
-      rectangles indicate the wavelength range used for excitation (exc) and
-      detection.
-  }
+    \textbf{Principle of fluorescence microscopy.}  \textbf{a:} Jablonski
+    diagram of fluorescence. A photon of energy $h\nu_\text{ex}$ gets absorbed
+    and excites the molecule from its electronic ground state $S_0$ to a
+    vibrational excited state of the electronic state $S_1$ (green
+    arrow). After radiation-less relaxation (black arrow) into the vibrational
+    ground state of $S_1$, the molecule returns to one of the vibrational
+    states of $S_0$ (red arrow) by emitting a photon of energy
+    $h\nu_\text{em}$, after which it relaxes to the lowest vibrational state
+    of $S_0$.  \textbf{b:} Typical absorbance (green) and emission (red)
+    spectra of a fluorescent dye molecule. Green and red rectangles indicate
+    the wavelength range used for excitation (exc) and detection in FM.  }
   \label{fig:jablonski-fluorescence}
@@
 shown in Fig.~\ref{fig:jablonski-fluorescence}b. In FM, a single wavelength or
-a wavelength range (green rectangle Fig.~\ref{fig:jablonski-fluorescence}b) in
-suitable to excite the fluorophore used is chosen, by using a suitable laser
+a wavelength range (green rectangle in Fig.~\ref{fig:jablonski-fluorescence}b) 
+suitable to excite the fluorophore used is chosen -- by using a suitable laser
 or LED or by selecting the wavelength range via a band-pass filter from a
-white light source and send through the objective lens of the microscope to
+white light source -- and send through the objective lens of the microscope to
 the sample. In most FMs (the so called epifluorescence microscopes), the
@@
 Fig.~\ref{fig:FM-setups}. In a wide-field FM (Fig.~\ref{fig:FM-setups}a), the
-entire sample is excited at 
-the same time, and all fluorophores in the sample emit at the same time
-(yellow circles in the right inset in Fig.~\ref{fig:FM-setups}a). The emission
-of the fluorophores (solid red shape in Fig.~\ref{fig:FM-setups}a, only five
-beam paths are shown for clarity) is collected by the objective lens, passes
-the dichroic mirror and is further cleared by a band-pass filter. The emission
-then is focused by the tube lens onto the camera, which records an image of
-the emission of all fluorophores at the same time.
+entire sample is illuminated at the same time, and all fluorophores in the sample
+emit at the same time (yellow circles in the right inset in
+Fig.~\ref{fig:FM-setups}a). The emission of the fluorophores (solid red shape
+in Fig.~\ref{fig:FM-setups}a, only five beam paths are shown for clarity) is
+collected by the objective lens, passes the dichroic mirror and is further
+cleared by a band-pass filter. The emission then is focused by the tube lens
+onto the camera, which records an image of the emission of all fluorophores at
+the same time.
 
 Each fluorophore in the sample generates a diffraction limited spot on the
-camera, and spots which are not separated in space by at least the diffraction
+camera, and spots which are not separated in space by at least the diffraction limit
 cannot be distinguished as single spots. Thus, the wavelength which determines
@@
 The major disadvantage of a wide-field microscope is that the sample is not
-only illuminated evenly in the focal plane of the objective lens, but also
-fluorophores outside the focal plane in $z$-direction are excited and their
+only illuminated in the focal plane of the objective lens, but also
+fluorophores above and below the focal plane are excited and their
 emission is collected (not shown for clarity). Since they are not located in
@@
 shown in Fig.~\ref{fig:FM-setups}b. Here, the excitation light (green solid
-shape) is focused into the sample by the objective lens and only the
-fluorophores within the diffraction limited spot are excited. Thus, the
+shape) is focused onto the sample by the objective lens and only the
+fluorophores within the resulting diffraction limited spot are excited. Thus, the
 wavelength which determines the resolution of a confocal microscope is the
@@
 name \emph{confocal}).
+
+For a potential combination with SICM, the most important aspect of the two
+techniques is the way the fluorescence is recorded. Wide-field FM uses a 
+camera to record the entire sample at once, whereas confocal FM is a scanning
+technique which records the single pixels subsequently, either by moving the
+sample through the beam or vice versa.
 
@@
 
-The principle of these methods is illustrated in
-Fig.~\ref{fig:lm}. Initially, all fluorophores within the sample are
-inactivated (``off''-state, grey dots in Fig.~\ref{fig:lm}a). Next,  light suitable to switch the fluorophores
-(cyan background, Fig.~\ref{fig:lm}b) from the inactivated to
-the activated (``on'') state (white dots) is applied. The intensity of the
-activation light is selected such that only a small subset of the inactivated
-molecules is activated, at maximum one molecule per area of the diffraction limited spot. The activated molecules are excited
-(green background, yellow dots) and their emission is recorded. The excitation
-light is applied as long as all excited molecules have bleached (black
-dots). The series of activation, excitation and read-out is repeated until all
-fluorophores have been excited and bleached, which results in a set of images
-containing diffraction limited emission spots of all fluorophores in the
-sample.
+The principle of these methods is illustrated in Fig.~\ref{fig:lm}. Initially,
+all fluorophores within the sample are inactivated (``off''-state, grey dots
+in Fig.~\ref{fig:lm}a). Next, light suitable to switch the fluorophores (cyan
+background, Fig.~\ref{fig:lm}b) from the inactivated to the activated (``on'')
+state (white dots) is applied. The intensity of the activation light is
+selected such that only a small subset of the inactivated molecules is
+activated, at maximum one molecule per area of the diffraction limited
+spot. The activated molecules are excited (green background, yellow dots) and
+their emission is recorded. The excitation light is applied as long as all
+excited molecules have bleached (black dots). The series of activation,
+excitation and read-out is repeated until all fluorophores have been excited
+and bleached, which results in a set of images containing diffraction limited
+emission spots of all fluorophores in the sample.
 
@@
 beam interacts with the excited fluorophore and causes it to de-excite to the
-ground state and to emit a photon of the same energy as the incoming
+ground state and to emit a second photon of the same energy as the incoming
 photon. Due to the non-linear relation between intensity and the probability
@@
 wavelength of the depletion beam and thus the wavelength of stimulated
-emission is selected such that it lies outside the detection window of the
+emission is selected such that it is outside the detection window of the
 microscope (Fig.~\ref{fig:STED-principle}c, right), which de-facto switches
-fluorophores that undergo stimulated emission to an ``off''-state.
+fluorophores that undergo stimulated emission to an invisible ``off''-state.
 
@@
 required to induce stimulated emission in half of the fluorophores.
+
+The best resolution (approximately 2\,nm) obtained by STED microscopy has
+been recorded on samples containing fluorescent color centers in diamond
+crystal \cite{Wildanger2012}. Note that, by applying a depletion beam of a
+different shape, STED microscopy allows to improve the resolution along the
+optical axis \cite{Wildanger2009}. A large number of reviews articles exist
+which summarize the use of STED (or in general, RESOLFT) microscopy in different
+fields in the life sciences, much too much to be listed here. We would like to
+refer the reader to exhaustive reviews, which, besides
+reviewing various applications, detail technical aspects of STED microscopy
+\cite{Turkowyd2016,Blom2017} as well as to a review which contains some
+anecdotal sections on how STED was developed \cite{Sahl2019}.
 

### 2020-10-09 sections/srfm.tex
Added on ref

@@
 different shape, STED microscopy allows to improve the resolution along the
-optical axis \cite{Wildanger2009}. A large number of reviews articles exist
+optical axis \cite{Harke2008, Wildanger2009}. A large number of reviews articles exist
 which summarize the use of STED (or in general, RESOLFT) microscopy in different

### 2020-10-09 sections/correlated-sicm-and-fm.tex

--- 2020-10-08 sections/correlated-sicm-and-fm.tex
@@
 
+%work in progress / noch nicht fertig
+Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and confocal 
+microscopy tracking the sample surface. This combination enables simultaneous SICM and FM imaging of
+the same region, in this case the surface, of the same sample at the same time. To achieve matching
+field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
+two slightly different setups are imaginable and have been put to the test (see figure 
+\ref{fig:sicm+sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
+\begin{figure}
+  \includegraphics[width=\textwidth]{gr/correlating/sicm+sscm_setup}
+  \caption{%
+    \textbf{Two possible setups for a combined SIC and SSC microscope.}
+    \textbf{a: Diagram of the combined setup with a xyz sample scan.}
+    \textbf{b: Diagram of the combined setup with a xy sample scan and a z probe scan.} 
+    Reprinted with permission from ref \cite{Shevchuk2013}.
+  }
+  \label{fig:sicm+sscm_setup}
+\end{figure}
+
 Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 

### 2020-10-09 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 two slightly different setups are imaginable and have been put to the test (see figure 
-\ref{fig:sicm+sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
+\ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
 \begin{figure}
-  \includegraphics[width=\textwidth]{gr/correlating/sicm+sscm_setup}
+  \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}
   \caption{%
-    \textbf{Two possible setups for a combined SIC and SSC microscope.}
+    \textbf{Two possible setups for a SSC microscope.}
     \textbf{a: Diagram of the combined setup with a xyz sample scan.}
@@
 \end{figure}
+The first setup (figure \ref{fig:sscm_setup}a), basically an inverted SIC microscope, holds the 
+SICM probe at a fixed position. The focus of the confocal FM objective is adjusted to the tip of SICM 
+probe for vertical alignment. To achieve lateral alignment of probe and pinhole mechanical 
+micromanipulators are used. Once the setup is aligned, the sample stage moves the sample in all three 
+dimensions (xyz) for imaging.
+The second setup (figure \ref{fig:sscm_setup}b) is almost identical to the first with just one 
+alteration: the sample stage only moves in xy dimensions while objective and probe have been equipped 
+with an extra piezo element to enable movement in z direction. Thus, instead of moving the sample in
+all three dimensions, it is only moved in x and y directions, while probe and objective simultaneously
+move in z direction.
+According to \cite{Shevchuk2013}, this change allows for faster scan rates as the resonant frequency
+of the 3D piezo-actuator acted as a limiting factor. Additionally, usage of three piezo-elements on the
+same platform lead to cross-talk and consequentially artefacts in the SICM data.
 

### 2020-10-09 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
     \textbf{Two possible setups for a SSC microscope.}
-    \textbf{a: Diagram of the combined setup with a xyz sample scan.}
-    \textbf{b: Diagram of the combined setup with a xy sample scan and a z probe scan.} 
+    \textbf{a:} Diagram of the combined setup with a xyz sample scan.
+    \textbf{b:} Diagram of the combined setup with a xy sample scan and a z probe and objective scan. 
     Reprinted with permission from ref \cite{Shevchuk2013}.

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 %work in progress / noch nicht fertig
-Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and confocal 
-microscopy tracking the sample surface. This combination enables simultaneous SICM and FM imaging of
+Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and scanning
+confocal microscopy (SCM). This combination enables simultaneous SICM and FM imaging of
 the same region, in this case the surface, of the same sample at the same time. To achieve matching
@@
 \ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
+
 \begin{figure}
@@
   }
-  \label{fig:sicm+sscm_setup}
+  \label{fig:sscm_setup}
 \end{figure}
+
 The first setup (figure \ref{fig:sscm_setup}a), basically an inverted SIC microscope, holds the 
@@
 dimensions (xyz) for imaging.
+
 The second setup (figure \ref{fig:sscm_setup}b) is almost identical to the first with just one 
@@
 with an extra piezo element to enable movement in z direction. Thus, instead of moving the sample in
-all three dimensions, it is only moved in x and y directions, while probe and objective simultaneously
-move in z direction.
+all three dimensions, it is only moved in x and y directions, while probe and objective, controlled by
+the same software, simultaneously move in z direction.
+
 According to \cite{Shevchuk2013}, this change allows for faster scan rates as the resonant frequency
@@
 same platform lead to cross-talk and consequentially artefacts in the SICM data.
+
+Both setups keep the probe-objective distance constant and enable the acquisition of a fluorescence
+image and a topography of the sample surface in the same scan. Photobleaching is equalized for every
+point of the sample allowing quantitative analysis of the FM data.
+
+As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
+corresponding data point in the other set. This immediate correlation allows not only for correlating
+studies in fixed samples, but also studies of dynamics in live samples.
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{gr/correlating/sicm+scm}
+  \caption{%
+    \textbf{Combining SICM and SCM.}
+    \textbf{a:} Schematic illustration of the correlating data acquired by SSCM.
+    \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
+    VLPs adsorbed to the surface of COS 7 cells. Reprinted with permission from ref \cite{Gorelik2002}.
+    \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
+    	\textit{Left:} Cell surface topography. 
+    	\textit{Middle:} Fluorescence recording of the cell shown left. 
+    	\textit{Right:} 3D overlay of topographical and fluorescent recordings. 
+    Reprinted with permission from ref \cite{Shevchuk2008}.
+    \textbf{d:} Live COS 7 cells sequentially scanned by SSCM. Overlays of simmultaneously obtained 
+    topographic and fluorescence scans. Fluorescence imaging was started 2 h 17 min after the first 
+    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2 h 40 min. 
+    Reprinted with permission from ref \cite{Gorelik2002}.
+  }
+  \label{fig:sicm+scm}
+\end{figure}
 

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 
-As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
-corresponding data point in the other set. This immediate correlation allows not only for correlating
-studies in fixed samples, but also studies of dynamics in live samples.
-
 \begin{figure}
@@
 
-Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
-scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
-simultaneously and -- because fluorescence signals should be investigated, which were originated
-from particles at or near to the surface of the cell -- it was important to keep the distance 
-between the sample and the pipette constant. In that study the SSCM was used for investigating the 
-dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
-The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
-(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
-cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.
+As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
+corresponding data point in the other set. This immediate correlation allows not only for correlating
+studies in fixed samples (figure \ref{fig:sicm+scm}c), but also studies of dynamics in live samples 
+(figure \ref{fig:sicm+scm}d).
 
-SSCM could be also used for investigating endocytotic pathways \cite{Shevchuk2008}. In a study 
-investigating topography together with actin-binding protein-green fluorescent protein (Abp1-GFP)
-and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) an alternative closing 
-mechanism for clathrin-coated pits (CCPs) \cite{Shevchuk2012}. In another study the uptake of
-200~nm fluorescent, carboxylated latex particles into immortalized human alveolar epithelial type
-1-like (AT1) cells was investigated. Additional to the fluorescence signal of the nanoparticle the 
-fluorescence signal of actin-binding protein-green fluorescent protein (Abp1-GFP) and clathrin
-light-chain-enhanced green fluorescent protein (Clc-EGFP) were detected. Both, actin, as part of
-the cytoskeleton (Quelle), and clathrin, as one important actor of endocytosis (Quelle), give 
-interesting Zusatzinformationen on how the nanoparticle is taken up into the cell 
-\cite{Novak2014}.
+To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating the
+dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells 
+(figure \ref{fig:sicm+scm}d), for the investigating the uptake of fluorescent nanoparticles in 
+immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells \cite{Kemp2008} and for 
+investigating the differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been utilized
+in studies investigating endocytotic pathways \cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and in
+a study investigating an alternative closing mechanism for clathrin-coated pits (CCPs) by recording 
+topography simultaneously with the fluorescence of actin-binding protein-green fluorescent protein 
+(Abp1-GFP) and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}.
+In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized human
+alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.
+
+%Anmerkung: Habe die folgenden Paragraphen versucht in oberen Text einzubauen und deshalb hier 
+%auskommentiert.
+
+%Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
+%scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
+%simultaneously and -- because fluorescence signals should be investigated, which were originated
+%from particles at or near to the surface of the cell -- it was important to keep the distance 
+%between the sample and the pipette constant. In that study the SSCM was used for investigating the 
+%dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
+%The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
+%(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
+%cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.
+%
+%SSCM could be also used for investigating endocytotic pathways \cite{Shevchuk2008}. In a study 
+%investigating topography together with actin-binding protein-green fluorescent protein (Abp1-GFP)
+%and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) an alternative closing 
+%mechanism for clathrin-coated pits (CCPs) \cite{Shevchuk2012}. In another study the uptake of
+%200~nm fluorescent, carboxylated latex particles into immortalized human alveolar epithelial type
+%1-like (AT1) cells was investigated. Additional to the fluorescence signal of the nanoparticle the 
+%fluorescence signal of actin-binding protein-green fluorescent protein (Abp1-GFP) and clathrin
+%light-chain-enhanced green fluorescent protein (Clc-EGFP) were detected. Both, actin, as part of
+%the cytoskeleton (Quelle), and clathrin, as one important actor of endocytosis (Quelle), give 
+%interesting Zusatzinformationen on how the nanoparticle is taken up into the cell 
+%\cite{Novak2014}.
 

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
 
-%work in progress / noch nicht fertig
 Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and scanning
@@
 As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
-corresponding data point in the other set. This immediate correlation allows not only for correlating
-studies in fixed samples (figure \ref{fig:sicm+scm}c), but also studies of dynamics in live samples 
-(figure \ref{fig:sicm+scm}d).
+corresponding data point in the other set. This immediate correlation, schematically illustrated in
+figure \ref{fig:sicm+scm}a, allows not only for correlating studies in fixed samples (figure 
+\ref{fig:sicm+scm}c), but also studies of dynamics in live samples (figure \ref{fig:sicm+scm}d).
 
@@
 dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells 
-(figure \ref{fig:sicm+scm}d), for the investigating the uptake of fluorescent nanoparticles in 
+(figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent nanoparticles in 
 immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells \cite{Kemp2008} and for 

### 2020-10-10 sections/correlated-sicm-and-fm.tex
minor

--- 2020-10-10 sections/correlated-sicm-and-fm.tex
@@
 \cite{Zhou2018}.
+
 % Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
@@
 %work in progress / noch nicht fertig
-Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and scanning
-confocal microscopy (SCM). This combination enables simultaneous SICM and FM imaging of
+Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and confocal 
+microscopy tracking the sample surface. This combination enables simultaneous SICM and FM imaging of
 the same region, in this case the surface, of the same sample at the same time. To achieve matching
@@
 two slightly different setups are imaginable and have been put to the test (see figure 
-\ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
-
+\ref{fig:sicm+sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
 \begin{figure}
-  \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}
+%  \includegraphics[width=\textwidth]{gr/correlating/sicm+sscm_setup}
   \caption{%
-    \textbf{Two possible setups for a SSC microscope.}
-    \textbf{a:} Diagram of the combined setup with a xyz sample scan.
-    \textbf{b:} Diagram of the combined setup with a xy sample scan and a z probe and objective scan. 
+    \textbf{Two possible setups for a combined SIC and SSC microscope.}
+    \textbf{a: Diagram of the combined setup with a xyz sample scan.}
+    \textbf{b: Diagram of the combined setup with a xy sample scan and a z probe scan.} 
     Reprinted with permission from ref \cite{Shevchuk2013}.
   }
-  \label{fig:sscm_setup}
-\end{figure}
-
-The first setup (figure \ref{fig:sscm_setup}a), basically an inverted SIC microscope, holds the 
-SICM probe at a fixed position. The focus of the confocal FM objective is adjusted to the tip of SICM 
-probe for vertical alignment. To achieve lateral alignment of probe and pinhole mechanical 
-micromanipulators are used. Once the setup is aligned, the sample stage moves the sample in all three 
-dimensions (xyz) for imaging.
-
-The second setup (figure \ref{fig:sscm_setup}b) is almost identical to the first with just one 
-alteration: the sample stage only moves in xy dimensions while objective and probe have been equipped 
-with an extra piezo element to enable movement in z direction. Thus, instead of moving the sample in
-all three dimensions, it is only moved in x and y directions, while probe and objective, controlled by
-the same software, simultaneously move in z direction.
-
-According to \cite{Shevchuk2013}, this change allows for faster scan rates as the resonant frequency
-of the 3D piezo-actuator acted as a limiting factor. Additionally, usage of three piezo-elements on the
-same platform lead to cross-talk and consequentially artefacts in the SICM data.
-
-Both setups keep the probe-objective distance constant and enable the acquisition of a fluorescence
-image and a topography of the sample surface in the same scan. Photobleaching is equalized for every
-point of the sample allowing quantitative analysis of the FM data.
-
-As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
-corresponding data point in the other set. This immediate correlation allows not only for correlating
-studies in fixed samples, but also studies of dynamics in live samples.
-
-\begin{figure}
-  \includegraphics[width=\textwidth]{gr/correlating/sicm+scm}
-  \caption{%
-    \textbf{Combining SICM and SCM.}
-    \textbf{a:} Schematic illustration of the correlating data acquired by SSCM.
-    \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
-    VLPs adsorbed to the surface of COS 7 cells. Reprinted with permission from ref \cite{Gorelik2002}.
-    \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
-    	\textit{Left:} Cell surface topography. 
-    	\textit{Middle:} Fluorescence recording of the cell shown left. 
-    	\textit{Right:} 3D overlay of topographical and fluorescent recordings. 
-    Reprinted with permission from ref \cite{Shevchuk2008}.
-    \textbf{d:} Live COS 7 cells sequentially scanned by SSCM. Overlays of simmultaneously obtained 
-    topographic and fluorescence scans. Fluorescence imaging was started 2 h 17 min after the first 
-    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2 h 40 min. 
-    Reprinted with permission from ref \cite{Gorelik2002}.
-  }
-  \label{fig:sicm+scm}
+  \label{fig:sicm+sscm_setup}
 \end{figure}

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Reviewed a bit of Annika's text

--- 2020-10-10 sections/correlated-sicm-and-fm.tex
@@
 
-Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and scanning
-confocal microscopy (SCM). This combination enables simultaneous SICM and FM imaging of
-the same region, in this case the surface, of the same sample at the same time. To achieve matching
-field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
-two slightly different setups are imaginable and have been put to the test (see figure 
-\ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
+Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a
+combination of SICM and scanning confocal microscopy (SCM) which enables
+simultaneous SICM and FM imaging of the surface of the same sample. In SSCM,
+the fluorescence data for each pixel is recorded at the position determined by
+SICM for that pixel. Up to now, two slightly different setups have been proposed
+(Fig.~\ref{fig:sscm_setup}) \cite{Gorelik2002,Shevchuk2013}.
 
@@
   \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}
+
   \caption{%
-    \textbf{Two possible setups for a SSC microscope.}
-    \textbf{a:} Diagram of the combined setup with a xyz sample scan.
-    \textbf{b:} Diagram of the combined setup with a xy sample scan and a z probe and objective scan. 
+    \textbf{Two setups for a SSC microscope.}
+    \textbf{a:} Diagram of the combined setup with an $x,y,z$ sample scanner.
+    \textbf{b:} Diagram of the combined setup with a $x,y$ sample scanner and
+    a $z$-probe and objective scanner. 
     Reprinted with permission from ref \cite{Shevchuk2013}.
@@
 
-The first setup (figure \ref{fig:sscm_setup}a), basically an inverted SIC microscope, holds the 
-SICM probe at a fixed position. The focus of the confocal FM objective is adjusted to the tip of SICM 
-probe for vertical alignment. To achieve lateral alignment of probe and pinhole mechanical 
-micromanipulators are used. Once the setup is aligned, the sample stage moves the sample in all three 
-dimensions (xyz) for imaging.
+In both setups, an SICM is mounted onto an inverted confocal microscope and
+before simultaneous recording, the focus of the confocal FM objective is
+aligned with the tip of the SICM probe via micrometer screws and the confocal
+microscope's focusing mechanics. The
+difference between the two setups is the way how the SICM pipette, the
+confocal focus and the sample are positioned with respect to each other during
+imaging. The
+first setup (Fig.~\ref{fig:sscm_setup}a) keeps the 
+SICM probe at a fixed position and scanning is performed by the sample
+stage which positions the sample in all three dimensions.
 
-The second setup (figure \ref{fig:sscm_setup}b) is almost identical to the first with just one 
-alteration: the sample stage only moves in xy dimensions while objective and probe have been equipped 
-with an extra piezo element to enable movement in z direction. Thus, instead of moving the sample in
-all three dimensions, it is only moved in x and y directions, while probe and objective, controlled by
-the same software, simultaneously move in z direction.
+In contrast, the second setup (Fig.~\ref{fig:sscm_setup}b) uses the sample
+stage to position the sample in $x$- and $y$-direction only while objective
+and probe are positioned by additional piezo elements in $z$-direction. Thus,
+when the surface is detected by the SICM pipette, subsequently the position of
+the confocal spot has to be adjusted by the objective positioning piezo.
 
-According to \cite{Shevchuk2013}, this change allows for faster scan rates as the resonant frequency
-of the 3D piezo-actuator acted as a limiting factor. Additionally, usage of three piezo-elements on the
-same platform lead to cross-talk and consequentially artefacts in the SICM data.
+Both setups do not allow to use the controlling software of the confocal
+microscope since the fluorescence data has to be recorded after the SICM
+pipette has detected the surface. Thus, the SICM controlling soft- and
+hardware had to be extended to at least allow reading from the detectors of
+the confocal microscope.
+
+Switching from full stage scanning to $z$-movement of the pipette allows for
+faster scan rates as the resonant frequency of the 3D piezo-actuator acted as
+a limiting factor. Additionally, usage of three piezo-elements on the same
+platform led to cross-talk and consequentially artefacts in the SICM data
+\cite{Shevchuk2013}.
+
+% Bis hier überarbeitet.
 

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
added to sicm + confocal FM

@@
 \subsection{Combining SICM and confocal FM}
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{gr/correlating/sicm+cfm}
+  \caption{%
+    \textbf{Combining SICM and confocal fluorescence microscopy.}
+    \textbf{a:}
+    \textbf{b:} 
+    Reprinted with permission from ref \cite{}.
+  }
+  \label{fig:sicm+cfm}
+\end{figure}
+
+Similar to a SICM and wide-field combination, a combination of SICM and confocal FM enables
+imaging of the same region and sample with both techniques (Fig.~\ref{fig:sicm+cfm}a). The technical
+implementation involves only mounting a SICM onto an inverted confocal FM. The software used to
+control the two microscopes does not have to the same as both microscope record data independently 
+from one another. However, as the recordings are not simultaneously pixel-by-pixel correlation is hardly,
+if at all, possible. Yet, a combination of SICM and z-stacking confocal FM yields more correlating data
+than combinations of SICM and wide-field techniques: z-stacking microscopy records data points in 
+multiple z planes. After imaging these can be aligned with the SICM data and non-correlating data can be
+separated from correlating data. Still, there is a potential mismatch in resolution and the data has to 
+be processed after imaging to yield correlation. Yet, this implementation is suitable for all, not only 
+flat, fixed samples.
+
+SICM and confocal FM has been combined for the first time by Korchev et al \cite{Korchev2000} in
+2000. The group used this combination to verify the volume measurements obtained by SICM. Just a 
+year later, further development of this combination enabled simultaneous acqusition of Ca^{2+} 
+imaging and topography data \cite{Shevchuk2001}. Afterwards, many different studies using a combination
+of SICM and confocal FM have been published:
 

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@
     \textbf{Combining SICM and confocal fluorescence microscopy.}
-    \textbf{a:}
+    \textbf{a:} Schematic illustration of the correlating data acquired by combining SICM and confocal FM.
     \textbf{b:} 
-    Reprinted with permission from ref \cite{}.
+    	\textit{Left:} Topography of a neuronal network.
+    	\textit{Middle:} Fluorescence of the same neuronal network as depicted on the left.
+    	\textit{Right:} Overlay of topography and fluorescence of two regions of interest (ROI 1, ROI 2) from
+    	the left and middle image.
+    Reprinted with permission from ref \cite{Novak2013}.
   }
@@
 imaging of the same region and sample with both techniques (Fig.~\ref{fig:sicm+cfm}a). The technical
-implementation involves only mounting a SICM onto an inverted confocal FM. The software used to
+implementation involves mounting a SICM onto an inverted confocal FM. The software used to
 control the two microscopes does not have to the same as both microscope record data independently 
-from one another. However, as the recordings are not simultaneously pixel-by-pixel correlation is hardly,
+from one another. However, as the recordings are not simultaneous, pixel-by-pixel correlation is hardly,
 if at all, possible. Yet, a combination of SICM and z-stacking confocal FM yields more correlating data
-than combinations of SICM and wide-field techniques: z-stacking microscopy records data points in 
-multiple z planes. After imaging these can be aligned with the SICM data and non-correlating data can be
+than combinations of SICM and wide-field techniques as z-stacking microscopy records data points in 
+multiple z planes. After imaging, these can be aligned with the SICM data and non-correlating data can be
 separated from correlating data. Still, there is a potential mismatch in resolution and the data has to 
@@
 
-SICM and confocal FM has been combined for the first time by Korchev et al \cite{Korchev2000} in
+SICM and confocal FM have been combined for the first time by Korchev et al \cite{Korchev2000} in
 2000. The group used this combination to verify the volume measurements obtained by SICM. Just a 
@@
 imaging and topography data \cite{Shevchuk2001}. Afterwards, many different studies using a combination
-of SICM and confocal FM have been published:
+of SICM and confocal FM were published:
 
-Topographical information obtained by SICM were successfully correlated with fluorescence signals
+Topographical information obtained by SICM was successfully correlated with fluorescence signals
 of stained cytoskeleton molecules obtained by laser scanning confocal microscopy in platelets 
@@
 
-In addition, hippocampal neurons, which were very delicate samples with many little protrusions, 
+In addition, hippocampal neurons, which are very delicate samples with many little protrusions, 
 could be investigated with correlated SICM and confocal microscopy. With such a combination active
-synaptic boutons could be identified \cite{Novak2013} or the topography could be correlated with 
-the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2019}.
+synaptic boutons could be identified \cite{Novak2013} (Fig.~\ref{fig:sicm+cfm}b) and topographical changes
+in dendrites were correlated to FM data of mitochondria-containing dendrite regions \cite{Takahashi2019}.
 

### 2020-10-11 sections/correlated-sicm-and-fm.tex
reworked (part of) the text on confocal amd SICM

@@
 region of interest such as an area containing active synapses in a culture of
-a neuronal network \cite{Novak2013,Scheenen2015}
-(Fig.~\ref{fig:sicm+fm}b--d). Furthermore, it has been used to first identify
-primary cilia in a cell culture and subsequently use SICM to reveal whether
-the selected cilium was extending into the extracellular space or was embedded
-in the cell, an information which could not be retrieved by using FM alone
-\cite{Zhou2018}.
+a neuronal network \cite{Scheenen2015} (Fig.~\ref{fig:sicm+fm}b--d) or to
+identify the neuron which had been investigated by SICM-guided patch-clamp of
+synaptic boutons \cite{Novak2013}.
+
+Furthermore, it has been used to first identify primary cilia in a cell
+culture and subsequently use SICM to reveal whether the selected cilium was
+extending into the extracellular space or was embedded in the cell, an
+information which could not be retrieved by using FM alone \cite{Zhou2018}.
 
@@
 
-Similar to a SICM and wide-field combination, a combination of SICM and confocal FM enables
-imaging of the same region and sample with both techniques (Fig.~\ref{fig:sicm+cfm}a). The technical
-implementation involves mounting a SICM onto an inverted confocal FM. The software used to
-control the two microscopes does not have to the same as both microscope record data independently 
-from one another. However, as the recordings are not simultaneous, pixel-by-pixel correlation is hardly,
-if at all, possible. Yet, a combination of SICM and z-stacking confocal FM yields more correlating data
-than combinations of SICM and wide-field techniques as z-stacking microscopy records data points in 
-multiple z planes. After imaging, these can be aligned with the SICM data and non-correlating data can be
-separated from correlating data. Still, there is a potential mismatch in resolution and the data has to 
-be processed after imaging to yield correlation. Yet, this implementation is suitable for all, not only 
-flat, fixed samples.
+Similar to a SICM and wide-field combination, a combination of SICM and
+confocal FM enables imaging of the same region and sample with both techniques
+(Fig.~\ref{fig:sicm+cfm}a). The technical implementation involves mounting a
+SICM onto an inverted confocal FM. The software used to control the two
+microscopes does not have to be the same as both microscopes record data
+independently from one another. However, as the recordings are not
+simultaneous, pixel-by-pixel correlation is hardly, if at all, possible.
 
-SICM and confocal FM have been combined for the first time by Korchev et al \cite{Korchev2000} in
-2000. The group used this combination to verify the volume measurements obtained by SICM. Just a 
-year later, further development of this combination enabled simultaneous acqusition of Ca^{2+} 
-imaging and topography data \cite{Shevchuk2001}. Afterwards, many different studies using a combination
-of SICM and confocal FM were published:
+Yet,
+a combination of SICM and $z$-stacking confocal FM yields more correlating
+data than combinations of SICM and wide-field techniques as $z$-stacking
+microscopy records data points in multiple $z$ planes. After imaging, these can
+be aligned with the SICM data and non-correlating data can be separated from
+correlating data. Still, there is a potential mismatch in resolution and the
+data has to be processed after imaging to yield correlation. Yet, this
+implementation is suitable for all, not only flat, fixed samples.
 
-Topographical information obtained by SICM was successfully correlated with fluorescence signals
-of stained cytoskeleton molecules obtained by laser scanning confocal microscopy in platelets 
-\cite{Seifert2017}.
+SICM and confocal FM have been combined for the first time by Korchev et al.
+\cite{Korchev2000} in 2000. The group used this combination to verify the
+volume measurements obtained by SICM. Just a year later, further development
+of this combination enabled simultaneous acqusition of Ca\textsuperscript{2+}
+imaging and topography data \cite{Shevchuk2001}.
+% Afterwards, many different
+% studies using a combination of SICM and confocal FM were published:
 
-In addition, hippocampal neurons, which are very delicate samples with many little protrusions, 
-could be investigated with correlated SICM and confocal microscopy. With such a combination active
-synaptic boutons could be identified \cite{Novak2013} (Fig.~\ref{fig:sicm+cfm}b) and topographical changes
-in dendrites were correlated to FM data of mitochondria-containing dendrite regions \cite{Takahashi2019}.
+Seifert et al. \cite{Seifert2017} investigated the morphological activity of
+platelets by time-lapse SICM and subsequently obtained confocal recordings of
+cytoskeletal proteins of the investigated cells, allowing them to correlate
+the activity of the platelets and the structure of the cytoskeleton.
 
-In a study investigating the formation of human immunodeficiency virus (HIV) virus-like particles 
-(VLPs) the correlated SICM-fluorescence confocal microscopy (SICM-FCM) was used to investigate 
+SICM has been shown to allow patch-clamp recordings from tiny neuronal
+structures like synaptic boutons \cite{Novak2013}. The combination of SICM and
+confocal FM allowed to first record an overview image and to identify active
+synaptic boutons (Fig.~\ref{fig:sicm+cfm}b), which, in a second step, could be
+patch-clamped.
+
+A second study on neurons investigated, besides others, cargo transport in
+neuronal dendrites \cite{Takahashi2019}. Here, the combination of
+confocal FM and SICM provided a hint that the transport processes observed by
+SICM were mediated by mitochondria.
+
+In a study investigating the formation of human immunodeficiency virus-like particles 
+(VLPs) the correlated SICM-fluorescence confocal microscopy was used to investigate 
 topography changes together with die distribution of fluorescently labeled viral proteins like Gag 
-or Viral Protein R (Vpr) \cite{Bednarska2020}. In contrast of investigating the virus formation 
-with total internal reflection fluorescence (TIRF) microscopy \cite{Jouvenet2008} the upside 
-(Oberseite?) of the cells were investigated. The release of VLPs from the upside can be a lot 
-faster, than the release times that were known from TIRF measurements and difference between 
-different cell types and labeled virus proteins were found \cite{Bednarska2020}.
+or Viral Protein R \cite{Bednarska2020}. In contrast to investigating the virus formation 
+with TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal
+FM allowed to investigate the apical side of the cells. It was found that the release of VLPs is a lot 
+faster than the release at the basal cell side as known from TIRF
+investigations and furthermore, a potential impact on the release time by the
+application of a fluorescent marker was found \cite{Bednarska2020}.
+
+% Bis hier...
 

### 2020-10-11 sections/correlated-sicm-and-fm.tex
Nashimoto auskommentiert. Ist das nicht wide-field?

@@
 
-In a study investigating the formation of human immunodeficiency virus-like particles 
-(VLPs) the correlated SICM-fluorescence confocal microscopy was used to investigate 
-topography changes together with die distribution of fluorescently labeled viral proteins like Gag 
-or Viral Protein R \cite{Bednarska2020}. In contrast to investigating the virus formation 
-with TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal
-FM allowed to investigate the apical side of the cells. It was found that the release of VLPs is a lot 
-faster than the release at the basal cell side as known from TIRF
-investigations and furthermore, a potential impact on the release time by the
-application of a fluorescent marker was found \cite{Bednarska2020}.
+In a study investigating the formation of human immunodeficiency virus-like
+particles (VLPs) the correlated SICM-fluorescence confocal microscopy was used
+to investigate topography changes together with die distribution of
+fluorescently labeled viral proteins like Gag or Viral Protein R
+\cite{Bednarska2020}. In contrast to investigating the virus formation with
+TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal FM
+allowed to investigate the apical side of the cells. It was found that the
+release of VLPs is a lot faster than the release at the basal cell side as
+known from TIRF investigations and furthermore, a potential impact on the
+release time by the application of a fluorescent marker was found
+\cite{Bednarska2020}.
 
@@
 
-The study of Nashimoto was showing that for the detection of secretory proteins, like the von 
-Willebrand factor, it is not always necessary to label the protein. Even with SICM alone the 
-detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
-images \cite{Nashimoto2015}.
+%% Wenn ich das Paper richtig verstehe, wurde hier aber kein konfokales FM
+%% genutzt, oder? 
+%
+% Nashimoto et al. investigated whether the secretion of the von 
+% Willebrand factor from living cells can be investigated by SICM without any
+% additional labeling. , it is not always necessary to label the protein. Even with SICM alone the 
+% detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
+% images \cite{Nashimoto2015}.
 

### 2020-10-12 sections/correlated-sicm-and-fm.tex
Moved section about z-stacks to bottom of section. Not yet integrated
reworked up to indication
Questions:
- Is Nashimoto2015 really confocal?
- What is meant by "equalized photobleaching"

@@
 
-Yet,
-a combination of SICM and $z$-stacking confocal FM yields more correlating
-data than combinations of SICM and wide-field techniques as $z$-stacking
-microscopy records data points in multiple $z$ planes. After imaging, these can
-be aligned with the SICM data and non-correlating data can be separated from
-correlating data. Still, there is a potential mismatch in resolution and the
-data has to be processed after imaging to yield correlation. Yet, this
-implementation is suitable for all, not only flat, fixed samples.
-
 SICM and confocal FM have been combined for the first time by Korchev et al.
@@
 
-% Bis hier...
+% ich würde hier etwas zu potentiellen z-stacks + SICM sagen wollen, das hat
+% ja meines Wissens nach noch niemand gemacht...
+The applications reviewed above used only a single confocal layer. Yet,
+a combination of SICM and $z$-stacking confocal FM could be used to yield more
+correlating data. After imaging the entire volume that is scanned by SICM, the
+data could be aligned and non-correlating data could be separated from
+correlating data. If stage scanning would be omitted, the two measurements
+could be performed simultaneously, but not synchronously.
 
@@
 
-% Bis hier überarbeitet.
-
-Both setups keep the probe-objective distance constant and enable the acquisition of a fluorescence
-image and a topography of the sample surface in the same scan. Photobleaching is equalized for every
-point of the sample allowing quantitative analysis of the FM data.
+Both setups keep the probe-objective distance constant and enable the
+acquisition of a fluorescence image and a topography of the sample surface in
+the same scan. Photobleaching is equalized for every point of the sample
+allowing quantitative analysis of the FM data.
 
@@
     \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
-    VLPs adsorbed to the surface of COS 7 cells. Reprinted with permission from ref \cite{Gorelik2002}.
+    VLPs adsorbed to the surface of Cos-7 cells. Reprinted with permission from ref \cite{Gorelik2002}.
     \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
     	\textit{Left:} Cell surface topography. 
-    	\textit{Middle:} Fluorescence recording of the cell shown left. 
+    	\textit{Center:} Fluorescence recording of the cell shown left. 
     	\textit{Right:} 3D overlay of topographical and fluorescent recordings. 
     Reprinted with permission from ref \cite{Shevchuk2008}.
-    \textbf{d:} Live COS 7 cells sequentially scanned by SSCM. Overlays of simmultaneously obtained 
-    topographic and fluorescence scans. Fluorescence imaging was started 2 h 17 min after the first 
-    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2 h 40 min. 
+    \textbf{d:} Live Cos-7 cells sequentially scanned by SSCM. Overlays of simultaneously obtained 
+    topographic and fluorescence scans. Fluorescence imaging was started 2\,h 17\,min after the first 
+    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2\,h 40\,min. 
     Reprinted with permission from ref \cite{Gorelik2002}.
@@
 
-As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
-corresponding data point in the other set. This immediate correlation, schematically illustrated in
-figure \ref{fig:sicm+scm}a, allows not only for correlating studies in fixed samples (figure 
-\ref{fig:sicm+scm}c), but also studies of dynamics in live samples (figure \ref{fig:sicm+scm}d).
+As the SICM and SCM data sets are recorded simultaneously, all data points inherently have a
+correlating data point in the other set. This immediate correlation, schematically illustrated in
+Fig.~\ref{fig:sicm+scm}a, allows not only for correlating studies in fixed
+samples (Fig.~\ref{fig:sicm+scm}c), but also studies of dynamics in live
+samples (Fig.~\ref{fig:sicm+scm}d).
+
+% Bis hier
 

### 2020-10-12 sections/correlated-sicm-and-srfm.tex
Reviewed and heavily shortened
For more detailed information, the people should look at the original paper. :-)

--- 2020-10-08 sections/correlated-sicm-and-srfm.tex
@@
 
-For resolving tiny structures like single cytoskeleton fibers, nanoparticle, with sizes smaller
-than the diffraction-limit, or protein complexes, it would be helpful to use microscopy
-techniques, which can resolve structures beyond the diffraction limit of light (see 
-equation~\ref{eq:diffraction-limit}; \cite{Abbe1873}).
+In contrast to the combination of AFM and SRFM, the development of correlated
+SICM and SRFM is still in its very early stages. The first combination of SRFM
+and SICM has been the use of STORM to determine the number of fluorescent
+molecules deposited via an SICM tip \cite{Hennig2015}. However, recently a
+first proof-of-principle study combining STED and SICM has been published
+\cite{Hagemann2018}.
 
-% Hier vielleicht auch noch Fig. 3 aus der ACSNano-Publikation einfügen??? Würde vielleicht ganz
-% gut passen!?
-
-One of that techniques, that can resolve structures beyond the diffraction limit, is STED 
-microscopy (see section~\ref{sec:deterministic-approaches}). In a proof-of-principle study the 
-topography of a group of fixed HeLa cells together with the distribution of actin filaments was
-investigated \cite{Hagemann2018}. Although both methods were able to investigate living cells, the 
-cells were fixed in that study, because the investigation was done consecutively onto two 
-microscopes. The topography was measured with SICM and the distribution of actin with STED 
-microscopy (see figure~\ref{fig:SICM_STED1}).
-
-% Hier soll jetzt Figure 4 unserer ACSNano-Publikation folgen. Patrick, du hast doch die 
-% Ursprungs-/Original-PDF-Version davon, oder? Kannst du die dann bitte hier einfügen und 
-% natürlich gucken, dass wir die Rechte dafür bekommen (das wolltest du ja machen, damit wir das 
-% alles in einem Dokument haben).
+In the latter, the topography of a group of fixed HeLa has been investigated by SICM
+(Fig.~\ref{fig:SICM_STED1}a) and, subsequently, the cytoskeletal protein actin by 
+confocal and STED microscopy (Fig.~\ref{fig:SICM_STED1}b). The area of the
+sample imaged by both methods is marked in Fig.~\ref{fig:SICM_STED1}c (SICM: yellow 
+rectangle, STED: gray rectangle).
 
@@
   \centering
-%    \includegraphics[clip,scale=1]{.PDF} % @Patrick hier bitte den Filename eintragen
+    \includegraphics[width=\textwidth]{gr/correlating/Hagemann2018-F4}
       \caption{
@@
 
-The topography of a group of more than four fixed HeLa cells can be seen in 
-figure~\ref{fig:SICM_STED1}Aa the corresponding slope representation in Ab, the confocal image in 
-Ac and the STED image in Ad. The confocal and STED image represents the same region as marked with 
-a black dotted line in Aa and Ab. C is showing the arrangement of the SICM image (yellow 
-rectangle) against the confocal/STED image (gray rectangle). Many different cell topographies were
-visible in Aa.
+Most interestingly, a protrusion (white arrowhead in
+Fig.~\ref{fig:SICM_STED1}a, b) extending from one cell was captured by both
+methods (magnified in Fig.~\ref{fig:SICM_STED1}d). The confocal recording
+showed a blurred spot within the protrusion (Fig.~\ref{fig:SICM_STED1}db),
+while the STED recording revealed that actin was arranged as a ring-shaped
+structure around two central spots. The authors speculate that this structure
+might be involved in the attachement or detachement of the cell from the cell
+culture dish. However, since the recordings were performed on fixed cells, no
+time-lapse data that could support this speculation exist.
 
-A round cell with a maximum height of approximately 16.4~{\textmu}m height can be seen in the 
-right upper region of the image (marked with a purple arrow in Aa/Ab/Ac/Ad). The cell next to this 
-was flat and exceeding the scanned region (yellow arrow). A second flat but smaller cell was 
-marked with a white arrow, which was ending with a white dot. Marked with an orange arrow (Aa, Ab) 
-respectively with a cyan arrow (Ba, Bb) was a small, kind of roundish cells. This cell posesses 
-a protrusion (white arrowhead), those magnification could be seen in Dd/Df respectively in De/Dg. 
-The protrusion was approximately 4~{\textmu}m long and 5~{\textmu}m high (Dc, 
-\cite{Hagemann2018}).
-
-Beside the different topographies of these two cells, they also display different types of actin 
-fibers. In the inside of the first mentioned round cell nearly no actin signal could be detected 
-(some dot-like structures were marked with purple arrowheads), whereas at the borders of the cell 
-some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
-fibers (yellow arrowheads). The cell marked with the white arrow, which was ending with a white 
-dot, could be just seen half in the confocal/STED images and dot-like actin structures 
-predominate. The cell with the protrusion was showing fan-like actin structures (cyan arrow, which
-was ending with a cyan dot and white arrow, which was ending with a white dot) where the cell was
-connected to surrounding cells and actin agglomerations (cyan arrow). The agglomerations turned 
-out to be \emph{rings} by watching the STED image (cyan circle). Such a structure could be also 
-found in the protrusion (white arrowhead, Df and Dg). In the center of the \emph{actin ring} two 
-dots could be identified (black arrowheads, Da).
-
-Structures that would have been missed and/or could have been misinterpreted, if just one single
-technique alone would have been used:
-
-\noindent\textsf{
-\begin{tabular}[c]{p{6cm}|p{3cm}|p{3.75cm}}
-\label{tab:missing_structures}
-What? & visible in fig.~\ref{fig:SICM_STED1} by SICM & visible in fig.~\ref{fig:SICM_STED1} by STED microscopy \\ \hline
-The connections between the small round cell with the protrusion and the other cells & \textbf{PARTLY} & YES \\ \hline
-The full extent of the protrusion & YES & \textbf{NO} \\ \hline
-The connection between the roundish and the flat cell & \textbf{NO} & YES \\
-\end{tabular}}
-
-This points out again one of the biggest advantage of correlative microscopy: making things 
-visible, that were invisible to one of the microscopy techniques alone. This could be due to 
-fluorescence signals that were out of focus -- this could be the case by the actin signal that
-suddenly ends in the protrusion -- (STED microscopy) or due to overhanging membranes -- this 
-could be the case by the connections between the cells (especially between the highest and the
-flat cell) -- (SICM) (Quelle).
+% Bis hier
 

### 2020-10-12 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Added Ali2019 as an example for SSCM. Searching for additional examples ...

@@
 volume measurements obtained by SICM. Just a year later, further development
-of this combination enabled simultaneous acqusition of Ca\textsuperscript{2+}
+of this combination enabled simultaneous acquisition of Ca\textsuperscript{2+}
 imaging and topography data \cite{Shevchuk2001}.
@@
 % Bis hier
+% Bitoun2005 -> PMID: 16227997; Zuechner2005 -> PMID: 15731758; Ali2019 -> PMID: 31017801
+% Added: Ali2019 -> ich suche noch nach weiteren Beispielen
 
-To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating the
-dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells 
-(figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent nanoparticles in 
-immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells \cite{Kemp2008} and for 
-investigating the differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been utilized
-in studies investigating endocytotic pathways \cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and in
-a study investigating an alternative closing mechanism for clathrin-coated pits (CCPs) by recording 
-topography simultaneously with the fluorescence of actin-binding protein-green fluorescent protein 
-(Abp1-GFP) and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}.
-In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized human
-alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.
+To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating 
+the dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 
+cells (figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent 
+nanoparticles in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells 
+\cite{Kemp2008} and for investigating the differentiation of stem cells \cite{Gorelik2008}. 
+Furthermore, it has been utilized in studies investigating endocytotic pathways 
+\cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and \cite{Shevchuk2012,Ali2019}. In the study of 
+Shevchuk et al. \cite{Shevchuk2012} in 2012 an alternative closing mechanism for clathrin-coated 
+pits (CCPs) were found by recording topography simultaneously with the fluorescence of actin-
+binding protein-green fluorescent protein (Abp1-GFP) and clathrin light-chain-enhanced green 
+fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}. In the study of Ali et al. \cite{Ali2019} the 
+effect of mutations in the Dynamin 2 (DNM2) gene, which play a role in diseases like centronuclear 
+myopathy \cite{Bitoun2005} or Charcot-Marie-Tooth disease \cite{Zuechner2005}, on the morphology 
+and the kinetics of the uptake-relevant processes -- formation, internalization … -- of CCPs were
+investigated.
+
+In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized 
+human alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.
 

### 2020-10-13 sections/correlated-sicm-and-fm.tex
Todo: Nanoinjection-part

--- 2020-10-12 sections/correlated-sicm-and-fm.tex
@@
 
-Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a
+Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002a} is a
 combination of SICM and scanning confocal microscopy (SCM) which enables
@@
 SICM for that pixel. Up to now, two slightly different setups have been proposed
-(Fig.~\ref{fig:sscm_setup}) \cite{Gorelik2002,Shevchuk2013}.
+(Fig.~\ref{fig:sscm_setup}) \cite{Gorelik2002a,Shevchuk2013}.
 
@@
 and probe are positioned by additional piezo elements in $z$-direction. Thus,
-when the surface is detected by the SICM pipette, subsequently the position of
-the confocal spot has to be adjusted by the objective positioning piezo.
+when the surface is detected by the SICM pipette,  the position of
+the confocal spot has to be adjusted by the objective positioning piezo subsequently.
 
@@
 
-Switching from full stage scanning to $z$-movement of the pipette allows for
-faster scan rates as the resonant frequency of the 3D piezo-actuator acted as
-a limiting factor. Additionally, usage of three piezo-elements on the same
-platform led to cross-talk and consequentially artefacts in the SICM data
-\cite{Shevchuk2013}.
+Switching from three-axis stage scanning to $z$-movement of the pipette
+allowed for faster scan rates as the resonant frequency of the 3D
+piezo-actor acted as a limiting factor. Additionally, usage of three
+piezo-elements on the same platform led to cross-talk and consequentially
+artefacts in the SICM data \cite{Shevchuk2013}.
 
@@
     \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
-    VLPs adsorbed to the surface of Cos-7 cells. Reprinted with permission from ref \cite{Gorelik2002}.
+    VLPs adsorbed to the surface of Cos-7 cells. Reprinted with permission from ref \cite{Gorelik2002a}.
     \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
@@
 samples (Fig.~\ref{fig:sicm+scm}c), but also studies of dynamics in live
-samples (Fig.~\ref{fig:sicm+scm}d).
+samples (Fig.~\ref{fig:sicm+scm}d).\todo{Improve paragraph}
 
@@
 
-To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating the
-dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells 
-(figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent nanoparticles in 
-immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells \cite{Kemp2008} and for 
-investigating the differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been utilized
-in studies investigating endocytotic pathways \cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and in
-a study investigating an alternative closing mechanism for clathrin-coated pits (CCPs) by recording 
-topography simultaneously with the fluorescence of actin-binding protein-green fluorescent protein 
-(Abp1-GFP) and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}.
-In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized human
-alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.
+SSCM has been used for investigating the dynamics of the interaction of
+Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
+(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
+uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
+type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
+differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been
+utilized in studies investigating endocytotic pathways \cite{Shevchuk2008}
+(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
+mechanism for clathrin-coated pits by recording topography simultaneously with
+the fluorescence of tagged actin-binding protein and the tagged
+clathrin light-chain \cite{Shevchuk2012}.
 

### 2020-10-13 sections/correlated-sicm-and-fm.tex

@@
 clathrin light-chain \cite{Shevchuk2012}.
+=======
+% Bitoun2005 -> PMID: 16227997; Zuechner2005 -> PMID: 15731758; Ali2019 -> PMID: 31017801
+% Added: Ali2019 -> ich suche noch nach weiteren Beispielen
+
+To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating 
+the dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 
+cells (figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent 
+nanoparticles in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells 
+\cite{Kemp2008} and for investigating the differentiation of stem cells \cite{Gorelik2008}. 
+Furthermore, it has been utilized in studies investigating endocytotic pathways 
+\cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and \cite{Shevchuk2012,Ali2019}. In the study of 
+Shevchuk et al. \cite{Shevchuk2012} in 2012 an alternative closing mechanism for clathrin-coated 
+pits (CCPs) were found by recording topography simultaneously with the fluorescence of actin-
+binding protein-green fluorescent protein (Abp1-GFP) and clathrin light-chain-enhanced green 
+fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}. In the study of Ali et al. \cite{Ali2019} the 
+effect of mutations in the Dynamin 2 (DNM2) gene, which play a role in diseases like centronuclear 
+myopathy \cite{Bitoun2005} or Charcot-Marie-Tooth disease \cite{Zuechner2005}, on the morphology 
+and the kinetics of the uptake-relevant processes -- formation, internalization … -- of CCPs were
+investigated.
+
+In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized 
+human alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}. 
+>>>>>>> 1dc5732e20282e8a916a002a11827856299c8360
 

### 2020-10-13 sections/correlated-sicm-and-fm.tex
Added the Gorelik-reserch to the widefield-FM part

--- 2020-10-13 sections/correlated-sicm-and-fm.tex
@@
 \label{sec:correlating-sicm-and-fm}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "../manuscript"
-%%% End:
 
@@
 
-% Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
-% (allerdings natürlich nicht innerhalb von irgendetwas). Und irgendwie ist
-% das ja auch nicht der "Haupt"-Vorteil, sondern, dass man überhaupt
-% Fluoreszenz sehen kann.
+\begin{figure}
+  \includegraphics[width=\textwidth]{gr/correlating/Nikolaev2010-F2}
+  \caption{
+    \textbf{a:}\textbf{b:}\textbf{c:}\textbf{d:}\textbf{e:}\textbf{f:}
+  }
+  \label{fig:nikolaev2010}
+\end{figure}
+Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
+crests (Fig.~\ref{fig:nikolaev2010}a, b). By first recording the topography
+and subsequently moving the SICM pipette to either a T-tubule or a crest,
+followed by the local application of agonists of either the $\beta_1$- or
+$\beta_2$-adrenergic receptor (AR) and recording the intensity ratio of cyan
+and yellow fluorescent protein, coupled to a Förster resonance energy transfer
+(FRET) based reporter of cyclic AMP (Fig.~\ref{fig:nikolaev2010}c--f), it was
+shown that the distribution of the $\beta_2$-AR was altered in failing
+cardio-myocytes \cite{Nikolaev2010}. Furthermore, this approach was used to
+investigate the effect of partial mechanical unloading, showing that it
+reduces the cyclic AMP response of $\beta_2$-ARs at the T-tubules
+\cite{Wright2018}. To investigate the distribution of the $\beta_3$-AR, the
+approach was extended to use a FRET-based reporter of cyclic GMP, showing that
+a redistribution of the $\beta_3$-AR occurs in failing cardio-myocytes, too
+\cite{Schobesberger2020}.
 
-% This is especially helpful for applications, where the reaction is not limited to \emph{one 
-% dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
-% be interesting to investigate, sowohl %german
-% the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
-% \cite{Hansma1989} --, als auch %german
-% to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
-% react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.
-
-% % Den Teil brauchen wir ja vielleicht nicht. 
-% AFM, a method belonging to the scanning probe microscopy techniques, was successfully
-% combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
-% cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
-% with this method is, that it is not the most favorable for investigating living cells in their
-% physiological surrounding. Certain destructive effects on the cell were found by using this 
-% technique \cite{}. A better fitting method for investigating living cells would be scanning 
-% ion conductance microscopy (SICM) \cite{Hansma1989}.
-
-% Hier jetzt der surface confocal scanning part, NP investigation part usw. (damit warte ich aber,
-% bis ich weiß, wie das richtig eingefügt wird.
-
-% Another very delicate sample, because of their three-dimensional, upright structure are cilia.
-% Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
-% distinguish between surface and sub-surface cilia, which could not be detected with SICM 
-% \cite{Zhou2018}.
 \subsection{Combining SICM and confocal FM}
@@
 the fluorescence of tagged actin-binding protein and the tagged
-clathrin light-chain \cite{Shevchuk2012}.
-
-%Anmerkung: Habe die folgenden Paragraphen versucht in oberen Text einzubauen und deshalb hier 
-%auskommentiert.
-
-%Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
-%scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
-%simultaneously and -- because fluorescence signals should be investigated, which were originated
-%from particles at or near to the surface of the cell -- it was important to keep the distance 
-%between the sample and the pipette constant. In that study the SSCM was used for investigating the 
-%dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
-%The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
-%(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
-%cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.
-%
-%SSCM could be also used for investigating endocytotic pathways \cite{Shevchuk2008}. In a study 
-%investigating topography together with actin-binding protein-green fluorescent protein (Abp1-GFP)
-%and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) an alternative closing 
-%mechanism for clathrin-coated pits (CCPs) \cite{Shevchuk2012}. In another study the uptake of
-%200~nm fluorescent, carboxylated latex particles into immortalized human alveolar epithelial type
-%1-like (AT1) cells was investigated. Additional to the fluorescence signal of the nanoparticle the 
-%fluorescence signal of actin-binding protein-green fluorescent protein (Abp1-GFP) and clathrin
-%light-chain-enhanced green fluorescent protein (Clc-EGFP) were detected. Both, actin, as part of
-%the cytoskeleton (Quelle), and clathrin, as one important actor of endocytosis (Quelle), give 
-%interesting Zusatzinformationen on how the nanoparticle is taken up into the cell 
-%\cite{Novak2014}.
+clathrin light-chain \cite{Shevchuk2012}. A further study on clathrin-coated
+pit formation and maturation revealed the effect of mutations in the Dynamin~2
+gene on the maturation and internalisation of clathrin coated pits \cite{Ali2019}.
 
@@
 the diffusion of single molecules over different regions at a spermatozoa were investigated.
-
-SICM in combination with Förster resonance energy transfer (FRET) sensors could be used for
-the localisation of $\beta_{1}$-adrenoceptors \cite{Wright2018}, $\beta_{2}$-adrenoceptors 
-\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and $\beta_{3}$-adrenoceptors 
-\cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
-After measuring the topography (SICM) the nanopipette could be moved to places -- e.g. the 
-z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} -- where the 
-adrenoceptor distribution should be investigated. Then the pipette could be used for stimulating 
-the receptor to produce cyclic adenosine monophosphate (cAMP) or cyclic guanosine monophosphate 
-(cGMP) \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes its 
-conformation and a FRET signal could be detected \cite{Nikolaev2010}.
 

### 2020-10-13 sections/correlated-sicm-and-fm.tex
Added Lyon2012 as a further example for SSCM

@@
 type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
-differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been
-utilized in studies investigating endocytotic pathways \cite{Shevchuk2008}
-(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
+differentiation of stem cells \cite{Gorelik2008}. The SSCM has also been used for correlating 
+topography and t-tubule distribution in cardiomyocytes \cite{Lyon2012}. 
+Furthermore, it has been utilized in studies investigating endocytotic pathways 
+\cite{Shevchuk2008} (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
 mechanism for clathrin-coated pits by recording topography simultaneously with

### 2020-10-13 sections/correlated-sicm-and-fm.tex
Including a short paragraph: SICM+SNOM/NSOM

@@
 \end{figure}
+
 Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
@@
 \cite{Schobesberger2020}.
+
+In contrast to combining SICM with wide-field microscopy techniques, SICM could be also 
+combined with near-field optical microscopy techniques (SNOM/NSOM) 
+\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002}.
 

### 2020-10-13 sections/correlated-sicm-and-fm.tex
some minor changes

--- 2020-10-13 sections/correlated-sicm-and-fm.tex
@@
 the fluorescence of tagged actin-binding protein and the tagged
-clathrin light-chain \cite{Shevchuk2012}. A further study on clathrin-coated
-pit formation and maturation revealed the effect of mutations in the Dynamin~2
+clathrin light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated endocytosis revealed the effect of mutations in the Dynamin~2
 gene on the maturation and internalisation of clathrin coated pits \cite{Ali2019}.
@@
 
-By using a special illumination system consisting of a light emitting diode (LED) light ring, SICM 
-could also being combined with condenser-free phase contrast, darkfield and brightfield images and 
-even Rheinberg illuminations were possible \cite{Webb2014}.
+% By using a special illumination system consisting of a light emitting diode (LED) light ring, SICM 
+% could also being combined with condenser-free phase contrast, darkfield and brightfield images and 
+% even Rheinberg illuminations were possible \cite{Webb2014}.
 

### 2020-10-13 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Added Piper2006 -> SICM-nanopipette as a fluorescence-based nanosensor
Update correlated-sicm-and-fm.tex
Adding Schultz2019 as an example for SSCM

--- 2020-10-13 sections/correlated-sicm-and-fm.tex
@@
 differentiation of stem cells \cite{Gorelik2008}. The SSCM has also been used for correlating 
-topography and t-tubule distribution in cardiomyocytes \cite{Lyon2012}. 
-Furthermore, it has been utilized in studies investigating endocytotic pathways 
-\cite{Shevchuk2008} (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
-mechanism for clathrin-coated pits by recording topography simultaneously with
+topography and t-tubule distribution in cardiomyocytes \cite{Lyon2012} or for investigating 
+intracellular contacts by correlating topography with the distribution of connexin-43 (Cx43) 
+\cite{Schultz2019}. Furthermore, it has been utilized in studies investigating endocytotic 
+pathways \cite{Shevchuk2008} (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative 
+closing mechanism for clathrin-coated pits by recording topography simultaneously with
 the fluorescence of tagged actin-binding protein and the tagged
@@
 
+% Piper2006 -> PMID: 17177370
+The SICM-nanopipette could be also used as a nanosensor for pH- or ionic concentration changes 
+\cite{Piper2006}. In this study fluorophores were trapped in the nanopipette and react on changes 
+of the pH value or the concentration of ions with alterations in the detected fluorescence signal.
+
 % Dieser Abschnitt passt nicht so wirklich zu Fluoreszenz-Mikroskopie! Vielleicht noch so was 

### 2020-10-13 sections/correlated-sicm-and-fm.tex
integrated the SNOM part into "what we will not review"

--- 2020-10-13 sections/correlated-sicm-and-fm.tex
@@
 focus on applications were SICM and FM data has been recorded from the same
-sample.
+sample. Furthermore, we focus on far-field FM techniques and do not review the
+combination of SICM with nearfield optical microscopy  
+\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002}.
 
@@
 type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
-differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been
-utilized in studies investigating endocytotic pathways \cite{Shevchuk2008}
-(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
-mechanism for clathrin-coated pits by recording topography simultaneously with
+differentiation of stem cells \cite{Gorelik2008}. The SSCM has also been used for correlating 
+topography and t-tubule distribution in cardiomyocytes \cite{Lyon2012} or for investigating 
+intracellular contacts by correlating topography with the distribution of connexin-43 (Cx43) 
+\cite{Schultz2019}. Furthermore, it has been utilized in studies investigating endocytotic 
+pathways \cite{Shevchuk2008} (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative 
+closing mechanism for clathrin-coated pits by recording topography simultaneously with
 the fluorescence of tagged actin-binding protein and the tagged

### 2020-10-13 sections/correlated-sicm-and-fm.tex
Moved Schultz2019 to SICM/confocal since it is not surface scanning

@@
 the activity of the platelets and the structure of the cytoskeleton.
+In co-cultures of cardio-myocytes and myofibroblasts, the dynamics of
+myocyte-myofibroblast connection was linked to the expression of connexin-43
+\cite{Schultz2019}.
 
@@
 uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
-type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
-differentiation of stem cells \cite{Gorelik2008}. The SSCM has also been used for correlating 
-topography and t-tubule distribution in cardiomyocytes \cite{Lyon2012} or for investigating 
-intracellular contacts by correlating topography with the distribution of connexin-43 (Cx43) 
-\cite{Schultz2019}. Furthermore, it has been utilized in studies investigating endocytotic 
-pathways \cite{Shevchuk2008} (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative 
-closing mechanism for clathrin-coated pits by recording topography simultaneously with
-the fluorescence of tagged actin-binding protein and the tagged
-clathrin light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated endocytosis revealed the effect of mutations in the Dynamin~2
-gene on the maturation and internalisation of clathrin coated pits \cite{Ali2019}.
+type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014}, for investigating
+the differentiation of stem cells \cite{Gorelik2008} and the correlation of
+topography and T-tubule distribution in cardiomyocytes \cite{Lyon2012} during
+recovery from heart failure. Furthermore, it has been utilized in studies
+investigating endocytotic pathways \cite{Shevchuk2008}
+(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
+mechanism for clathrin-coated pits by recording topography simultaneously with
+the fluorescence of tagged actin-binding protein and the tagged clathrin
+light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated
+endocytosis revealed the effect of mutations in the Dynamin~2 gene on the
+maturation and internalisation of clathrin coated pits \cite{Ali2019}.
 

### 2020-10-13 sections/correlated-sicm-and-fm.tex
commented the nanoinjection section. Is it really necessary?

@@
 In co-cultures of cardio-myocytes and myofibroblasts, the dynamics of
-myocyte-myofibroblast connection was linked to the expression of connexin-43
+myocyte-myofibroblast connections was linked to the expression of connexin-43
 \cite{Schultz2019}.
@@
 could be performed simultaneously, but not synchronously.
-
-%% Wenn ich das Paper richtig verstehe, wurde hier aber kein konfokales FM
-%% genutzt, oder? 
-%
-% Nashimoto et al. investigated whether the secretion of the von 
-% Willebrand factor from living cells can be investigated by SICM without any
-% additional labeling. , it is not always necessary to label the protein. Even with SICM alone the 
-% detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
-% images \cite{Nashimoto2015}.
-
-% \subsection{\emph{Indirect} combination of SICM and FM}
-
-% Beside \emph{direct} combinations in one instrument and correlations, which are displaying 
-% images obtained by SICM and fluorescence microscopy of the same cell/same region, also 
-% \emph{indirect} correlations exist. They are showing images under comparable conditions and 
-% extent the investigation to aspects, which could not be obtained by using one technique alone. 
-% Such \emph{indirect} correlations were used for investigating the uptake of nanotubes 
-% \cite{Lee2013}, nanoparticles \cite{Gesper2017} or for investigating healthy and failing 
-% myocytes \cite{Lyon2009}. Nevertheless is it important to mention, that they could just giving 
-% hints of correlations, it is not directly comparable with investigations of both in the same 
-% cell.
 
@@
 
-% Bis hier
-
 SSCM has been used for investigating the dynamics of the interaction of
@@
 
-\subsection{Nanoinjection of fluorescently labeled molecules}
+% Bis hier
 
-Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
-the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
-fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
-could be also used for nanoinjection of fluorescently labeled molecules into living cells 
-\cite{Hennig2015a}. The SICM was therefore combined with wide-field and direct stochastic 
-optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
-stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
-introduced into the membranes, could occur \cite{Hennig2015a}.
+% \subsection{Nanoinjection of fluorescently labeled molecules}
 
-The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
-combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
-In both studies the scanning ion conductance microscope was combined with TIRF investigations and 
-the diffusion of single molecules over different regions at a spermatozoa were investigated.
+% Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
+% the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
+% fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
+% could be also used for nanoinjection of fluorescently labeled molecules into living cells 
+% \cite{Hennig2015a}. The SICM was therefore combined with wide-field and direct stochastic 
+% optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
+% stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
+% introduced into the membranes, could occur \cite{Hennig2015a}.
 
-The SICM-nanopipette could be also used for investigating membrane rafts 
-\cite{Simons1997,Pike2006} by coordinated manipulation of focal adhesions. The pipette was 
-functionalized with fibronectin, gangliosides were fluorescently labeled, the pipette deformed the 
-focal adhesion side and the behavior of the fluorescently labeled gangliosides were detected. This 
-was seen as a hint, how membrane rafts reacted \cite{Fuentes2012}.
+% The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
+% combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
+% In both studies the scanning ion conductance microscope was combined with TIRF investigations and 
+% the diffusion of single molecules over different regions at a spermatozoa were investigated.
 
-Another example for a SICM-nanopipette based manipulation could be found in the study on the 
-generation and distribution of plasma-derived extracellular vesicles (PEVs) on MDA-MB-231 and U87 
-cells. Here the nanopipette were used for both, investigating the topography and for inducing the 
-generation of the PEVs. Additionally the SICM was build up onto a confocal microscope, which could 
-be used for the detection of Calcium \cite{Wang2020}.
+% The SICM-nanopipette could be also used for investigating membrane rafts 
+% \cite{Simons1997,Pike2006} by coordinated manipulation of focal adhesions. The pipette was 
+% functionalized with fibronectin, gangliosides were fluorescently labeled, the pipette deformed the 
+% focal adhesion side and the behavior of the fluorescently labeled gangliosides were detected. This 
+% was seen as a hint, how membrane rafts reacted \cite{Fuentes2012}.
 
-% Piper2006 -> PMID: 17177370
-The SICM-nanopipette could be also used as a nanosensor for pH- or ionic concentration changes 
-\cite{Piper2006}. In this study fluorophores were trapped in the nanopipette and react on changes 
-of the pH value or the concentration of ions with alterations in the detected fluorescence signal.
+% Another example for a SICM-nanopipette based manipulation could be found in the study on the 
+% generation and distribution of plasma-derived extracellular vesicles (PEVs) on MDA-MB-231 and U87 
+% cells. Here the nanopipette were used for both, investigating the topography and for inducing the 
+% generation of the PEVs. Additionally the SICM was build up onto a confocal microscope, which could 
+% be used for the detection of Calcium \cite{Wang2020}.
+
+% % Piper2006 -> PMID: 17177370
+% The SICM-nanopipette could be also used as a nanosensor for pH- or ionic concentration changes 
+% \cite{Piper2006}. In this study fluorophores were trapped in the nanopipette and react on changes 
+% of the pH value or the concentration of ions with alterations in the detected fluorescence signal.
 

### 2020-10-13 sections/correlated-sicm-and-srfm.tex
commented the last paragraph, is included in the first one

@@
 
-As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
-with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015a}. The difference to the 
-SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
-fluorescently labeled molecules -- ATTO 655-phalloidin -- into living U2OS cells.
+% As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
+% with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015a}. The difference to the 
+% SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
+% fluorescently labeled molecules -- ATTO 655-phalloidin -- into living U2OS cells.
 

### 2020-10-14 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Ich habe den "Nanoinjection"-Teil in 2 Sätzen zusammengefasst. 
Der ist jetzt da zu finden, wo wir schon sagen, dass wir nichts über SNOM und so sagen werden.

@@
 combination of SICM with nearfield optical microscopy  
-\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002}.
+\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002}. We also do not review
+studies, that use the nanopipette for targeted deposition 
+\cite{Ying2002,Bruckbauer2007,Bruckbauer2010,Hennig2015} or for injection 
+\cite{Hennig2015a} of fluorescent/fluorescently-labeled molecules. As well, as studies, 
+where the nanopipette was used for manipulation \cite{Fuentes2012,Wang2020} or as a 
+fluorescence-based nanosensor \cite{Piper2006}.
+
+% Vielleicht können wir die letzten beiden Sätze (siehe Absatz darüber) noch einfügen, 
+% dann würde das so aussehen, dass die Entscheidung, über diesen Bereich nicht zu berichten 
+% gezielt war und nicht dass wir sie vergessen hätten!?
 

### 2020-10-14 sections/pitfalls.tex
Complete rework, shortened.

--- 2020-10-05 sections/pitfalls.tex
@@
-\section{Potential Pitfalls}
+\section{Outlook}
 \label{sec:pitfalls}
 
-\begin{figure}
-  \sidecaption
-  \includegraphics{gr/pitfalls/CombinedMicroscopy}%
-  \caption{\textbf{Potential implementations of combined SICM and FM.} 
-  			\textit{Left:} Schematic depiction of potential combined SICM 
-  			and TIRF or standard wide-field microscopy (\textit{top}),
-  			SICM and z-stacking (\textit{middle}) and SICM and surface
-  			scanning (\textit{bottom}). 
-  			\textit{Right:} Resulting correlating data of these combinations.}
-  \label{fig:CombinedMicroscopy}
-\end{figure}
+In the previous sections, we have reviewed the combination of SICM and FM and
+have shown that this combination allows to gather new insights into the
+physiology of living cells. However, despite the mismatch in resolution, most
+of these studies combine SICM and diffraction limited FM. Even other scanning
+probe techniques such as atomic force microscopy, which has a much larger user
+base than SICM, have been combined with SRFM only in a few studies
+\cite{Harke2012,Chacko2013,Chacko2013b,Odermatt2015,Curry2017,Hirvonen2018}.
 
-Combining SRFM and SICM in one setup is bound to bring up some potential
-pitfalls, some of which are discussed in the following:
+We can only speculate about the reasons for this. In its most simple
+implementation, SICM and SRFM data could be recorded on two different
+instruments subsequently \cite{Hagemann2018}. The major problem with this
+approach is finding the same region of the sample in both instruments. Here,
+strategies from correlating FM and electron microscopy (recently reviewed for
+example in \cite{Begemann2016}) might be adapted. A second drawback when using
+TIRF-based methods such as PALM or STORM is the limited penetration depth of
+the excitation beam, which only allows recording fluorescence data close to
+the interface between sample and cell culture dish. However, approaches
+allowing 3D imaging by localisation microscopy exist
+\cite{Huang2008a,Huang2008} and might allow to circumvent this limit.
 
-To avoid some problems from the beginning, both the SRFM and SICM setups
-should provide spatial resolutions in the same range. Also, if possible, one
-software should be used to control both setups to prevent delays in the
-imaging process due to ... (?)
+% Instead of having to worsen SICM resolution to match FM resolution, it might be 
+% reasonable to combine SICM and SRFM in one setup. Though, this implementation
+% comes with its own potential pitfalls, especially as due to the super resolution
+% of both techniques small deviations or disturbances are sufficient to ruin the 
+% alignment of the setup. Some of these potential pitfalls are discussed in the 
+% following:
 
-Some potential pitfalls can arise when aligning the SRFM and SICM
-setups. There are two alignment options: The first one is aligning the pipette
-tip and the laser beam only in the xy plane, e.g. for imaging fluorescent
-proteins in the cytoskeleton and the cell membrane simultaneously. The second
-one is additionally aligning the tip and beam in the z plane, e.g. to image
-cell membrane and fluorescent particles or proteins within the membrane
-simultaneously, as has been done in SSCM \cite{Gorelik2002a}\cite{Shevchuk2008}.
+% To avoid some problems from the beginning, both the SRFM and SICM setups
+% should provide spatial resolutions in the same range. Also, if possible, one
+% software should be used to control both setups to prevent delays in the
+% imaging process due to transmitting information from one software to the other.
 
-Especially the second option tracing the cell surface would require constant
-focal plane adjustment of the optical setup. This might eventually lead to a
-mismatch in the excitation and depletion beam superimposition.
+In the case of combining SICM with a scanning technique such as STED, there
+are two alignment options: The first one is aligning the pipette tip and the
+laser beam only in the $x,y$ plane. This is comparable, in terms of data
+recording, to the above mentioned combinations of SICM and wide-field or
+confocal microscopy.  The second one, surface scanning, requires the
+additional alignment of the tip and, in case of STED, the two beams in the
+$z$-plane.
 
-It has to be put into consideration whether fine adjustment screws are enough
-to align the pipette and the beam. It is apparently sufficient for aligning
-SICM and confocal microscopes (??). In case it isn't accurate enough piezo
-elements might have to be used. However, the usage of 3 piezo elements mounted
-to the same platform, may it be the pipette holder or sample stage, is
-reported to have caused cross-talk during sample positioning leading to image
-artifacts in the range of 100 nm \cite{Shevchuk2013}. Hence, it would be
-better to uncouple xy piezos from the z piezo. Furthermore, z piezos come with
-an increased risk of piezo drift. Therefore, especially the sample stage
-should ideally avoid z piezo usage.
+Especially the second option would require repeated
+focal plane adjustment of the optical setup. In turn, this requires meticulous
+alignment of the excitation and depletion beam to retain the super-imposition
+of the two beams during the adjustment of the focal plane. To minimize the
+pixels that require an adjustment of the focal plane, the adjustment has been
+only applied if a $z$-range of more than one micrometer was exceeded
+\cite{Novak2014}. If STED recordings with increased vertical resolution are
+intended, the acceptable range for not adjusting the focal plane decreases,
+which in turn might lead to longer and less stable recordings.
 
-Both alignment options may lead to the pipette tip reflecting the beam and
-thereby distorting the resulting recordings. In this case the pipette tip
-would have to be retracted until it can't reflect the beam light anymore,
-before a recording with the optical setup can be executed. Consequently, this
-means the SRFM and the SICM recording can't be executed simultaneously but
-successively.
+Due to the increased horizontal resolution, even the $x,y$-alignment of SICM
+pipette and the laser beams becomes more challenging since the tolerable
+offset between the two decreases. While it has been reported that fine
+adjustment screws are sufficient to align the pipette and the beam in the
+combination of SICM and confocal microscopes \cite{Gorelik2002a,
+  Shevchuk2008,Novak2014}, additional piezo elements might be required for the
+alignment of STED and SICM.
 
-While this might seem like a drawback extending the overall recording time, it
-also solves another problem that comes with combining SRFM and SICM:
-photo-bleaching and photo-damage of the sample. SRFM techniques like STED
-microscopy come with a general risk of photo-bleaching and -damage as high
-intensity lasers are used. Combining SRFM with SICM increases this risk,
-as SICM is a much slower imaging technique. The pipette will not only have to
-be moved in the xy plane but also in the z plane to avoid sample
-contact. Hence, the imaging speed will mostly be dependent on the SICM
-capillary speed especially in z direction. If the sample is illuminated by the
-laser continuously during capillary approach and retraction, photo-bleaching
-and -damage is likely to occur. Therefore, illuminating the sample right after
-SICM surface detection, recording and pipette retraction for a short period of
-time would not only result in reflection avoidance but also in less
-photo-bleaching and -damage. In case, light reflection by the scanning
-capillary doesn't occur, the sample could be illuminated right after surface
-detection leading to a faster imaging speed of the combined setup.
+If the depletion laser and the pipette tip are aligned in all three
+dimensions, the pipette tip might reflect the depletion beam. Since the
+intensity of the beam is large to achieve a high resolution, the reflected
+light might not be completely filtered by the filters in the emission beam
+path. In this case, the pipette would have to be retracted first before the
+recording of the fluorescence data could be performed.
 
-The switching of the laser beams could either be done via mechanical
-shutters. However, as mechanical shutters have a limited switching frequency,
-it might be preferential to switch beams by switching akkusto-optical modulators.
+This, in turn, requires a precise control of the data acquisition by the two
+imaging methods, which can be only obtained by a designated controlling soft-
+and hardware.
 
-Another problem stemming from capillary movement is the resonance of the
-pipette resulting from it. Some groups have ensured resonance reduction by
-using a v-groove mounting plate for the capillary instead of the conventional
-patch clamp pipette holders \cite{Shevchuk2013}.
+In summary, the development of combined SICM and SRFM instruments has just
+begun, and several technical hurdles have to be overcome during the
+further development. However, there are no fundamental contradictions that
+would hinder the combination of SICM and SRFM. Therefore, we expect this field
+of research to grow in the near future.
 

### 2020-10-14 sections/correlated-sicm-and-fm.tex
reworked Astrid'S paragraph

@@
 combination of SICM with nearfield optical microscopy  
-\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002}. We also do not review
-studies, that use the nanopipette for targeted deposition 
+\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002} or studies where
+the SICM pipette is used for targeted deposition 
 \cite{Ying2002,Bruckbauer2007,Bruckbauer2010,Hennig2015} or for injection 
-\cite{Hennig2015a} of fluorescent/fluorescently-labeled molecules. As well, as studies, 
-where the nanopipette was used for manipulation \cite{Fuentes2012,Wang2020} or as a 
-fluorescence-based nanosensor \cite{Piper2006}.
+\cite{Hennig2015a} of molecules, as a nano-sensor \cite{Piper2006} or for manipulating the sample
+\cite{Fuentes2012,Wang2020}.
 

### 2020-10-14 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Added Miragoli2016 in SSCM part

@@
 the differentiation of stem cells \cite{Gorelik2008} and the correlation of
-topography and T-tubule distribution in cardiomyocytes \cite{Lyon2012} during
-recovery from heart failure. Furthermore, it has been utilized in studies
-investigating endocytotic pathways \cite{Shevchuk2008}
+topography and T-tubule distribution \cite{Lyon2012} or topography and
+mitochondria localization and appearance \cite{Miragoli2016} in healthy and 
+heart-failure cardiomyocytes. Furthermore, it has been utilized in 
+studies investigating endocytotic pathways \cite{Shevchuk2008}
 (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing

### 2020-10-15 sections/correlated-sicm-and-fm.tex
minor

--- 2020-10-14 sections/correlated-sicm-and-fm.tex
@@
 view, the different pixel sizes and the different times required to record one
-image, the two data sets are not recorded synchronously and thus cannot by
+image, the two data sets are not recorded synchronously and cannot be
 correlated pixel-by-pixel. Technically, the combination is simple, since
@@
   \caption{
-    \textbf{a:}\textbf{b:}\textbf{c:}\textbf{d:}\textbf{e:}\textbf{f:}
+    \textbf{a:} SICM recording of a cardio-myocyte which was subsequently
+    tested for the occurrence of the $\beta_1$-AR at the crest (\textbf{b})
+    and at the T-tubule (\textbf{c}). 
+    \textbf{d:} SICM recording of a cardio-myocyte which was subsequently
+    tested for the occurrence of the $\beta_2$-AR at the crest (\textbf{d})
+    and at the T-tubule (\textbf{e}).
+    Reprinted with permission from ref. \cite{Nikolaev2010}.
   }
@@
 Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
-crests (Fig.~\ref{fig:nikolaev2010}a, b). By first recording the topography
+crests (Fig.~\ref{fig:nikolaev2010}a, d). By first recording the topography
 and subsequently moving the SICM pipette to either a T-tubule or a crest,
@@
 and yellow fluorescent protein, coupled to a Förster resonance energy transfer
-(FRET) based reporter of cyclic AMP (Fig.~\ref{fig:nikolaev2010}c--f), it was
+(FRET) based reporter of cyclic AMP (Fig.~\ref{fig:nikolaev2010}b, c, e, f), it was
 shown that the distribution of the $\beta_2$-AR was altered in failing
@@
 \begin{figure}
-  \includegraphics[width=\textwidth]{gr/correlating/sicm+cfm}
+  \includegraphics[width=\textwidth]{gr/correlating/sicm+cfm2}
   \caption{%
     \textbf{Combining SICM and confocal fluorescence microscopy.}
-    \textbf{a:} Schematic illustration of the correlating data acquired by combining SICM and confocal FM.
+    \textbf{a:} Schematic illustration of the data acquired by combining SICM and confocal FM.
     \textbf{b:} 
-    	\textit{Left:} Topography of a neuronal network.
-    	\textit{Middle:} Fluorescence of the same neuronal network as depicted on the left.
-    	\textit{Right:} Overlay of topography and fluorescence of two regions of interest (ROI 1, ROI 2) from
+    	(left:) Topography of a neuronal network.
+    	(center:) Fluorescence of the same neuronal network as depicted on the left.
+    	(right:) Overlay of topography and fluorescence of two regions of interest (ROI 1, ROI 2) from
     	the left and middle image.

### 2020-10-15 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Added figure description Nikolaev2010
Information on the rights for reprinting is missing! 
Needs to be updated!!!

--- 2020-10-14 sections/correlated-sicm-and-fm.tex
@@
   \caption{
-    \textbf{a:}\textbf{b:}\textbf{c:}\textbf{d:}\textbf{e:}\textbf{f:}
+    \textbf{Distribution of $\beta_1$- and $\beta_2$-adrenergic receptors (AR) on the surface of cardiomyocytes obtained from healthy rats.}
+    \textbf{a:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, where the stimulation of the $\beta_1$-AR was take place.
+    \textbf{b:} F\"orster resonance energy transfer (FRET) YFP/CFP (yellow and cyan fluorescent protein) ratio after $\beta_1$-AR stimulation in the crest of the cell (a). 
+    \textbf{c:} FRET YFP/CFP ratio after $\beta_1$-AR stimulation in the T-tubule of the cell (a).
+    \textbf{d:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, where the stimulation of the $\beta_2$-AR was take place. 
+    \textbf{e:} FRET YFP/CFP ratio after $\beta_2$-AR stimulation in the crest of the cell (c).
+    \textbf{f:} FRET YFP/CFP ratio after $\beta_2$-AR stimulation in the T-tubule of the cell (c).
+    ICI: ICI118551 is a $\beta_2$-AR antagonist; CGP: CGP20712A is a $\beta_1$-AR antagonist
+    A decrease in the FRET YFP/CFP ratio between YFP and CFP indicates an increase in cAMP.
   }

### 2020-10-15 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Minor revisions in the figure description of Nikolaev2010

@@
   \caption{
-    \textbf{Distribution of $\beta_1$- and $\beta_2$-adrenergic receptors (AR) on the surface of cardiomyocytes obtained from healthy rats.}
-    \textbf{a:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, where the stimulation of the $\beta_1$-AR was take place.
-    \textbf{b:} F\"orster resonance energy transfer (FRET) YFP/CFP (yellow and cyan fluorescent protein) ratio after $\beta_1$-AR stimulation in the crest of the cell (a). 
-    \textbf{c:} FRET YFP/CFP ratio after $\beta_1$-AR stimulation in the T-tubule of the cell (a).
-    \textbf{d:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, where the stimulation of the $\beta_2$-AR was take place. 
-    \textbf{e:} FRET YFP/CFP ratio after $\beta_2$-AR stimulation in the crest of the cell (c).
-    \textbf{f:} FRET YFP/CFP ratio after $\beta_2$-AR stimulation in the T-tubule of the cell (c).
+    \textbf{Distribution of $\beta_1$- and $\beta_2$-adrenergic receptors (AR) on the surface of 
+    cardiomyocytes obtained from healthy rats.}
+    \textbf{a:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, 
+    where the stimulation of the $\beta_1$-AR was take place.
+    \textbf{b:} F\"orster resonance energy transfer (FRET)-YFP/CFP (yellow and cyan fluorescent 
+    protein)-ratio after $\beta_1$-AR stimulation in the crest of the cell (a). 
+    \textbf{c:} FRET-YFP/CFP-ratio after $\beta_1$-AR stimulation in the T-tubule of the cell (a).
+    \textbf{d:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, 
+    where the stimulation of the $\beta_2$-AR was take place. 
+    \textbf{e:} FRET-YFP/CFP-ratio after $\beta_2$-AR stimulation in the crest of the cell (c).
+    \textbf{f:} FRET-YFP/CFP-ratio after $\beta_2$-AR stimulation in the T-tubule of the cell (c).
     ICI: ICI118551 is a $\beta_2$-AR antagonist; CGP: CGP20712A is a $\beta_1$-AR antagonist
-    A decrease in the FRET YFP/CFP ratio between YFP and CFP indicates an increase in cAMP.
+    A decrease in the FRET-YFP/CFP-ratio indicates an increase in cyclic adenosine monophosphate 
+    (cAMP).
+    % The rights need to be added here.
   }

### 2020-10-17 sections/introduction.tex
changed text to match new figures

@@
 
-\begin{figure}
-  \sidecaption[t]
+\begin{figure}\centering
   \includegraphics{gr/intro/Fig_SICM-resolution}
-  \caption{\textbf{Resolution of SICM.} \textbf{a:} Height profiles (plotted
-    vertically) of modelled SICM recordings of two cilindrical particles
-    (height and diameter: $r_\text{i}$) at varying distances. \textbf{b:} Two
-    consecutive SICM recordings of the equatorial segment of a living boar
-    spermatozoon recorded 10 minutes apart with a scanning pipette with
-    $r_\mathrm{i} \approx 6.75\,\text{nm}$. \textbf{a:} reprinted with
-    permission from ref. \cite{rheinlaender:094905}, \textbf{b:} reprinted
-    with permission from ref. \cite{Shevchuk2006}. 
-  }
+  \caption{\textbf{Resolution of SICM.}  \textbf{a:} Height profiles
+    (plotted vertically) of modelled SICM recordings of two cilindrical
+    particles (height and diameter: $r_\text{i}$) at varying
+    distances. \textbf{b:} Apparent height of the particles (solid line) and of
+    the gap between them (dahsed line) as determined by SICM. At distances
+    $d\lessapprox3r_\text{i}$, no gap between the particles is detected.
+    Reprinted from Johannes Rheinlaender, Tilman E. Schäffer: \emph{Image
+      formation, resolution, and height measurement in scanning ion
+      conductance microscopy}, Journal of Applied Physics 2009, 105(9), with
+    the permission of AIP Publishing.  }
   \label{fig:sicm-resolution}
@@
 openings. Pipettes with radii of approximately 6.75\,nm have been used in for
-SICM imaging (Fig.~\ref{fig:sicm-resolution}b) \cite{Shevchuk2006}. In
+SICM imaging \cite{Shevchuk2006}. In
 contrast, the resolution in light microscopy is fundamentally limited by the
@@
 limit is in the range of 200\,nm. This is approximately 14 times the size of
-the smallest structures observed in the SICM recordings shown in
-Fig.~\ref{fig:sicm-resolution}B, which were reported to be 14\,nm
+the smallest structures observed in the SICM recordings, which were reported to be 14\,nm
 \cite{Shevchuk2006}.
@@
 \begin{figure}
-  \sidecaption
-  \includegraphics{gr/intro/Fig_SICM-and-Light-resolution}%
-  \caption{\textbf{Hypothetical fluorescence analysis of proteins in the boar
-      spermatozoon.} \textbf{a:} Proteins A and B in the stable structures
-    observed by SICM. \textbf{b:} Hypothetical positions of the fluorescent
-    labels of proteins A and B. Scale bar: 200\,nm \textbf{c:} Computed
-    fluorescence image, resolutions were 250\,nm for the magenta and 300\,nm
-    for the green marker.}
+  \centering
+  \includegraphics{gr/intro/effect-of-resolution}%
+  \caption{\textbf{Hypothetical fluorescence analysis of a protein forming
+      membrane protrusions.} \textbf{a:} SICM recording of membrane protrusion
+    and location of a putative protein within it. \textbf{b:} Computed
+    diffraction limited fluorescence recording of the protein with a resolution
+    of 250\,nm. \textbf{c:} Computed
+    diffraction unlimited fluorescence recording of the protein with a
+    resolution of 75\,nm.}
   \label{fig:sicm-and-light-resolution}
 \end{figure}
-In all stable structures in the recordings (highlighted by the dashed lines)
-at least one group of three protrusions arranged in a line are observable. To
-exemplify the impact of the limited resolution of light microscopy, assume,
-without any biological support, that such a complex is comprised of two
-different proteins A and B, which float in the plasma membrane until they form
-the complex. In the complex, protein A is located at the first and last
-position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and
-protein B on the central spot (green arrows in
-Fig.~\ref{fig:sicm-and-light-resolution}a). Further, assume that the two
-different proteins have been labelled by two different fluorescent markers
-(the positions of the markers are indicated by the magenta and green dots in
-Fig.~\ref{fig:sicm-and-light-resolution}b) and a correlating light microscopic
-image has been recorded (Fig.~\ref{fig:sicm-and-light-resolution}c) to analyze
-the molecular composition of the stable structures.
 
-Due to the limited resolution, the fluorescence image consists of overlapping
-spots of the two different markers and looks blurred, compared to the
-SICM topography image. Although co-localisation of the two proteins can be
-observed at the positions of the stable structures, it is hard if not
-impossible to allocate the fluorescent spots to protrusions in the topography
-image.
+To exemplify the impact of the limited resolution of light microscopy, assume,
+without any biological support, that a cellular protrusion as shown in
+Fig.~\ref{fig:sicm-and-light-resolution}a is formed by a protein (black line
+in Fig.~\ref{fig:sicm-and-light-resolution}a). A -- hypothetical --
+diffraction limited recording of that protein would only show a blurred spot
+(Fig.~\ref{fig:sicm-and-light-resolution}b), while a recording with an
+improved resolution would clearly allow to see that the location of the
+protein correlates with the position of the protrusion
+(Fig.~\ref{fig:sicm-and-light-resolution}c).
 

### 2020-10-18 manuscript.tex
slight change in abstract, re-ordered authors

@@
 
+\newcommand\todo[1]{\marginpar{\small\itshape\textcolor{red}{#1}}}
 \begin{document}
@@
 
-\author{Annika Haak, Astrid Gesper and Patrick Happel}
+\author{Patrick Happel \and Annika Haak \and Astrid Gesper}
 \authorrunning{Haak et al.}
@@
 %
-  The latter, however, is a unique strength of scanning ion conductance
+  Investiganting the cell membrane is a unique strength of scanning ion conductance
   microscopes (SICM),
   which use a fine tip to determine the topography of the investigated sample
-  and thus allow to investigate the cell membrane without labelling.    
+  and thus allows to investigate the cell membrane without labelling.    
 %  
@@
 %  
-  Here we briefly introduce the different approaches to Super-Resolved
+  Here, we briefly introduce the different approaches to Super-Resolved
   Fluorescence Microscopy (SRFM) and review the applications of correlating SICM

### 2020-10-18 sections/correlated-sicm-and-srfm.tex
minor
reworked

@@
 \label{sec:correlating-sicm-and-srfm}
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "../manuscript"
-%%% End:
 
-In contrast to the combination of AFM and SRFM, the development of correlated
+The development of correlated
 SICM and SRFM is still in its very early stages. The first combination of SRFM
@@
 
-In the latter, the topography of a group of fixed HeLa has been investigated by SICM
-(Fig.~\ref{fig:SICM_STED1}a) and, subsequently, the cytoskeletal protein actin by 
-confocal and STED microscopy (Fig.~\ref{fig:SICM_STED1}b). The area of the
-sample imaged by both methods is marked in Fig.~\ref{fig:SICM_STED1}c (SICM: yellow 
+In the latter, the topography of a group of fixed HeLa has been investigated
+by SICM (Fig.~\ref{fig:SICM_STED1}a) and, subsequently, the distribution of
+the cytoskeletal protein actin was determined by confocal and STED microscopy
+(Fig.~\ref{fig:SICM_STED1}b) on a second instrument. The area of the sample
+imaged by both methods is marked in Fig.~\ref{fig:SICM_STED1}c (SICM: yellow
 rectangle, STED: gray rectangle).
@@
       \textbf{Correlative SICM and STED recording of a group of HeLa cells.} 
-      (\textbf{Aa}) SICM recording of the HeLa cells, (\textbf{Ab}) slope representation of the
-      SICM recording. Confocal (\textbf{Ba}) and STED (\textbf{Bb}) recording of the region marked 
-      with a black dotted line in \textbf{Aa} and \textbf{Ab}. (\textbf{C}) Relative position of 
-      the SICM (yellow rectangle) and the confocal/STED (gray rectangle) images against each 
-      other. Magnification of the STED (\textbf{Da}), confocal (\textbf{Db}), SICM (\textbf{Dd}) 
-      and slope (\textbf{De}) images. The region, that is magnified, is marked with a white 
-      arrowhead in \textbf{Aa, Ab, Ac and Ad}. (\textbf{Df} and (\textbf{Dg}) show an overlay of 
-      the STED with the SICM (\textbf{Df}) or the slope representation (\textbf{Dg}). 
-      (\textbf{Dc}) Height profile along the white dotted line in \textbf{Dd}. \newline Reprinted 
-      with permission from \emph{Philipp Hagemann*, Astrid Gesper*, Patrick Happel}, Correlative 
-      stimulated emission depletion and scanning ion conductance microscopy, \emph{ACS Nano} 2018, 
-      12, 5807-5815, DOI: 10.1021/acsnano.8b01731. Copyright 2020 American Chemical Society}
+      \textbf{a:} Height (aa) and slope representatin (ab) of a SICM recording
+      of HeLa cells. \textbf{b:} Confocal (ba) and STED (bb) recording of the
+      region marked  
+      with a black dotted line in a. \textbf{c:}  Relative position of 
+      the SICM (yellow rectangle) and the confocal/STED (gray rectangle)
+      images with respect to  each 
+      other. \textbf{d:} Magnification of the STED (da), confocal  (db), SICM
+      (dd) and slope (de) images. The magnified region is marked with a white 
+      arrowhead in a and b. \textbf{df} and \textbf{dg} show an overlay of 
+      the STED and the SICM data. 
+      \textbf{Dc} shows the height profile along the white dotted line in dd.  Reprinted 
+      with permission from Philipp Hagemann, Astrid Gesper, Patrick Happel: \emph{Correlative 
+      stimulated emission depletion and scanning ion conductance microscopy.} ACS Nano 2018, 
+      12, 5807-5815. Copyright 2018 American Chemical Society.}
   \label{fig:SICM_STED1}
@@
 while the STED recording revealed that actin was arranged as a ring-shaped
-structure around two central spots. The authors speculate that this structure
-might be involved in the attachement or detachement of the cell from the cell
-culture dish. However, since the recordings were performed on fixed cells, no
-time-lapse data that could support this speculation exist.
+structure around two central spots (Fig.~\ref{fig:SICM_STED1}da). The authors
+speculate that this structure might be involved in the attachement or
+detachement of the cell from the cell culture dish. However, since the
+recordings were performed on fixed cells, time-lapse data that supports this
+speculation could not be obtained.
 

### 2020-10-18 sections/correlated-sicm-and-fm.tex
reworked

--- 2020-10-15 sections/correlated-sicm-and-fm.tex
@@
     \textbf{Combining SICM and wide-field fluorescence microscopy.}
-    \textbf{a:}
-    \textbf{b:} FM image of presynaptic nerve terminals stained with
-    FM1-43. \textbf{c:} Overlay of the FM-image and two SICM recordings of the
-    same region. \textbf{d:} 3D-representation of the lower right SICM
-    recording from c.
-    \textbf{b--d:} Reprinted with permission from ref \cite{Scheenen2015}.
+    \textbf{a:} Sketch of the data obtained by combining SICM and wide-field
+    FM. 
+    \textbf{b:} (left) FM image of a cilium in a RPE-1 cell, (right) SICM recording of
+    the area marked by the dashed rectangle. The cilium is not visible since
+    it is located benaeth the cell membrane \textbf{c:} (left) FM image of a
+    cilium in a MDCK cell, (right) SICM recording of the
+    region marked by the dashed rectangle. The cilium is clearly visible since
+    it protrudes into the extracellular space.
+    \textbf{b, c:} Reprinted with permission from Yuanshu Zhou, Masaki Saito,
+    Takafumi Miyamoto, et al.: \emph{Nanoscale Imaging of Primary Cilia with
+      Scanning Ion Conductance Microscopy.} Anal. Chem. 2018, 90, 4,
+    2891–2895. Copyright 2018 American Chemical Society.
   }
@@
 region of interest such as an area containing active synapses in a culture of
-a neuronal network \cite{Scheenen2015} (Fig.~\ref{fig:sicm+fm}b--d) or to
+a neuronal network \cite{Scheenen2015} or to
 identify the neuron which had been investigated by SICM-guided patch-clamp of
@@
 culture and subsequently use SICM to reveal whether the selected cilium was
-extending into the extracellular space or was embedded in the cell, an
+extending into the extracellular space or was embedded in the cell
+(Fig.~\ref{fig:sicm+fm}b, c), an
 information which could not be retrieved by using FM alone \cite{Zhou2018}.
 
-\begin{figure}
-  \includegraphics[width=\textwidth]{gr/correlating/Nikolaev2010-F2}
-  \caption{
-    \textbf{a:} SICM recording of a cardio-myocyte which was subsequently
-    tested for the occurrence of the $\beta_1$-AR at the crest (\textbf{b})
-    and at the T-tubule (\textbf{c}). 
-    \textbf{d:} SICM recording of a cardio-myocyte which was subsequently
-    tested for the occurrence of the $\beta_2$-AR at the crest (\textbf{d})
-    and at the T-tubule (\textbf{e}).
-    Reprinted with permission from ref. \cite{Nikolaev2010}.
-  }
-  \label{fig:nikolaev2010}
-\end{figure}
-
 Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
-crests (Fig.~\ref{fig:nikolaev2010}a, d). By first recording the topography
+crests. By first recording the topography
 and subsequently moving the SICM pipette to either a T-tubule or a crest,
@@
 and yellow fluorescent protein, coupled to a Förster resonance energy transfer
-(FRET) based reporter of cyclic AMP (Fig.~\ref{fig:nikolaev2010}b, c, e, f), it was
+(FRET) based reporter of cyclic AMP, it was
 shown that the distribution of the $\beta_2$-AR was altered in failing
@@
     	the left and middle image.
-    Reprinted with permission from ref \cite{Novak2013}.
+    Reprinted with permission from P. Novak, J. Gorelik, U. Vivekananda, et
+    al.: \emph{Nanoscale-Targeted Patch-Clamp Recordings of Functional
+      Presynaptic Ion Channels.} Neuron 2013, 79, 1067--1077.
   }
@@
 imaging and topography data \cite{Shevchuk2001}.
-% Afterwards, many different
-% studies using a combination of SICM and confocal FM were published:
 
@@
 
-% ich würde hier etwas zu potentiellen z-stacks + SICM sagen wollen, das hat
-% ja meines Wissens nach noch niemand gemacht...
 The applications reviewed above used only a single confocal layer. Yet,
@@
 \begin{figure}
-  \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}
+  \centering
+  \includegraphics{gr/correlating/sscm_setup}
 
@@
     \textbf{b:} Diagram of the combined setup with a $x,y$ sample scanner and
-    a $z$-probe and objective scanner. 
-    Reprinted with permission from ref \cite{Shevchuk2013}.
+    additional $z$-scanners for probe and objective. 
   }
@@
 In contrast, the second setup (Fig.~\ref{fig:sscm_setup}b) uses the sample
-stage to position the sample in $x$- and $y$-direction only while objective
-and probe are positioned by additional piezo elements in $z$-direction. Thus,
-when the surface is detected by the SICM pipette,  the position of
-the confocal spot has to be adjusted by the objective positioning piezo subsequently.
+stage to position the sample only in $x$- and $y$-direction while objective
+and probe are positioned by additional piezo actors in $z$-direction. Thus,
+when the surface is detected by the SICM pipette, the position of the confocal
+spot has to be adjusted by the objective positioning piezo actor subsequently.
 
@@
 
-Switching from three-axis stage scanning to $z$-movement of the pipette
-allowed for faster scan rates as the resonant frequency of the 3D
-piezo-actor acted as a limiting factor. Additionally, usage of three
-piezo-elements on the same platform led to cross-talk and consequentially
+Switching from three-axis stage scanning to $z$-movement of the pipette and
+objective allowed for faster scan rates since the resonant frequency of the 3D
+scanning stage limited the recording velocity. Additionally, usage of three
+piezo-actors on the same platform led to cross-talk and consequentially
 artefacts in the SICM data \cite{Shevchuk2013}.
@@
 Both setups keep the probe-objective distance constant and enable the
-acquisition of a fluorescence image and a topography of the sample surface in
-the same scan. Photobleaching is equalized for every point of the sample
-allowing quantitative analysis of the FM data.
+acquisition of a fluorescence image and the topography of the sample surface in
+the same scan.
 
@@
     \textbf{a:} Schematic illustration of the correlating data acquired by SSCM.
-    \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
-    VLPs adsorbed to the surface of Cos-7 cells. Reprinted with permission from ref \cite{Gorelik2002a}.
-    \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
-    	\textit{Left:} Cell surface topography. 
-    	\textit{Center:} Fluorescence recording of the cell shown left. 
-    	\textit{Right:} 3D overlay of topographical and fluorescent recordings. 
-    Reprinted with permission from ref \cite{Shevchuk2008}.
-    \textbf{d:} Live Cos-7 cells sequentially scanned by SSCM. Overlays of simultaneously obtained 
-    topographic and fluorescence scans. Fluorescence imaging was started 2\,h 17\,min after the first 
-    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2\,h 40\,min. 
-    Reprinted with permission from ref \cite{Gorelik2002}.
+    \textbf{b:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
+    	(left:) Cell surface topography. 
+    	(center:) Fluorescence recording of clathrin in the cell shown left. 
+    	(right:) 3D overlay of topographical and fluorescent recordings. 
+    Reprinted from Shevchuk, A.I., Hobson, P., Lab, M.J., et al.: \emph{Endocytic
+    pathways: combined scanning ion conductance and surface confocal
+    microscopy study.} Pflugers Arch - Eur J Physiol 2008, 456, 227–235 with permission.
   }
@@
 
-As the SICM and SCM data sets are recorded simultaneously, all data points inherently have a
-correlating data point in the other set. This immediate correlation, schematically illustrated in
-Fig.~\ref{fig:sicm+scm}a, allows not only for correlating studies in fixed
-samples (Fig.~\ref{fig:sicm+scm}c), but also studies of dynamics in live
-samples (Fig.~\ref{fig:sicm+scm}d).\todo{Improve paragraph}
+As the SICM and SCM data sets are recorded simultaneously, all data points
+inherently have a correlating data point in the other set, as illustrated in
+Fig.~\ref{fig:sicm+scm}a. This allows for determining the distribution of
+proteins in the proximity of the cell membrane (Fig.~\ref{fig:sicm+scm}b).
 
-SSCM has been used for investigating the dynamics of the interaction of
+First, SSCM  has been used for investigating the dynamics of the interaction of
 Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
-(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
-uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
-type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014}, for investigating
-the differentiation of stem cells \cite{Gorelik2008} and the correlation of
-topography and T-tubule distribution \cite{Lyon2012} or topography and
-mitochondria localization and appearance \cite{Miragoli2016} in healthy and 
-heart-failure cardiomyocytes. Furthermore, it has been utilized in 
-studies investigating endocytotic pathways \cite{Shevchuk2008}
-(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
-mechanism for clathrin-coated pits by recording topography simultaneously with
-the fluorescence of tagged actin-binding protein and the tagged clathrin
-light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated
-endocytosis revealed the effect of mutations in the Dynamin~2 gene on the
-maturation and internalisation of clathrin coated pits \cite{Ali2019}.
+\cite{Gorelik2002a}.
 
-% Bis hier
+Furthermore, it has been utilized in studies investigating endocytotic
+pathways \cite{Shevchuk2008a} (Fig.~\ref{fig:sicm+scm}b), besides others
+revealing an alternative closing mechanism for clathrin-coated pits by
+recording topography simultaneously with the fluorescence of tagged
+actin-binding protein and the tagged clathrin light-chain
+\cite{Shevchuk2012}. A further study on clathrin-mediated endocytosis revealed
+the effect of mutations in the Dynamin~2 gene on the maturation and
+internalisation of clathrin coated pits \cite{Ali2019}.
 
-% \subsection{Nanoinjection of fluorescently labeled molecules}
+\begin{figure}
+  \centering
+  \includegraphics{gr/correlating/SSCM-np}
+  \caption{%
+    \textbf{Investigation on nanoparticle uptake by SSCM.}  \textbf{a:} Height
+    profile of a section of a AT1-like cell treated with 200\,nm fluorescent
+    nanoparticles.  \textbf{b:} Slope representation of the area shown in a.
+    \textbf{c:} Surface fluoresecence of the same area.  \textbf{d:} Overlay
+    of surface fluorescence and slope representation.  Yellow arrowheads mark
+    nanoparticles that co-localise with membrane protrusions (white
+    arrowheads), blue arrowheads mark nanoparticles being in the process of
+    internalisation, green arrowheads mark fully internalised nanoparticles.
+    Reprinted with permission from P. Novak, A Shevchuk, P. Ruenraroengsak, et
+    al.: \emph{Imaging Single Nanoparticle Interactions with Human Lung Cells
+      Using Fast Ion Conductance Microscopy.} Nano Lett. 2014, 14, 3,
+    1202–1207. Copyright 2014 American Chemical Society.}
+  \label{fig:sscm-np}
+\end{figure}
 
-% Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
-% the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
-% fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
-% could be also used for nanoinjection of fluorescently labeled molecules into living cells 
-% \cite{Hennig2015a}. The SICM was therefore combined with wide-field and direct stochastic 
-% optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
-% stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
-% introduced into the membranes, could occur \cite{Hennig2015a}.
+SSCM was used to characterise the nanoparticle uptake by primary human alveolar
+epithelial type 2 (AT2) and by immortalized AT2 cells. Only the latter showed
+a strong tendency to internalise nanoparticles. Since, furthermore, the
+immortalized cells exhibited several characteristics of alveolar
+epithelial type 1 (AT1) cells, it was suggested that AT1 cells play a pivotal
+role in the translocation of nanometer-sized particles in the lung
+\cite{Kemp2008}.
 
-% The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
-% combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
-% In both studies the scanning ion conductance microscope was combined with TIRF investigations and 
-% the diffusion of single molecules over different regions at a spermatozoa were investigated.
+Figure~\ref{fig:sscm-np} shows nanoparticles in the proximity of the surface of
+AT1-like cells at three different stages of the internalisation: co-localised
+with membrane protrusions (yellow and white arrowheads, respectively), in the
+process of internalisation (blue arrowheads) and fully internalised (green
+arrowheads). An improvement of the scanning velocity by the addition of a stiff,
+short-range piezo actor onto the pipette positioning piezo actor allowed to
+follow the internalisation process with a temporal resolution of 15 seconds in
+detail \cite{Novak2014}.
 
-% The SICM-nanopipette could be also used for investigating membrane rafts 
-% \cite{Simons1997,Pike2006} by coordinated manipulation of focal adhesions. The pipette was 
-% functionalized with fibronectin, gangliosides were fluorescently labeled, the pipette deformed the 
-% focal adhesion side and the behavior of the fluorescently labeled gangliosides were detected. This 
-% was seen as a hint, how membrane rafts reacted \cite{Fuentes2012}.
-
-% Another example for a SICM-nanopipette based manipulation could be found in the study on the 
-% generation and distribution of plasma-derived extracellular vesicles (PEVs) on MDA-MB-231 and U87 
-% cells. Here the nanopipette were used for both, investigating the topography and for inducing the 
-% generation of the PEVs. Additionally the SICM was build up onto a confocal microscope, which could 
-% be used for the detection of Calcium \cite{Wang2020}.
-
-% % Piper2006 -> PMID: 17177370
-% The SICM-nanopipette could be also used as a nanosensor for pH- or ionic concentration changes 
-% \cite{Piper2006}. In this study fluorophores were trapped in the nanopipette and react on changes 
-% of the pH value or the concentration of ions with alterations in the detected fluorescence signal.
-
-% Dieser Abschnitt passt nicht so wirklich zu Fluoreszenz-Mikroskopie! Vielleicht noch so was 
-% schreiben, wie „SICM kann nicht nur mit Fluoreszenz mikroskopischen Methoden kombiniert werden, 
-% sondern kann auch mit … kombiniert werden!? Sonst kann der einfach auch weg. Mal gucken.
-
-% By using a special illumination system consisting of a light emitting diode (LED) light ring, SICM 
-% could also being combined with condenser-free phase contrast, darkfield and brightfield images and 
-% even Rheinberg illuminations were possible \cite{Webb2014}.
+Furthermore, SSCM was used for investigating the differentiation of stem cells
+\cite{Gorelik2008} and the correlation of topography and T-tubule distribution
+\cite{Lyon2012} or topography and mitochondria localisation and appearance
+\cite{Miragoli2016} in healthy and heart-failure cardiomyocytes.
 

### 2020-10-18 sections/srfm.tex
reworked

@@
 light beam and the image is collected pixel by
-pixel. Fig.~\ref{fig:FM-setups}c illustrates the major effect of the pinhole:
+pixel. Figure~\ref{fig:FM-setups}c illustrates the major effect of the pinhole:
 Emission from out-of-focus planes (dotted and dashed lines) is blocked by the
@@
   \includegraphics{gr/intro/localisation-mic}
-  \caption{}
+  \caption{%
+    \textbf{Principle of PALM.}
+    \textbf{a:} Initially, all fluorophores are in the inactivated state (grey
+    dots).
+    \textbf{b:} A small subset of the fluorophores is activated (cyan
+    background, white dots) and subsequently excited (green background, yellow
+    dots) until the fluorophores bleach (black dots). The emission of the
+    fluorophores is recorded. This series is repeated until all fluorophores
+    have emitted.
+    \textbf{c:} The positions of the fluorophores in the recordings are
+    determined and plotted as a Gaussian distribution with a standard
+    deviation equal to the uncertainty of the localisation and the single
+    images are combined to a single image with improved resolution.
+  }
   \label{fig:lm}
@@
 
-The principle of these methods is illustrated in Fig.~\ref{fig:lm}. Initially,
+As an example, the principle of PALM is illustrated in Fig.~\ref{fig:lm}. Initially,
 all fluorophores within the sample are inactivated (``off''-state, grey dots
@@
 which is a modification of Abbe's original equation
-(eq.~\eqref{eq:diffraction-limit}). Here, $I_\text{sat}$ is the intensity
-required to induce stimulated emission in half of the fluorophores.
+(Eq.~\ref{eq:diffraction-limit}). Here, $I_\text{sat}$ is the intensity
+required to induce stimulated emission in half of the fluorophores. The best resolution (approximately 2\,nm) obtained by STED microscopy has
+been recorded on samples containing fluorescent color centers in diamond
+crystal \cite{Wildanger2012}.
 
-The best resolution (approximately 2\,nm) obtained by STED microscopy has
-been recorded on samples containing fluorescent color centers in diamond
-crystal \cite{Wildanger2012}. Note that, by applying a depletion beam of a
+Note that, by applying a depletion beam of a
 different shape, STED microscopy allows to improve the resolution along the

### 2020-10-18 sections/introduction.tex
reworked

@@
     and location of a putative protein within it. \textbf{b:} Computed
-    diffraction limited fluorescence recording of the protein with a resolution
-    of 250\,nm. \textbf{c:} Computed
-    diffraction unlimited fluorescence recording of the protein with a
-    resolution of 75\,nm.}
+    diffraction limited fluorescence recording of the protein with a
+    resolution of 250\,nm. \textbf{c:} Computed diffraction unlimited
+    fluorescence recording of the protein with a resolution of 75\,nm.
+    Reprinted with permission from Philipp Hagemann, Astrid Gesper, Patrick
+    Happel: \emph{Correlative stimulated emission depletion and scanning ion
+      conductance microscopy.} ACS Nano 2018, 12, 5807-5815. Copyright 2018
+    American Chemical Society.}
   \label{fig:sicm-and-light-resolution}
@@
 protein correlates with the position of the protrusion
-(Fig.~\ref{fig:sicm-and-light-resolution}c).
+(Fig.~\ref{fig:sicm-and-light-resolution}c). Note that the resolutions used to
+compute the hypothetical fluorescent images correspond to resolutions
+experimentally obtained on corresponding instruments \cite{Hagemann2018}.
 

### 2020-10-18 manuscript.tex
ordered 2nd and 3rd author alphabetically
Update manuscript.tex
First typo-correction

@@
 
-\author{Patrick Happel \and Annika Haak \and Astrid Gesper}
-\authorrunning{Haak et al.}
+\author{Patrick Happel \and Astrid Gesper \and Annika Haak}
+\authorrunning{Happel et al.}
 % Use \authorrunning{Short Title} for an abbreviated version of
@@
 %
-  Investiganting the cell membrane is a unique strength of scanning ion conductance
+  Investigating the cell membrane is a unique strength of scanning ion conductance
   microscopes (SICM),

### 2020-10-18 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
First typo-correction

@@
 particles (VLPs) the correlated SICM-fluorescence confocal microscopy was used
-to investigate topography changes together with die distribution of
+to investigate topography changes together with the distribution of
 fluorescently labeled viral proteins like Gag or Viral Protein R
@@
 
-In both setups, an SICM is mounted onto an inverted confocal microscope and
+In both setups, a SICM is mounted onto an inverted confocal microscope and
 before simultaneous recording, the focus of the confocal FM objective is
@@
     nanoparticles.  \textbf{b:} Slope representation of the area shown in a.
-    \textbf{c:} Surface fluoresecence of the same area.  \textbf{d:} Overlay
+    \textbf{c:} Surface fluorescence of the same area.  \textbf{d:} Overlay
     of surface fluorescence and slope representation. Yellow arrowheads mark

### 2020-10-18 sections/srfm.tex
Update srfm.tex
First typo-correction

@@
 a wavelength range (green rectangle in Fig.~\ref{fig:jablonski-fluorescence}b) 
-suitable to excite the fluorophore used is chosen -- by using a suitable laser
+appropriate to excite the fluorophore used is chosen -- by using a suitable laser % I changed one "suitable" to "appropiate"
 or LED or by selecting the wavelength range via a band-pass filter from a

### 2020-10-18 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Second typo-correction

@@
 to investigate topography changes together with the distribution of
-fluorescently labeled viral proteins like Gag or Viral Protein R
+fluorescently labelled viral proteins like Gag or Viral Protein R
 \cite{Bednarska2020}. In contrast to investigating the virus formation with
@@
 First, SSCM has been used for investigating the dynamics of the interaction of
-Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
+Cy3-labelled polyoma virus-like particles (VLPs) with Cos-7 cells
 \cite{Gorelik2002a}.

### 2020-10-18 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex
First typo-correction
Update correlated-sicm-and-srfm.tex
Second typo-correction

@@
 imaged by both methods is marked in Fig.~\ref{fig:SICM_STED1}c (SICM: yellow
-rectangle, STED: gray rectangle).
+rectangle, STED: grey rectangle).
 
@@
       \textbf{Correlative SICM and STED recording of a group of HeLa cells.} 
-      \textbf{a:} Height (aa) and slope representatin (ab) of a SICM recording
+      \textbf{a:} Height (aa) and slope representation (ab) of a SICM recording
       of HeLa cells. \textbf{b:} Confocal (ba) and STED (bb) recording of the
@@
       with a black dotted line in a. \textbf{c:}  Relative position of 
-      the SICM (yellow rectangle) and the confocal/STED (gray rectangle)
+      the SICM (yellow rectangle) and the confocal/STED (grey rectangle)
       images with respect to each 
@@
 % SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
-% fluorescently labeled molecules -- ATTO 655-phalloidin -- into living U2OS cells.
+% fluorescently labelled molecules -- ATTO 655-phalloidin -- into living U2OS cells.
 

### 2020-10-18 sections/pitfalls.tex
minor changes, added acknowledgements
Update pitfalls.tex
First typo-correction

@@
 are two alignment options: The first one is aligning the pipette tip and the
-laser beam only in the $x,y$ plane. This is comparable, in terms of data
+laser beam only in the $x,y$-plane. This is comparable, in terms of data
 recording, to the above mentioned combinations of SICM and wide-field or
@@
 
+\section{Acknowledgements}
+The authors acknowledge support from the Volkswagen
+Foundation (grant 88 390) and the German Research Foundation (grant
+411517989). 
 %%% Local Variables:

### 2020-10-18 manuscript.tex
Update manuscript.tex
Second typo-correction

@@
   available, allowing to investigate 
-  labeled specimen such as proteins and their distribution within a cell at a
+  labelled specimen such as proteins and their distribution within a cell at a
   new level of detail. However, the place of the interaction between the

### 2020-10-18 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Third typo-correction

@@
     the area marked by the dashed rectangle. The cilium is not visible since
-    it is located benaeth the cell membrane \textbf{c:} (left) FM image of a
+    it is located beneath the cell membrane \textbf{c:} (left) FM image of a
     cilium in a MDCK cell, (right) SICM recording of the

### 2020-10-19 sections/srfm.tex
deleted one "suitable", removed "appropriate"

--- 2020-10-18 sections/srfm.tex
@@
 a wavelength range (green rectangle in Fig.~\ref{fig:jablonski-fluorescence}b) 
-suitable to excite the fluorophore used is chosen -- by using a suitable laser
+suitable to excite the fluorophore used is chosen -- by using a laser
 or LED or by selecting the wavelength range via a band-pass filter from a

### 2020-10-19 sections/introduction.tex
Update introduction.tex
First typo-correction
minor

@@
 
-\begin{figure}\centering
+\begin{figure}[t]\centering
   \includegraphics{gr/intro/Fig_SICM-resolution}
@@
     distances. \textbf{b:} Apparent height of the particles (solid line) and of
-    the gap between them (dahsed line) as determined by SICM. At distances
+    the gap between them (dashed line) as determined by SICM. At distances
     $d\lessapprox3r_\text{i}$, no gap between the particles is detected.
@@
 \cite{rheinlaender:094905,Rheinlaender2015}. Thus, the resolution of SICM is
-only limited by the technical limits to produce pipettes with very small
-openings. Pipettes with radii of approximately 6.75\,nm have been used in for
+only limited by the technical difficulties to produce pipettes with very small
+openings. Pipettes with radii of approximately 6.75\,nm have been used for
 SICM imaging \cite{Shevchuk2006}. In

### 2020-10-19 sections/srfm.tex
reworked

@@
 Fig.~\ref{fig:jablonski-fluorescence}a. Due to the non-radiative loss of
-energy during the involved vibrational decays (black arrows in
+energy during the involved vibrational decays (black wave-like arrows in
 Fig.~\ref{fig:jablonski-fluorescence}a), the energy $h\nu_\text{em}$ of the
@@
     vibrational excited state of the electronic state $S_1$ (green
-    arrow). After radiation-less relaxation (black arrow) into the vibrational
+    arrow). After radiation-less relaxation (black wave-like arrow) into the
+    vibrational 
     ground state of $S_1$, the molecule returns to one of the vibrational
@@
 
-Typical absorbance/emission spectra of fluorophores used as dyes in FM are
-shown in Fig.~\ref{fig:jablonski-fluorescence}b. In FM, a single wavelength or
-a wavelength range (green rectangle in Fig.~\ref{fig:jablonski-fluorescence}b) 
-suitable to excite the fluorophore used is chosen -- by using a laser
-or LED or by selecting the wavelength range via a band-pass filter from a
-white light source -- and send through the objective lens of the microscope to
-the sample. In most FMs (the so called epifluorescence microscopes), the
-emission is collected via the same objective lens. Since the emission is
-red-shifted with respect to the excitation wavelength, the emitted photons
-(wavelength range depicted by red rectangle in
-Fig.~\ref{fig:jablonski-fluorescence}b) can be separated from the ones used to
-excite the fluorophores by a dichroic mirror.
+A typical absorbance/emission spectrum of an arbitrary fluorophore used as dye
+in FM is shown in Fig.~\ref{fig:jablonski-fluorescence}b. In FM, a single
+wavelength or a wavelength range (green rectangle in
+Fig.~\ref{fig:jablonski-fluorescence}b) suitable to excite the fluorophore
+used is chosen -- by using a laser or LED or by selecting the wavelength range
+via a band-pass filter from a white light source -- and send through the
+objective lens of the microscope to the sample. In most FMs (the so called
+epifluorescence microscopes), the emission is collected via the same objective
+lens. Since the emission is red-shifted with respect to the excitation
+wavelength, the emitted photons can be separated from the ones used to
+excite the fluorophores by a dichroic mirror. The wavelength range of a typical
+detection window is depicted by the red rectangle in
+Fig.~\ref{fig:jablonski-fluorescence}b.
 
 \begin{figure}
-  \includegraphics{gr/intro/FM-setups}
-  \caption{\textbf{Beam paths and major components of fluorescent
-      microscopes.} \textbf{a:} Excitation (green) and emission (red) beam
-    paths of a wide-field microscope. \textbf{b:} Excitation (green) and
+  \includegraphics{gr/intro/widefield-setup}
+  \caption{\textbf{Beam paths and major components of a wide-field fluorescent
+      microscope.} Excitation (green) and emission (red) beam
+    paths. \textbf{b:} Excitation (green) and
     emission beam paths (red) of a confocal microscope.  \textbf{c:} Emission
@@
 sample is excited and how the emission is recorded. The beam paths and the
-major components of a wide-field and a confocal FM are depicted in
-Fig.~\ref{fig:FM-setups}. In a wide-field FM (Fig.~\ref{fig:FM-setups}a), the
+major optical components of a wide-field FM are depicted in
+Fig.~\ref{fig:FM-setups}. In a wide-field FM, the
 entire sample is illuminated at the same time, and all fluorophores in the sample
 emit at the same time (yellow circles in the right inset in
-Fig.~\ref{fig:FM-setups}a). The emission of the fluorophores (solid red shape
-in Fig.~\ref{fig:FM-setups}a, only five beam paths are shown for clarity) is
+Fig.~\ref{fig:FM-setups}). The emission of the fluorophores (solid red shape
+in Fig.~\ref{fig:FM-setups}, only five beam paths are shown for clarity) is
 collected by the objective lens, passes the dichroic mirror and is further
@@
 Each fluorophore in the sample generates a diffraction limited spot on the
-camera, and spots which are not separated in space by at least the diffraction limit
-cannot be distinguished as single spots. Thus, the wavelength which determines
-the resolution in a wide-field microscope is the wavelength $\lambda_\text{em}$
-of the emission.
+camera, and spots which are not separated in space by at least the diffraction
+limit overlap and cannot be distinguished as single spots. Thus, the
+wavelength which determines the resolution in a wide-field microscope is the
+wavelength $\lambda_\text{em}$ of the emission.
 
@@
 
+\begin{figure}
+  \includegraphics{gr/intro/confocal-setup}
+  \caption{\textbf{Beam paths and major components of a confocal fluorescent
+      microscope.} \textbf{a:} Excitation (green) and
+    emission beam paths (red).  \textbf{b:} Emission
+    beam path (filters omitted for clarity) of a confocal microscope showing
+    how out-of-focus emission (dashed and dotted lines) is suppressed by the
+    confocal pinhole.}
+  \label{fig:confocal-setup}
+\end{figure}
+
 This led to the invention of the confocal microscope
 \cite{Heimstaedt1911,Minsky1988}. The beam path of a confocal microscope is
-shown in Fig.~\ref{fig:FM-setups}b. Here, the excitation light (green solid
+shown in Fig.~\ref{fig:confocal-setup}a. Here, the excitation light (green solid
 shape) is focused onto the sample by the objective lens and only the
@@
 is located in front of a single detector (left inset in
-Fig.~\ref{fig:FM-setups}b). Since this setup does not allow imaging the entire
+Fig.~\ref{fig:confocal-setup}a). Since this setup does not allow imaging the entire
 sample at once, the sample has to be scanned with respect to the excitation
 light beam and the image is collected pixel by
-pixel. Figure~\ref{fig:FM-setups}c illustrates the major effect of the pinhole:
+pixel. Figure~\ref{fig:confocal-setup}b illustrates the major effect of the pinhole:
 Emission from out-of-focus planes (dotted and dashed lines) is blocked by the
@@
     determined and plotted as a Gaussian distribution with a standard
-    deviation equal to the uncertainty of the localisation and the single
+    deviation equal to the uncertainty of the localisation and the 
     images are combined to a single image with improved resolution.
@@
 overview is provided by several reviews of the techniques
-\cite{Patterson2010,Sengupta2014,Liu2015,Sauer2017}, suitable dyes
+\cite{Patterson2010,Sengupta2014,Liu2015,Sauer2017}, of suitable dyes 
 \cite{Li2018a} as well as by detailed imaging protocols
@@
 resolution beyond the diffraction limit (Fig.~\ref{fig:STED-principle}d). The
-resolution provided by STED microscopy depends on the intensity $I$ of the
+resolution obtained by STED microscopy depends on the intensity $I$ of the
 depletion beam and is given by
@@
 
-% The first concept to circumvent the diffraction limit was published in 1994
-% and realised in 2000 \cite{hell+wichmann,Klar2000}
-
-% Ernst Abbe found in 1873 \cite{Abbe1873} that the resolution $d$ of
-% conventional light microscopes is limited by diffaction to 
-% \begin{equation}
-%   d_\text{min} = \frac{\lambda}{2\mathrm{NA}} = \frac\lambda{2n\sin\alpha}\text.
-%   \label{eq:abbe}
-% \end{equation}
-%  One consequence of the diffraction limit is
-% that a beam of light cannot be focused to a spot smaller than $d_\text{min}$.
-
-% The place in the micropscope where the diffraction limited spot limits the
-% resolution of a microscopic recording depends on the implementation of the
-% microscope.
-
-% \begin{figure}
-% %  \includegraphics{gr/introduction/}
-% \end{figure}
-
-% \subsection{General approach}
-
-% \subsubsection{Different approaches}
-% While the majority of SRFM techniques follows the approach outlined above,
-% other techniques exist that use different approaches.
-
-% \subsection{Scanning techniques}
-
 %%% Local Variables:

### 2020-10-19 sections/correlated-sicm-and-fm.tex
reworked

@@
 confocal FM enables imaging of the same region and sample with both techniques
-(Fig.~\ref{fig:sicm+cfm}a). The technical implementation involves mounting a
-SICM onto an inverted confocal FM. The software used to control the two
-microscopes does not have to be the same as both microscopes record data
-independently from one another. However, as the recordings are not
-simultaneous, pixel-by-pixel correlation is hardly, if at all, possible.
+(Fig.~\ref{fig:sicm+cfm}a). Again, the technical implementation requires mounting a
+SICM onto an inverted confocal FM. Two different modes of operation are
+conceivable. In the first one, both microscopes record data
+independently from each other and thus both microscopes can use their own
+soft- and hardware to control the single components. However, pixel-by-pixel
+correlation, if desired, might be impeded by different
+implementations to compensate for non-linear responses of the positioning
+piezo-actors in the different software. This problem might become even more
+prominent if different positioning devices such as beam scanning for confocal
+FM and stage scanning for SICM are used.
+
+The second mode of operation is to record the topography and the fluorescence at each
+$x, y$-position at the same time or with only a minimal temporal
+offset. Technically, this requires the synchronisation of the SICM and the
+confocal microscope, which at least requires a distinct software.
 
@@
 
-Seifert et al. \cite{Seifert2017} investigated the morphological activity of
+Seifert et al. investigated the morphological activity of
 platelets by time-lapse SICM and subsequently obtained confocal recordings of
 cytoskeletal proteins of the investigated cells, allowing them to correlate
-the activity of the platelets and the structure of the cytoskeleton.
-In co-cultures of cardio-myocytes and myofibroblasts, the dynamics of
-myocyte-myofibroblast connections was linked to the expression of connexin-43
-\cite{Schultz2019}.
+the activity of the platelets and the structure of the cytoskeleton
+\cite{Seifert2017}.
+
+Another investigation which correlated SICM and subsequent confocal FM
+recordings studied cell-cell connections in co-cultures of cardio-myocytes and
+myofibroblasts. Here, the dynamics of myocyte-myofibroblast connections was
+linked to the expression of connexin-43 \cite{Schultz2019}.
 
@@
 A second study on neurons investigated, besides others, cargo transport in
-neuronal dendrites \cite{Takahashi2019}. Here, the combination of
+neuronal dendrites \cite{Takahashi2019}. Here, the simultaneous combination of
 confocal FM and SICM provided a hint that the transport processes observed by
@@
 
-In a study investigating the formation of human immunodeficiency virus-like
-particles (VLPs) the correlated SICM-fluorescence confocal microscopy was used
-to investigate topography changes together with the distribution of
-fluorescently labelled viral proteins like Gag or Viral Protein R
-\cite{Bednarska2020}. In contrast to investigating the virus formation with
-TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal FM
-allowed to investigate the apical side of the cells. It was found that the
-release of VLPs is a lot faster than the release at the basal cell side as
-known from TIRF investigations and furthermore, a potential impact on the
-release time by the application of a fluorescent marker was found
-\cite{Bednarska2020}.
+The simultaneous recording of SICM and confocal data was used to study the
+formation of human immunodeficiency virus-like particles (VLPs) together with
+the dynamics of fluorescently labelled viral proteins like Gag or Viral
+Protein R \cite{Bednarska2020}. In contrast to investigating the virus
+formation with TIRF microscopy \cite{Jouvenet2008}, the combination of SICM
+and confocal FM allowed to investigate the apical side of the cells. It was
+found that the release of VLPs is a lot faster than the release at the basal
+cell side as known from TIRF investigations and furthermore, a potential
+impact on the release time by the application of a fluorescent marker was
+found \cite{Bednarska2020}. The total height differences of the topographies
+analyzed in this study were approximately in the range of the vertical
+resolution of the confocal data, and thus, the data sets were not only
+correlated in the horizontal, but also in the vertical direction.
 

### 2020-10-19 sections/srfm.tex
added one more ref
added another ref

@@
 resolution obtained by STED microscopy depends on the intensity $I$ of the
-depletion beam and is given by
+depletion beam and is given by \cite{Harke2008a}
 \begin{equation}
@@
 different shape, STED microscopy allows to improve the resolution along the
-optical axis \cite{Harke2008, Wildanger2009}. A large number of reviews articles exist
+optical axis \cite{Klar2000,Harke2008, Wildanger2009}. A large number of reviews articles exist
 which summarize the use of STED (or in general, RESOLFT) microscopy in different

### 2020-10-19 sections/pitfalls.tex
reworked

@@
 
-% Instead of having to worsen SICM resolution to match FM resolution, it might be 
-% reasonable to combine SICM and SRFM in one setup. Though, this implementation
-% comes with its own potential pitfalls, especially as due to the super resolution
-% of both techniques small deviations or disturbances are sufficient to ruin the 
-% alignment of the setup. Some of these potential pitfalls are discussed in the 
-% following:
-
-% To avoid some problems from the beginning, both the SRFM and SICM setups
-% should provide spatial resolutions in the same range. Also, if possible, one
-% software should be used to control both setups to prevent delays in the
-% imaging process due to transmitting information from one software to the other.
-
 In the case of combining SICM with a scanning technique such as STED, there
@@
 Especially the second option would require repeated
-focal plane adjustment of the optical setup. In turn, this requires meticulous
+focal plane adjustment of the optical setup. If this is implemented by moving
+the objective (Fig.~\ref{fig:sscm_setup}b), this requires meticulous
 alignment of the excitation and depletion beam to retain the super-imposition
-of the two beams during the adjustment of the focal plane. To minimize the
+of the two beams during the adjustment of the focal plane.
+
+To minimize the
 pixels that require an adjustment of the focal plane, the adjustment has been
 only applied if a $z$-range of more than one micrometer was exceeded
-\cite{Novak2014}. If STED recordings with increased vertical resolution are
-intended, the acceptable range for not adjusting the focal plane decreases,
+\cite{Novak2014}. However, the resolution of STED microscopy depends on
+the intensity of the depletion beam, which decreases along the optical
+axis. Thus, the range for unadjusted imaging might decrease and, if STED
+recordings with increased vertical resolution are
+targeted, will decrease even further,
 which in turn might lead to longer and less stable recordings.
@@
 combination of SICM and confocal microscopes \cite{Gorelik2002a,
-  Shevchuk2008,Novak2014}, additional piezo elements might be required for the
-alignment of STED and SICM.
+  Shevchuk2008,Novak2014}, additional piezo actors might be required for the
+alignment of STED and SICM. However, for the alignment of the SICM pipette and a
+confocal beam by piezo actors a remaining offset in the alignement has been
+reported \cite{Bednarska2020}.
 

### 2020-10-19 sections/pitfalls.tex
Update pitfalls.tex
Typo-correction

@@
 alignment of STED and SICM. However, for the alignment of the SICM pipette and a
-confocal beam by piezo actors a remaining offset in the alignement has been
+confocal beam by piezo actors a remaining offset in the alignment has been
 reported \cite{Bednarska2020}.

### 2020-10-19 manuscript.tex
One correction and one suggestion

@@
   which use a fine tip to determine the topography of the investigated sample
-  and thus allows to investigate the cell membrane without labelling.    
+  and thus allows investigating the cell membrane without labelling.
+  % 3 times the word "investigating" in this sentence does not look very elegant to me!? 
+  % Maybe we can change the senctence to:
+  %   The possibility of studying the cell membrane is a unique strength of scanning ion 
+  %   conductance microscopes (SICM), which use a fine tip to determine the topography 
+  %   of the sample and thus allows investigating the cell membrane without labelling.
 %  
